---
title: "Thoughts about Power and Sample Size for On-Farm Strip Trials"
author: "Peter Claussen"
date: "6/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

Experimentalists are frequently introduced to the design of experiments with a discussion of statistical power and sample size calculations. This discussion starts with a simple formula based on scalar (point) estimates of means and standard deviation and leads to planning replication of treatments over experimental units.

How do we extend power and sample size calculations to strip trials? When the experimental design includes strips in a field, we no longer have point estimates of the effect of treatments on experimental units; we instead can model response as a one-dimensional function of position in the strip, or a two-dimensional function of a point in space. We no longer model standard deviation as the expected variance of scalar random variable from the point estimate of the mean; instead, we can consider variation as dependent on location over both time and space.

Using examples of analysis of past on-farm strip trials, we discuss how understanding analysis methods beyond point estimation (i.e. time-series, geospatial statistics or functional data analysis) can guide planning for future on-farm trials.

```{r}
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```



# East Quarter

```{r}
load(file="../yield_monitor_data/workshop2017/Case Study 2/Strips.Rda")
```

```{r,fig.width=8,fig.height=4, EastQuarterProduct}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r}

#EastQuarter.dat$ObjId <- as.numeric(as.character(EastQuarter.dat$ObjId))
#EastQuarter.dat <- EastQuarter.dat[!is.na(EastQuarter.dat$ObjId),]
#EastQuarter.dat$Pass <- 1
#Pass <- 1
#for(i in 2:dim(EastQuarter.dat)[1]) {
#  if(EastQuarter.dat$ObjId[i] > (EastQuarter.dat$ObjId[i-1]+2)) {
#    Pass <- Pass + 1
#  }
#  EastQuarter.dat$Pass[i] <- Pass
#}
#EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
#levels(EastQuarter.dat$Pass)

EastQuarter.dat$Pass <- floor(EastQuarter.dat$Northing/6)+1
EastQuarter.dat$Pair <- floor((EastQuarter.dat$Pass+1)/2)
EastQuarter.dat$Direction <- "Easterly"
EastQuarter.dat$Direction[EastQuarter.dat$Heading>100] <- "Westerly"
EastQuarter.dat$Direction <- as.factor(EastQuarter.dat$Direction)

#EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] <- EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] + 400
EastQuarter.dat$PassNo <- EastQuarter.dat$Pass

EastQuarter.dat$Block <- ceiling(EastQuarter.dat$Pair/2)
EastQuarter.dat$Strip <- EastQuarter.dat$Pair %/% EastQuarter.dat$Block
EastQuarter.dat$Block <- as.factor(EastQuarter.dat$Block)
EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
EastQuarter.dat$Pair <- as.factor(EastQuarter.dat$Pair)
EastQuarter.dat$Strip <- as.factor(EastQuarter.dat$Strip)

```




```{r,fig.width=8,fig.height=4, EastQuarterPass}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pass),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pass", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```


```{r,fig.width=8,fig.height=4, EastQuarterPair}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pair),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pair", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterDirection}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Direction),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Direction", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterBlock}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Block),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Block", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterStrip}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Strip),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Strip", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

# One dimensional analysis

Strips as experimental units

```{r}
means.dat <- with(EastQuarter.dat, data.frame(
  Pass = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,1],
  Yield = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Product = aggregate(as.numeric(Product) ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Northing = aggregate(Northing ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2]
))
means.dat
means.dat$Product <- levels(EastQuarter.dat$Product)[means.dat$Product]
```

```{r}
ggplot(EastQuarter.dat, aes(x=Northing, y=Yield)) + 
geom_boxplot(aes(group=Pass,color=Product)) + geom_jitter(width = 0.2,size=0.2) +
scale_colour_manual(values=cbPalette) +
labs(colour = "Yield", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```



```{r}
ggplot(means.dat, aes(x=Northing, y=Yield, color=Product,fill=Product)) +
  geom_bar(stat="identity") + scale_colour_manual(values=cbPalette) + scale_fill_manual(values=cbPalette)
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Product, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Product,colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```





```{r}
#levels(as.factor(EastQuarter.dat$Swath))
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pair, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

## Smoothing

Assume that most error is sampling error, so we produce LOESS smoothed curves.
```{r}
Travel <- abs(EastQuarter.dat$Easting[2:dim(EastQuarter.dat)[1]] - EastQuarter.dat$Easting[1:(dim(EastQuarter.dat)[1]-1)])
hist(Travel)
Travel <- Travel[Travel<5]
hist(Travel)
mean(Travel)
```

Create a data frame of passes, one observation for every 2 meters, excluding ends
```{r}
LOESS.basis <- rep(seq(2,398,by=2))
total.passes <- max(EastQuarter.dat$PassNo)
Smoothed.dat <- data.frame(
  Yield = rep(0,total.passes*length(LOESS.basis)),
  Easting = rep(LOESS.basis,total.passes),
  PassNo = rep(1:total.passes,each=length(LOESS.basis)),
  Pair = rep(0,total.passes*length(LOESS.basis)),
  Product = rep(levels(EastQuarter.dat$Product),total.passes*length(LOESS.basis)/2),
  Northing = rep(0,total.passes*length(LOESS.basis))
)
#for(i in 1:max(EastQuarter.dat$PassNo)) {
for(i in 1:total.passes) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  current.loess <- loess(Yield ~ Easting,data=current.pass)
  current.smoothed <- predict(current.loess, data.frame(Easting = LOESS.basis))
  Smoothed.dat$Yield[Smoothed.dat$PassNo==i] <- current.smoothed
  Smoothed.dat$Pair[Smoothed.dat$PassNo==i] <- current.pass$Pair[1]
  Smoothed.dat$Product[Smoothed.dat$PassNo==i] <- current.pass$Product[1]
  Smoothed.dat$Northing[Smoothed.dat$PassNo==i] <- mean(current.pass$Northing)
}
Smoothed.dat$Pass <- as.factor(Smoothed.dat$PassNo)
```
```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```


```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r}
#head(EastQuarter.dat)
```


# Permutations
Possible combinations of pairs
$$
\frac{14!}{7!(14!-7!)}
$$
Lady tasting tea example:
```{r}
fac8 <- factorial(8)
fac4 <- factorial(4)
fac8/(fac4*fac4)
```

Note that
```{r}
2/70
```

```{r}
fac12 <- factorial(12)
fac6 <- factorial(6)

fac12/(fac6*fac6)
```

Note the relationship between rank sum permutations
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3111167/pdf/bjc2011157a.pdf

Iterating over each possible combination, 000000 111111 to 111111 000000

000000 111111
000001 011111
000010 011111
000100 011111

Modified from 
```{r}
binary <- function(x,digits=32) {
  i <- 0
  string <- rep(0,digits)
  while(x > 0) {
    string[digits - i] <- x %% 2
    x <- x %/% 2
    i <- i + 1 
  }
  string
}
```


```{r}
permutations <- fac12/(fac6*fac6)
randomizations <- matrix(0,nrow=permutations,ncol=12)
idx <- 1
for(i in 1:(2^12)) {
  trts <- binary(i,12)
  if(sum(trts) == 6) {
    randomizations[idx,] <- trts
    idx <- idx+1
  }
}
head(randomizations)
tail(randomizations)
```

```{r}
pair.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Pair),mean,na.rm=TRUE)
Strip <- 1:12
Product <- rep(c(1,0), 6)
summary(lm(pair.means ~ Strip))

#product.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Product),mean,na.rm=TRUE)
product.means <- tapply(pair.means,list(Product),mean,na.rm=TRUE)
product.means
product.sd <- tapply(pair.means,list(Product),sd,na.rm=TRUE)
product.sd
mean(pair.means)
sd(pair.means)

product.diff <- product.means[1]-product.means[2]
product.diff
```


Rememer that our $t$ statistic is

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sigma / \sqrt{n}}
$$

With two sd, we can write

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sqrt{\sigma^2_1/n_1 + \sigma^2_2/n_2}}
$$

```{r}
product.diff / sqrt(sum(product.sd^2/6))
```

```{r}
summary(aov(pair.means ~ as.factor(Product)))
qt(1-0.05/2,10)
```

```{r}
2*(1-pt(product.diff / sqrt(sum(product.sd^2/6)),10))
```

```{r}
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(pair.means,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=30)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



## Permuations by position

```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
Prob$Diff <- 0
Prob$SD <- 0
Prob$SE <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.sd <- tapply(obs$Yield,list(obs$Product),sd,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  Prob$Diff[i] <- product.diff
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  Prob$P[i] <- 2*sum(diffs>product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
  #Prob$SD[i] <- sd(pair.means)
  #pooled SD
  Prob$SD[i] <- sqrt(sum(product.sd^2)/2)
  Prob$SE[i] <- sqrt(sum(product.sd^2/6))
}
```

```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") #+ylim(125, 275)
```



```{r,fig.width=8,fig.height=8}
#Prob$Z <- Prob$Diff/(Prob$SE/sqrt(6))
Prob$Z <- Prob$Diff/Prob$SE
Prob$PZ <- 2*(1-pt(Prob$Z,10))
par(mfrow=c(2,2))
plot(Diff ~ Easting,data=Prob,type='l',main='Treatment Differences')
plot(P ~ Easting,data=Prob,type='l',main='Probability')
lines(PZ ~ Easting,data=Prob,type='l',col='blue')
abline(h=0.05,col='red')
plot(SD ~ Easting,data=Prob,type='l',main='Standard Deviation')
plot(Z ~ Easting,data=Prob,type='l',main='t Value')
abline(h=qt(1-0.05/2,10),col='blue')
```

```{r}

```

```{r,fig.width=6,fig.height=9}
par(mfrow=c(3,1))
plot(P ~ SD,data=Prob)
plot(P ~ Diff,data=Prob)
plot(P ~ Z,data=Prob)
abline(h=0.05,col='red')
abline(v=qt(1-0.05/2,10),col='blue')
plot(P ~ PZ,data=Prob)
```



### From ISA

```{r}
Yield <- c(44.8,48.6,51.8,46.9,46.4,47.9,53.9,52.8,60.9,57.9,60.9,58.1)
Treatment <- c('Untreated','Priaxor','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated')
Strip <- 1:12
Pair <- as.factor(ceiling(Strip/2))
summary(lm(Yield ~ Strip))
```

using the lm permutation library
```{r}
library(lmPerm)
summary(aovp(Yield ~ Treatment))
summary(aovp(Yield ~ Treatment + Pair))
summary(aovp(Yield ~ Treatment + Pair,perm="Exact"))
```

We start using the same randomizations as our previous example - this assumes that any strip in the field could have been either untreated or Priaxor treated.

```{r}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```

In the event, strips were randomized in pairs. Thus, we have $2^n = 2^6 = 64$ possible randomizations. We recompute by

```{r}
randomizations <- matrix(0,nrow=64,ncol=12)
pair.trt <- matrix(c(0,1,1,0),nrow=2)
idx <- binary(3,6)
as.vector(t(pair.trt[idx+1,]))
for(i in 1:64) {
  idx <- binary(i-1,6)
  randomizations[i,] <- as.vector(t(pair.trt[idx+1,]))
}
colSums(randomizations)
rowSums(randomizations)
```

```{r}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  sum(diffs>=product.diff)
  Prob$P[i] <- 2*sum(diffs>=product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
}

plot(P ~ Easting,data=Prob)
abline(h=0.05,col='red')
```


# Functional

Create a matrix of passes, 1 row per second

```{r}
pass.length <- tapply(EastQuarter.dat$Yield, list(EastQuarter.dat$Pass),length)
pass.length
time.points <- max(pass.length)
time.points
pass.mat <- matrix(NA,nrow=time.points,ncol=max(EastQuarter.dat$PassNo))
for(i in 1:max(EastQuarter.dat$PassNo)) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  direction <- order(current.pass$Easting)
  pass.mat[1:dim(current.pass)[1],i] <- t(current.pass$Yield[direction])
}
```

First, we need to create a set of functions.  How many observations per pass?

```{r}

library(fda)
time <- 1:time.points
test.mat <- pass.mat[1:min(pass.length),1:12]
#passes.fda <- smooth.basisPar(argvals=time, y=pass.mat, lambda=1)
```

```{r}
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=40)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=400)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4000)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
```


```{r}

summary(aov(Yield ~ Product + Block+Pair+Pass,data= EastQuarter.dat))
library(nlme)
summary(lme(Yield ~ Product + Block, random = ~ 1 | Pass,data= EastQuarter.dat))
summary(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))

summary(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))

summary(aov(Yield ~ Block+Product + Error(Product:Block), data= EastQuarter.dat))
```

# Paired vs unpaired tests
https://en.wikipedia.org/wiki/Paired_difference_test

# Two dimensions
