---
title: "Optimality Criteria for Covariance"
author: "Peter Claussen"
output: html_document
---

```{r}
options(digits=12)
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
trace <- function(x) {sum(diag(x))}
```

Cochran and Cox, Table 3.1
```{r}
Cochran3_1.dat <- data.frame(
Rep=as.factor(c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4)),
Blk=as.factor(c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6)),
Col=as.factor(c(1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 5, 6, 7, 8, 5, 6, 7, 8, 5, 6, 7, 8, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 5, 6, 7, 8, 5, 6, 7, 8, 5, 6, 7, 8)),
Plot=as.factor(c(101, 102, 103, 104, 201, 202, 203, 204, 301, 302, 303, 304, 401, 402, 403, 404, 501, 502, 503, 504, 601, 602, 603, 604, 701, 702, 703, 704, 801, 802, 803, 804, 901, 902, 903, 904, 1001, 1002, 1003, 1004, 1101, 1102, 1103, 1104, 1201, 1202, 1203, 1204)),
Trt=as.factor(c(4, 10, 3, 9, 12, 6, 8, 5, 1, 11, 7, 2, 7, 5, 10, 4, 9, 6, 8, 11, 2, 12, 1, 3, 8, 1, 10, 6, 7, 11, 9, 4, 12, 2, 5, 3, 11, 12, 6, 7, 1, 5, 3, 9, 4, 8, 2, 10)),
First=c(162, 191, 107, 67, 102, 193, 128, 42, 124, 211, 194, 222, 23, 19, 44, 48, 29, 9, 17, 19, 193, 209, 109, 153, 282, 230, 216, 145, 138, 100, 197, 263, 269, 283, 252, 212, 88, 25, 42, 62, 107, 89, 41, 74, 95, 127, 80, 134),
Second=c(365, 563, 415, 338, 363, 561, 311, 222, 268, 505, 433, 408, 80, 114, 268, 298, 254, 92, 28, 106, 292, 352, 132, 454, 372, 256, 708, 304, 194, 219, 421, 379, 466, 280, 398, 386, 356, 212, 308, 221, 236, 332, 176, 137, 199, 166, 142, 590)
)
Cochran3_1.dat$lat <- as.numeric(Cochran3_1.dat$Blk)
Cochran3_1.dat$lon <- as.numeric(Cochran3_1.dat$Col)
Cochran3_1.dat$Treatment <- as.character(Cochran3_1.dat$Trt)
Cochran3_1.dat$Treatment[Cochran3_1.dat$Treatment %in% c("9","10","11","12")] <- "Check"
Cochran3_1.dat$Treatment <- as.factor(Cochran3_1.dat$Treatment)
```

```{r}
library(desplot)
```

# Analysis of Covariance

Following Milliken (), we model the standard randomized complete block model as


$$
y_{ij} = \alpha_i + b_j + e_{ij}
$$
and add a linear response to a covariate

$$
y_{ij} = \alpha_i + b_j + \beta x_{ij} + e_{ij}
$$

We can extend this to include a treatment-specific response to covariate

$$
y_{ij} = \alpha_i + b_j +\beta_0 x_{ij} + \beta_i x_{ij} + e_{ij}
$$
Optionally, we might center the covariate by
$$
y_{ij} = \alpha_i + b_j +\beta_0 (x_{ij} - \bar{x}) + \beta_i (x_{ij} - \bar{x}) + e_{ij}
$$

## Models

- RCB
- RCB + covariate
- RCB + covariate + treatment interaction
- RCB + covariate + treatment interaction + replicate interaction
- covariate
- covariate interaction

```{r}
rcb.lm <- lm(Second ~ Rep + Trt, data=Cochran3_1.dat, x=TRUE)
rcbc.lm <- lm(Second ~ Rep + Trt + First, data=Cochran3_1.dat, x=TRUE)
rcbci.lm <- lm(Second ~ Rep + Trt + First + Trt:First, data=Cochran3_1.dat, x=TRUE)
rcbciri.lm <- lm(Second ~ Rep + Trt + First + Rep:First + Trt:First, data=Cochran3_1.dat, x=TRUE)
c.lm <- lm(Second ~ First, data=Cochran3_1.dat, x=TRUE)
ci.lm <- lm(Second ~ First + Trt:First, data=Cochran3_1.dat, x=TRUE)
```

```{r}
summary(aov(rcbciri.lm))
```
In this case, there is no evidence of an interaction, so we can use the simple covariate regression model

```{r}
summary(aov(rcbc.lm))
summary(aov(c.lm))
```

```{r}
summary(rcbc.lm)
summary(lm(Second ~ First + Rep + Trt, data=Cochran3_1.dat))
summary(c.lm)
```
## Table 9.1, Milliken III


```{r}
arm.dat <- data.frame(
plot=as.factor(c(102, 201, 302, 401, 502, 601, 101, 202, 301, 402, 501, 602)), 
treatment=as.factor(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2)), 
replicate=as.factor(c(1, 2, 3, 4, 5, 6, 1, 2, 3, 4, 5, 6)),
assessment2=c(26.600000, 31.100000, 34.700000, 34.400000, 32.100000, 28.500000, 30.200000, 29.200000, 32.100000, 31.900000, 30.200000, 31.000000), 
assessment1=c(0.910000, 1.220000, 1.430000, 1.450000, 1.330000, 1.100000, 1.020000, 0.890000, 1.390000, 1.470000, 1.270000, 1.120000)
)
arm.lm <- lm(assessment2 ~ replicate + assessment1 + treatment, data=arm.dat, model=FALSE)
alt.lm <- lm(assessment2 ~ treatment + assessment1 + replicate, data=arm.dat, model=FALSE,x=TRUE)
aov.tbl<-anova(arm.lm)
alt.tbl<-anova(alt.lm)
print(summary(arm.lm))
print(aov.tbl)
print(alt.tbl)

treatments <- length(levels(arm.dat$treatment))
C.t <- match.fun(arm.lm$contrasts[['treatment']])(treatments)
reps <- length(levels(arm.dat$replicate))
L.r <- matrix(rep(1,(reps-1)*treatments),nrow=treatments)
L.r <- L.r/(reps)
coeffs <- arm.lm$coefficients

cov.means <- rep(mean(arm.dat$assessment1),dim(C.t)[1])
L  <- cbind(rep(1,dim(C.t)[1]), cov.means, L.r, C.t)
trt.means <- L %*% coeffs
means.tbl <- data.frame(trt=as.integer(levels(arm.dat$treatment)),arith=tapply(arm.dat$assessment2, list(arm.dat$treatment), mean),lsmean= trt.means)
means.tbl
L.contrasts <- NULL
for(i in 1:  (dim(L)[1]-1)) {
  for(j in (i+1):(dim(L)[1])) {
    L.contrasts <- rbind(L.contrasts, L[i,]-L[j,])
  }
}
L.contrasts

Vcoeffs <- vcov(arm.lm)
Vcoeffs
Sigma.m <- 1 / sqrt(diag(L.contrasts %*% Vcoeffs %*% t(L.contrasts)))
if(dim(L.contrasts)[1]>1) {
  Sigma <- diag(Sigma.m)
} else {
  Sigma <- Sigma.m
}
Sigma.m
t_ <- Sigma %*% L.contrasts %*% coeffs
Cor <- Sigma %*% (L.contrasts %*% Vcoeffs %*% t(L.contrasts)) %*% t(Sigma)
se.vec <- diag(L.contrasts %*% Vcoeffs %*% t(L.contrasts))
SE.table <- matrix(0,nrow=treatments,ncol=treatments)

se.idx <- 1
for (i in 1:(dim(L)[1]-1)) {
   for(j in (i+1):(dim(L)[1])) {
      SE.table[i,j] <- se.vec[se.idx]
      SE.table[j,i] <- se.vec[se.idx]
      se.idx <- se.idx + 1
   }
}
SE.table
X <- alt.lm$x
(t(X) %*% X)

alpha = 0.05
err.df <- arm.lm$df.residual
crit.t <-qtukey(1 - alpha / 2, treatments, err.df)
crit.tbl <- SE.table * crit.t
crit.tbl
```


```{r,fig.height=5,fig.width=5}
qplot(treatment,assessment1,data=arm.dat,geom='boxplot') +   
  stat_summary(fun.y=mean,shape=1,col='red',geom='point') + 
  labs(y= "OC", x = "Treatment") +
  ggtitle("RCB Blocks")
```

```{r,fig.height=5,fig.width=8}
ggplot(arm.dat, aes(replicate,assessment1)) + 
geom_point(aes(colour = treatment),size=2) + 
scale_colour_manual(values=cbPalette) +
  labs(colour = "Treatment", x="Replicate", y="OC", title = "Replicate Covariates")
```

```{r}
ggplot(arm.dat, aes(assessment1,assessment2)) + 
geom_point(aes(colour = treatment),size=2) + 
geom_smooth(aes(group=treatment),se = FALSE, method = lm) +
scale_colour_manual(values=cbPalette) +
  labs(colour = "Treatment", x="OC", y="Yield", title = "Replicate Covariates")
```

```{r}
ggplot(arm.dat, aes(assessment1,assessment2)) + 
geom_point(aes(colour = treatment),size=2) + 
geom_smooth(se = FALSE, method = lm) +
scale_colour_manual(values=cbPalette) +
  labs(x="OC", y="Yield", title = "Replicate Covariates")
```

```{r}
ggplot(arm.dat[arm.dat$treatment %in% c(1,11),], aes(assessment1,assessment2)) + 
geom_point(aes(colour = treatment),size=2) + 
geom_smooth(se = FALSE, method = lm) +
scale_colour_manual(values=cbPalette) +
  labs(x="OC", y="Yield", title = "Replicate Covariates")
```

# Comparisons

We need to normalize the covariate

```{r}
arm.dat$cov <- arm.dat$assessment1/(max(arm.dat$assessment1))
```

```{r}
rcb.lm <- lm(assessment2 ~ replicate + treatment, data=arm.dat, x=TRUE)
rcbc.lm <- lm(assessment2 ~ replicate + treatment + cov, data=arm.dat, x=TRUE)
rcbci.lm <- lm(assessment2 ~ replicate + treatment + cov + treatment:cov, data=arm.dat, x=TRUE)
rcbciri.lm <- lm(assessment2 ~ replicate + treatment + cov + replicate:cov + treatment:cov, data=arm.dat, x=TRUE)
c.lm <- lm(assessment2 ~ cov, data=arm.dat, x=TRUE)
ci.lm <- lm(assessment2 ~ cov + treatment:cov, data=arm.dat, x=TRUE)
```

```{r}
summary(aov(rcb.lm))
summary(aov(rcbc.lm))
summary(aov(rcbci.lm))
summary(aov(rcbciri.lm))
summary(aov(c.lm))
summary(aov(ci.lm))
```

```{r}
#summary(rcb.lm)
#summary(rcbc.lm)
#summary(rcbci.lm)
#summary(c.lm)
#summary(ci.lm)
```

## Information

- Design information

$$
\mathcal{I} = X^{t} X
$$

```{r}
print(I.rcb <- t(rcb.lm$x) %*% rcb.lm$x)
print(I.rcbc <- t(rcbc.lm$x) %*% rcbc.lm$x)
print(I.rcbci <- t(rcbci.lm$x) %*% rcbci.lm$x)
print(I.c <- t(c.lm$x) %*% c.lm$x)
print(I.ci <- t(ci.lm$x) %*% ci.lm$x)

print(Ds <- c(det(I.rcb), det(I.rcbc), det(I.rcbci), det(I.c), det(I.ci)))
print(As <- c(trace(I.rcb), trace(I.rcbc), trace(I.rcbci), trace(I.c), trace(I.ci)))
```

- Contrast information

$$
c^{t} \mathcal{I}^{-} c
$$

since $Var(\widehat{ {c^{t} \tau}} ) = c^{t} \mathcal{I}^{-} c \sigma^2$

```{r}
print(I.rcb <- t(rcb.lm$x) %*% rcb.lm$x)
print(I.rcbc <- t(rcbc.lm$x) %*% rcbc.lm$x)
print(I.rcbci <- t(rcbci.lm$x) %*% rcbci.lm$x)
print(I.c <- t(c.lm$x) %*% c.lm$x)
print(I.ci <- t(ci.lm$x) %*% ci.lm$x)

treatments <- length(levels(arm.dat$treatment))
C.t.rcb <- match.fun(rcb.lm$contrasts[['treatment']])(treatments)
reps <- length(levels(arm.dat$replicate))
L.r.rcb <- matrix(rep(1,(reps-1)*treatments),nrow=treatments)
L.r.rcb <- L.r.rcb/(reps)
```

```{r}
midpoint <- mean(arm.dat$cov) #(max(arm.dat$cov) + min(arm.dat$cov))/2
cov.means <-rep(midpoint,dim(C.t.rcb)[1]) # rep(mean(arm.dat$assessment1),dim(C.t.rcb)[1])
L.rcb  <- cbind(rep(1,dim(C.t.rcb)[1]), L.r.rcb, C.t.rcb)
L.rcbc  <- cbind(rep(1,dim(C.t.rcb)[1]), L.r.rcb, C.t.rcb, cov.means)
L.rcbci  <- cbind(rep(1,dim(C.t.rcb)[1]), L.r.rcb, C.t.rcb, cov.means, C.t.rcb*mean(arm.dat$cov))
L.c  <- cbind(rep(1,dim(C.t.rcb)[1]), cov.means)
L.ci  <- cbind(rep(1,dim(C.t.rcb)[1]), cov.means, C.t.rcb*mean(arm.dat$cov))
```


```{r}
Table9.1.means <- data.frame(
  RCB = L.rcb %*% coef(rcb.lm),
  RCBC = L.rcbc %*% coef(rcbc.lm),
  RCBCI = L.rcbci %*% coef(rcbci.lm),
  C = L.c %*% coef(c.lm),
  CI = L.ci %*% coef(ci.lm)
)
Table9.1.means
```

```{r}
library(lsmeans)

lsmeans(rcb.lm, ~ treatment)
lsmeans(rcbc.lm, ~ treatment)
lsmeans(rcbci.lm, ~ treatment)
```

```{r}
L.rcb.contrasts <- NULL
L.rcbc.contrasts <- NULL
L.rcbci.contrasts <- NULL
L.c.contrasts <- NULL
L.ci.contrasts <- NULL

for(i in 1:  (dim(L.rcb)[1]-1)) {
  for(j in (i+1):(dim(L.rcb)[1])) {
    L.rcb.contrasts <- rbind(L.rcb.contrasts, L.rcb[i,]-L.rcb[j,])
    L.rcbc.contrasts <- rbind(L.rcbc.contrasts, L.rcbc[i,]-L.rcbc[j,])
    L.rcbci.contrasts <- rbind(L.rcbci.contrasts, L.rcbci[i,]-L.rcbci[j,])
    L.c.contrasts <- rbind(L.c.contrasts, L.c[i,]-L.c[j,])
    L.ci.contrasts <- rbind(L.ci.contrasts, L.ci[i,]-L.ci[j,])
  }
}
```


```{r}
print(CI.rcb <- L.rcb.contrasts %*% I.rcb %*% t(L.rcb.contrasts))
print(CI.rcbc <- L.rcbc.contrasts %*% I.rcbc %*% t(L.rcbc.contrasts))
print(CI.rcbci <- L.rcbci.contrasts %*% I.rcbci %*% t(L.rcbci.contrasts))
print(CI.c <- L.c.contrasts %*% I.c %*% t(L.c.contrasts))
print(CI.ci <- L.ci.contrasts %*% I.ci %*% t(L.ci.contrasts))

print(DCs <- c(det(CI.rcb), det(CI.rcbc), det(CI.rcbci), det(CI.c), det(CI.ci)))
print(ACs <- c(trace(CI.rcb), trace(CI.rcbc), trace(CI.rcbci), trace(CI.c), trace(CI.ci)))
```

## Cochran Data

```{r}
aov.lm <- lm(Second ~ Rep + Trt, data=Cochran3_1.dat,x=TRUE)
aocv.lm <- lm(Second ~ First + Rep + Trt, data=Cochran3_1.dat,x=TRUE)
alt.lm <- lm(Second ~ Trt + Rep +  First +  0, data=Cochran3_1.dat,x=TRUE)
aov.tbl<-anova(aov.lm)
aocv.tbl<-anova(aocv.lm)
alt.tbl<-anova(alt.lm)
print(summary(aov.lm))
print(aov.tbl)

print(summary(aocv.lm))
print(aocv.tbl)

print(summary(alt.lm))
print(alt.tbl)
```

```{r}
treatments <- length(levels(Cochran3_1.dat$Trt))
C.t <- match.fun(aocv.lm$contrasts[['Trt']])(treatments)
reps <- length(levels(Cochran3_1.dat$Rep))
L.r <- matrix(rep(1,(reps-1)*treatments),nrow=treatments)
L.r <- L.r/(reps)
coeffs <- aocv.lm$coefficients
if(any(is.na(coeffs))) { coeffs[is.na(coeffs)] <- 0 }
cov.means <- rep(mean(Cochran3_1.dat$First),dim(C.t)[1])
L  <- cbind(rep(1,dim(C.t)[1]), cov.means, L.r, C.t)
trt.means <- L %*% coeffs
means.tbl <- data.frame(trt=as.integer(levels(Cochran3_1.dat$Trt)),arith=tapply(Cochran3_1.dat$Second, list(Cochran3_1.dat$Trt), mean),lsmean= trt.means)

L.contrasts <- NULL
for(i in 1:  (dim(L)[1]-1)) {
  for(j in (i+1):(dim(L)[1])) {
    L.contrasts <- rbind(L.contrasts, L[i,]-L[j,])
  }
}

Vcoeffs <- vcov(aocv.lm)
Sigma.m <- 1 / sqrt(diag(L.contrasts %*% Vcoeffs %*% t(L.contrasts)))
if(dim(L.contrasts)[1]>1) {
  Sigma <- diag(Sigma.m)
} else {
  Sigma <- Sigma.m
}
Sigma.m
t_ <- Sigma %*% L.contrasts %*% coeffs
Cor <- Sigma %*% (L.contrasts %*% Vcoeffs %*% t(L.contrasts)) %*% t(Sigma)
se.vec <- diag(L.contrasts %*% Vcoeffs %*% t(L.contrasts))
SE.table <- matrix(0,nrow=treatments,ncol=treatments)
se.idx <- 1
for (i in 1:(dim(L)[1]-1)) {
   for(j in (i+1):(dim(L)[1])) {
      SE.table[i,j] <- se.vec[se.idx]
      SE.table[j,i] <- se.vec[se.idx]
      se.idx <- se.idx + 1
   }
}

X <- alt.lm$x
alpha = 0.05
err.df <- aov.lm$df.residual
crit.t <-qtukey(1 - alpha / 2, treatments, err.df)
crit.tbl <- SE.table * crit.t
```


# Optimal Designs

Assume our analysis is based on solving 
$$
\hat{\beta} = (F^T F)^{-1} F^T y
$$

with

$$
var(\hat{\beta}) = \sigma^2 (F^T F)^{-1}
$$

where $F$ is the design matrix for the experiment.

D-optimal design maximizes $| F^T F |$, since this minimizes $\sigma^2 (F^T F)^{-1}$

A-optimal are less stringent - they minimize the average variance, or $trace((F^T F)^{-1})$
## 



```{r}
desplot(First~lon*lat, data=Cochran3_1.dat, cex=1, text=Trt,
        main="Initial Counts")
```


```{r}
Cochran3_1.dat$Unit <- 1
#lm1 <- lm(Unit ~ First,data=Cochran3_1.dat,x=TRUE)
#lm2 <- lm(Unit ~ Rep + Trt + First,data=Cochran3_1.dat,x=TRUE)
#lm3 <- lm(Unit ~ Rep + Trt + First + I(First^2),data=Cochran3_1.dat,x=TRUE)

lm1 <- lm(Second ~ Rep + Trt,data=Cochran3_1.dat,x=TRUE)
lm2 <- lm(Second ~ Rep + Trt + First,data=Cochran3_1.dat,x=TRUE)
lm3 <- lm(Second ~ Rep + Trt + First + I(First^2),data=Cochran3_1.dat,x=TRUE)
#lm3 <- lm(Second ~ Rep + Trt*First,data=Cochran3_1.dat,x=TRUE)
```

```{r}
aov1.tbl <- anova(lm1)
aov1.tbl
summary(lm1)
aov2.tbl <- anova(lm2)
summary(lm2)
aov2.tbl
aov3.tbl <- anova(lm3)
aov3.tbl
summary(lm3)
```

```{r}
X1 <- lm1$x
FtF1 <- t(X1)%*% X1
det(FtF1)
#det(FtF1)*aov1.tbl[3,3]

X2 <- lm2$x
FtF2 <- t(X2)%*% X2
det(FtF2)
solve(FtF2)

X3 <- lm3$x
FtF3 <- t(X3)%*% X3
det(FtF3)

sum(diag(FtF1))
sum(diag(FtF2))
sum(diag(FtF3))
```

# Adaptive randomization
```{r}
set.seed(1000)
Cochran3_1.dat$Rank <- rank(Cochran3_1.dat$First,ties.method = c("random"))
Cochran3_1.dat$PostBlock <- ceiling(Cochran3_1.dat$Rank/12)
Cochran3_1.dat[,c("Trt","Rep","Rank","PostBlock")]
Cochran3_1.dat$TreatmentRank <- 0
for(blk in 1:max(Cochran3_1.dat$PostBlock)) {
  Cochran3_1.dat$TreatmentRank[Cochran3_1.dat$PostBlock==blk] <- sample(1:12)
}
Cochran3_1.dat$TrtNoRank <- Cochran3_1.dat$TreatmentRank
Cochran3_1.dat$TreatmentRank <- as.factor(Cochran3_1.dat$TreatmentRank)
```

# Compare randomizations
Scale the data

```{r}
Cochran3_1.dat$FirstScaled <- Cochran3_1.dat$First/max(Cochran3_1.dat$First)
```

```{r}

max.sim <- 10
plans <- vector("list", max.sim)
res.tbl <- data.frame(
  D = rep(NA,max.sim),
  A = rep(NA,max.sim)
)

for (j in 1:max.sim) {
  Current.dat <- Cochran3_1.dat
  
  Current.dat$Trt <- as.factor(sample(levels(Current.dat$Trt))[Current.dat$Trt])
  lm.tmp <- lm(Second ~ 0 + Trt:First,data=Current.dat,x=TRUE)
  plans[[j]] <- Current.dat
  #hash.key <- ""

  
  X.tmp <- lm.tmp$x
  FtF.tmp <- t(X.tmp)%*% X.tmp
  print(diag(FtF.tmp))
  res.tbl$D[j] <- det(FtF.tmp)
  res.tbl$A[j] <- sum(diag(FtF.tmp))
}
res.tbl$D
plot(res.tbl$D/max(res.tbl$D))
plot(res.tbl$A/max(res.tbl$A))
```


# Optimal design in regression

```{r}
quantiles <- quantile(Cochran3_1.dat$FirstScaled, seq(0, 1, 1/4))
mid.points <- (quantiles[2:5]+quantiles[1:4])/2
mid.points
Cochran3_1.dat$FirstQ <- mid.points[Cochran3_1.dat$Rep]

uniform <- seq(min(Cochran3_1.dat$FirstScaled), max(Cochran3_1.dat$FirstScaled),(max(Cochran3_1.dat$FirstScaled)- min(Cochran3_1.dat$FirstScaled))/4)
uniform.points <- (uniform[2:5]+uniform[1:4])/2
Cochran3_1.dat$FirstU <- uniform.points[Cochran3_1.dat$Rep]

lm.S <- lm(Second ~ 0 + Trt:FirstScaled,data=Cochran3_1.dat,x=TRUE)
X.S <- lm.S$x
FtF.S <- t(X.S)%*% X.S
det(FtF.S)
sum(diag(FtF.S))

lm.R <- lm(Second ~ 0 + TreatmentRank:FirstScaled,data=Cochran3_1.dat,x=TRUE)
X.R <- lm.R$x
FtF.R <- t(X.R)%*% X.R
det(FtF.R)
sum(diag(FtF.R))

lm.Q <- lm(Second ~ 0 + Trt:FirstQ,data=Cochran3_1.dat,x=TRUE)

X.Q <- lm.Q$x
FtF.Q <- t(X.Q)%*% X.Q
det(FtF.Q)
sum(diag(FtF.Q))


lm.U <- lm(Second ~ 0 + Trt:FirstU,data=Cochran3_1.dat,x=TRUE)

X.U <- lm.U$x
FtF.U <- t(X.U)%*% X.U
det(FtF.U)
sum(diag(FtF.U))

```


```{r}
Cochran3_1.dat$TrtNo <- as.numeric(as.character((Cochran3_1.dat$Trt)))
plot(FirstScaled ~ TrtNo,data=Cochran3_1.dat,type='p',pch=19)
#points(FirstQ ~ TrtNo,data=Cochran3_1.dat,col='red')
#points(FirstU ~ TrtNo,data=Cochran3_1.dat,col='blue')
abline(h=uniform.points,col='blue')
abline(h=mid.points,col='red')
points(FirstScaled ~ TrtNoRank,data=Cochran3_1.dat,col='green')
```

