---
title: "Cochran 1947"
author: "Peter Claussen"
date: "10/3/2017"
output: html_document
---

```{r,echo=FALSE}
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000")
```

Spatial analysis of Cochran, 1947, in ARM table format:

```{r}
arm.dat <- data.frame(
plot=c(101, 804, 103, 503, 303, 801, 302, 803, 202, 701, 403, 504, 404, 802, 102, 602, 104, 501, 304, 604, 401, 703, 204, 702, 301, 601, 402, 603, 203, 704, 201, 502), 
treatment=as.factor(c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5, 6, 6, 7, 7, 8, 8, 9, 9, 10, 10, 11, 11, 12, 12, 13, 13, 14, 14, 15, 15, 16, 16)), 
replicate=as.factor(c(1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 2)), 
block=as.factor(c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)), 
column=as.factor(c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)), 
y=c(1, 4, 1, 1, 3, 4, 3, 4, 2, 3, 4, 1, 4, 4, 1, 2, 1, 1, 3, 2, 4, 3, 2, 3, 3, 2, 4, 2, 2, 3, 2, 1), 
x=c(1, 8, 3, 7, 3, 5, 2, 7, 2, 5, 3, 8, 4, 6, 2, 6, 4, 5, 4, 8, 1, 7, 4, 6, 1, 5, 2, 7, 3, 8, 1, 6), 
lat=c(3, 24, 3, 3, 17, 24, 17, 24, 10, 17, 24, 3, 24, 24, 3, 10, 3, 3, 17, 10, 24, 17, 10, 17, 17, 10, 24, 10, 10, 17, 10, 3), 
lon=c(2, 33.5, 11, 29, 11, 20, 6.5, 29, 6.5, 20, 11, 33.5, 15.5, 24.5, 6.5, 24.5, 15.5, 20, 15.5, 33.5, 2, 29, 15.5, 24.5, 2, 20, 6.5, 29, 11, 33.5, 2, 24.5), 
assessment1=c(1240, 640, 1770, 1410, 1460, 630, 1370, 560, 2180, 1680, 700, 1300, 810, 970, 1660, 1950, 1530, 1330, 1710, 1790, 840, 1890, 2280, 1580, 1480, 1910, 660, 1890, 2470, 1520, 1790, 1450)
)
arm.dat$block <- as.factor(arm.dat$y)
arm.dat$column<- as.factor(arm.dat$x)
```

Edited code from ARM

Calculate base (treatment only) model
```{r}
crd.lm <- lm(assessment1 ~ treatment, data=arm.dat,x=TRUE)
```

Calculate Neighbor residuals
```{r}
plots <- dim(arm.dat)[1]
cols <- max(arm.dat$x)
rows <- max(arm.dat$y)
mat.dim <- rows*cols
W.row <- matrix(rep(0, mat.dim*mat.dim),nrow = mat.dim)
W.col <- matrix(rep(0, mat.dim*mat.dim),nrow = mat.dim)
arm.dat$plot <- 1:plots
trial.map <- matrix(rep(0,mat.dim),nrow=rows)
for(p in 1:plots) {
  trial.map[arm.dat$y[p],arm.dat$x[p]] <- arm.dat$plot[p]
}
arm.dat$x.m <- arm.dat$x-1
arm.dat$x.p <- arm.dat$x+1
arm.dat$y.m <- arm.dat$y-1
arm.dat$y.p <- arm.dat$y+1
arm.dat$x.m[arm.dat$x.m<min(arm.dat$x)] <- NA
arm.dat$x.p[arm.dat$x.p>cols] <- NA
arm.dat$y.m[arm.dat$y.m<min(arm.dat$y)] <- NA
arm.dat$y.p[arm.dat$y.p>rows] <- NA
plot.width <- 6
plot.height <- 4
plot.buffer <- 0.5
row.buffer <- 1
col.space <- plot.width+plot.buffer
row.space <- plot.height+row.buffer
row.neighbors <- NA
for(p in 1:plots) {
  col.neighbors <- trial.map[c(arm.dat$y.m[p], arm.dat$y.p[p]), arm.dat$x[p]]
  row.neighbors <- trial.map[arm.dat$y[p], c(arm.dat$x.m[p],arm.dat$x.p[p])]
  W.row[p,row.neighbors] <- 1/col.space
  W.col[p,col.neighbors] <- 1/row.space
}
W <- W.col + W.row
W <- W[1:plots,1:plots]
row.sums <- rowSums(W)
row.sums[row.sums==0] <- 1
W <- W/row.sums
W.row <- W.row[1:plots,1:plots]
row.sums <- rowSums(W.row)
row.sums[row.sums==0] <- 1
W.row <- W.row/row.sums
W.col <- W.col[1:plots,1:plots]
row.sums <- rowSums(W.col)
row.sums[row.sums==0] <- 1
W.col <- W.col/row.sums
arm.dat$res <- NA
crd.res <- residuals(crd.lm)
arm.dat$res[as.numeric(names(crd.res))] <- crd.res
arm.dat$res[is.na(arm.dat$res)] <- 0
arm.dat$X.row = W.row %*% arm.dat$res
arm.dat$X.col = W.col %*% arm.dat$res
arm.dat$X = W %*% arm.dat$res
```

Compute design model
```{r}
arm.lm <- update(crd.lm, . ~ . + replicate )
```

Calculate and compare trend and neighbor models

```{r}
trend1.lm <- update(crd.lm, . ~ lat + lon + . )
trend2.lm <- update(crd.lm, . ~ lat + lon + I(lat^2) + I(lon^2) + I(lat*lon) + . )
trend3.lm <- update(crd.lm, . ~ lat + lon + I(lat^2) + I(lon^2) + I(lat*lon) + I(lat^3) + I(lon^3) + I(lat*lon^2) + I(lat^2*lon) + . )
nnx.lm <- update(crd.lm, . ~ X.col + . , data=arm.dat)
nny.lm <- update(crd.lm, . ~ X.row + . , data=arm.dat)
nnxy.lm <- update(crd.lm, . ~ X + . , data=arm.dat)
nns.lm <- update(crd.lm, . ~ X.row + X.col + . , data=arm.dat)
model.list <- list(crd.lm, arm.lm, nnx.lm, nny.lm, nnxy.lm, nns.lm, trend1.lm, trend2.lm, trend3.lm)
anova.tbl <- do.call(anova, model.list)
anova.tbl$RMS <- anova.tbl$RSS/anova.tbl$Res.Df
anova.tbl$AIC <- unlist(lapply(model.list, AIC))
anova.tbl$BIC <- unlist(lapply(model.list, BIC))
anova.tbl$logLik <- unlist(lapply(model.list, logLik))
best.tbl <- anova.tbl[, c('RMS', 'AIC', 'BIC', 'logLik')]
```

```{r}
best.aic <- which.min(anova.tbl$AIC)
best.bic <- which.min(anova.tbl$BIC)
best.rms <- which.min(anova.tbl$RMS)
best.tbl <- rbind(c(best.rms,best.aic,best.bic,0),best.tbl)
best.idx <- best.aic

arm.lm <- model.list[[best.idx]]
aov.tbl<-anova(arm.lm)
res.row <- dim(aov.tbl)[1]
print(aov.tbl)
coeffs.fix <- arm.lm$coefficients
na.coeffs.fix <- is.na(coeffs.fix)
if(any(na.coeffs.fix)) {
  coeffs.fix[na.coeffs.fix] <- 0 
}
if(any(na.coeffs.fix)) {
  idx<-which(na.coeffs.fix)
  aov.tbl <- rbind(aov.tbl[1:(idx-2),],rep(0,dim(aov.tbl)[2]),aov.tbl[-(1:(idx-2)),])
}
crd.tbl<-anova(crd.lm)
arith.means <- tapply(arm.dat$assessment1, list(arm.dat$treatment), mean, na.rm=TRUE)
valid.arith.means <- !is.na(arith.means)
arith.means <- arith.means[valid.arith.means]
trt.names <- as.numeric(levels(arm.dat$treatment)[valid.arith.means])
treatments <- length(arith.means)
C.t <- match.fun(arm.lm$contrasts[['treatment']])(treatments)
C.m <- rep(1,treatments)
L.fix <- NULL
  if(best.idx %in% c(3,4,5,6)) {
    cov.list <- NULL
    if(best.idx == 3) {
       cov.list <- c('X.col')
    } else if(best.idx == 4) {
       cov.list <- c('X.row')
    } else if(best.idx == 5) {
       cov.list <- c('X')
    } else if(best.idx == 6) {
       cov.list <- c('X.row', 'X.col')
    } 
    col.means <- colMeans(arm.dat[,cov.list])
    cov.means <- matrix(rep(col.means, treatments), nrow = treatments, byrow = TRUE)
    L.fix  <- cbind(C.m,cov.means,C.t)
} else {
  m.r <- (min(arm.dat$lat)+max(arm.dat$lat))/2
  m.c <- (min(arm.dat$lon)+max(arm.dat$lon))/2
  if (best.idx == 7) {
    C.trend <- c(1, m.r, m.c)
  } else if(best.idx == 8) {
    C.trend <- c(1, m.r, m.c, m.r^2, m.c^2, m.r*m.c)
  } else if(best.idx == 9) {
    C.trend <- c(1, m.r, m.c, m.r^2, m.c^2, m.r*m.c, m.r^3, m.c^3, m.r*m.c^2, m.r^2*m.c)
  }
  L.trend <- matrix(rep(C.trend,treatments),nrow=treatments, byrow=TRUE)
  L.fix <- cbind(L.trend,C.t)
}
if(best.idx %in% c(7,8,9)) {
  y.III.tbl <- anova(update(arm.lm, . ~ . - lat), arm.lm)
  x.III.tbl <- anova(update(arm.lm, . ~ . - lon), arm.lm)
  x.III.tbl <- rbind(y.III.tbl[2,], x.III.tbl[2,])
  if(best.idx %in% c(8,9)) {
    yy.III.tbl <- anova(update(arm.lm, . ~ . -  I(lat^2)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, yy.III.tbl[2,])
    xx.III.tbl <- anova(update(arm.lm, . ~ . -  I(lon^2)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, xx.III.tbl[2,])
    xy.III.tbl <- anova(update(arm.lm, . ~ . -  I(lat*lon)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, xy.III.tbl[2,])
  }
  if(best.idx == 9) {
    yyy.III.tbl <- anova(update(arm.lm, . ~ . -  I(lat^3)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, yyy.III.tbl[2,])
    xxx.III.tbl <- anova(update(arm.lm, . ~ . -  I(lon^3)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, xxx.III.tbl[2,])
    yxx.III.tbl <- anova(update(arm.lm, . ~ . -  I(lat*lon^2)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, yxx.III.tbl[2,])
    yyx.III.tbl <- anova(update(arm.lm, . ~ . -  I(lat^2*lon)), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, yyx.III.tbl[2,])
  }
} else {
  if(best.idx == 3) {
    x.III.tbl <- anova(update(arm.lm, . ~ . - X.col), arm.lm)[-1,]
  } else if(best.idx == 4) {
    x.III.tbl <- anova(update(arm.lm, . ~ . - X.row), arm.lm)[-1,]
  } else if(best.idx == 5) {
    x.III.tbl <- anova(update(arm.lm, . ~ . - X), arm.lm)[-1,]
  } else if(best.idx == 6) {
    x.III.tbl <- anova(update(arm.lm, . ~ . - X.row), arm.lm)[-1,]
    col.III.tbl <- anova(update(arm.lm, . ~ . -  X.col), arm.lm)
    x.III.tbl <- rbind(x.III.tbl, col.III.tbl[2,])
  }
}
  L <- L.fix
  na.coeffs <- na.coeffs.fix
  coeffs <- coeffs.fix
trt.means <- L %*% coeffs
means.tbl <- data.frame(trt= trt.names,arith=arith.means,lsmean= trt.means)
L.rows <- dim(L)[1]
L.contrasts <- matrix(0,nrow=((L.rows-1)*(L.rows)/2),ncol=dim(L)[2])
l.idx <- 1
for(i in 1:(L.rows-1)) {
  for(j in (i+1):L.rows) {
    L.contrasts[l.idx,] <- L[i,]-L[j,]
    l.idx <- l.idx+1
  }
}
L.contrasts <- L.contrasts[,!na.coeffs]
  Vcoeffs <- vcov(arm.lm)
LVL <- L.contrasts %*% Vcoeffs %*% t(L.contrasts)
se.vec <- diag(LVL)
SE.table <- matrix(0,nrow=treatments,ncol=treatments)
se.idx <- 1
for (i in 1:(L.rows-1)) {
   for(j in (i+1):L.rows) {
      SE.table[i,j] <- sqrt(se.vec[se.idx])
      SE.table[j,i] <- sqrt(se.vec[se.idx])
      se.idx <- se.idx + 1
   }
}
X <- crd.lm$x
alpha = 0.05
err.df <- arm.lm$df.residual
crit.t <-qt(1 - alpha / 2, err.df)
crit.tbl <- SE.table * crit.t
```


# Explanation of analysis

We start with the designed analysis of variance. This will be the second entry in `model.list`, the first is the treatment only (CRD) model.

```{r}
rcb.lm <- model.list[[2]]
anova(rcb.lm)
```

We will be creating an imaginary uniformity trial by calculating spatial effects and estimate plot yield as if only a single treatment where planted in each plot. We'll use the treatment with an arithmetic mean closest to the median of all treatments as our check for an imaginary uniformity trial.

```{r}
print(treatment.means <- tapply(arm.dat$assessment1,list(arm.dat$treatment),mean))
print(treatment.median <- median(treatment.means))
print(check.trt <-which.min(abs(treatment.means-treatment.median)))
```

This suggests why there's a need for spatial analysis - the median is an untreated treatment.

Now create a data frame for prediction
```{r}
pred.dat <- arm.dat[,c("plot","replicate", "y", "x", "lat", "lon","X.col","X.row","X")]
pred.dat$treatment <- levels(arm.dat$treatment)[which(levels(arm.dat$treatment)==check.trt)]
pred.dat$rcb <- predict(rcb.lm,pred.dat)

pred.dat$block <- as.factor(pred.dat$y)
pred.dat$column<- as.factor(pred.dat$x)
```

```{r}
library(agridat)
desplot(assessment1 ~ x+y, arm.dat, out1=replicate, out2=plot)
desplot(rcb ~ x+y, pred.dat, out1=replicate, out2=plot)
```



Add residuals to the table.
```{r}
pred.dat$CRDresid <- resid(crd.lm)
pred.dat$RCBresid <- resid(rcb.lm)
pred.dat$Trend1resid <- resid(trend1.lm)
pred.dat$Trend2resid <- resid(trend2.lm)
pred.dat$Trend3resid <- resid(trend3.lm)
pred.dat$Colresid <- resid(nnx.lm)
pred.dat$Rowresid <- resid(nny.lm)
pred.dat$RowColresid <- resid(nnxy.lm)
pred.dat$Papresid <- resid(nns.lm)
```

And a data frame for plotting residuals
```{r}
residuals.dat <- data.frame(
  Residual = c(pred.dat$CRDresid,
               pred.dat$RCBresid,
               pred.dat$Trend1resid,
               pred.dat$Trend2resid,
               pred.dat$Trend3resid,
               pred.dat$Colresid,
               pred.dat$Rowresid,
               pred.dat$RowColresid,
               pred.dat$Papresid),
  Model = c(rep("CRD",length(pred.dat$CRDresid)),
            rep("RCB",length(pred.dat$RCBresid)),
            rep("Trend1",length(pred.dat$Trend1resid)),
            rep("Trend2",length(pred.dat$Trend2resid)),
            rep("Trend3",length(pred.dat$Trend3resid)),
            rep("Col",length(pred.dat$Colresid)),
            rep("Row",length(pred.dat$Rowresid)),
            rep("RowCol",length(pred.dat$RowColresid)),
            rep("Pap",length(pred.dat$Papresid)))
)
```

```{r}
ggplot(residuals.dat, aes(sample=Residual,color=Model,linetype=Model)) + 
  stat_qq(aes(color=Model)) +
 #stat_density(geom="line",position="identity",size=1)
 # stat_ecdf(size=1)  +  #facet_wrap(~Source,scales = "free") + 
  scale_colour_manual(values=cbPalette) +
  labs(colour = "Model",x="Residuals")
```

```{r}
ggplot(pred.dat, aes(x, CRDresid)) + geom_point(aes(colour = block),size = 2) + geom_line(aes(colour = block)) + scale_colour_manual(values=cbPalette) 
#+ stat_smooth(aes(group=block,colour=block),method = "lm", formula = y ~ poly(x, 3), se=FALSE, size = 1)
  
# + labs(colour = "Yield (bu/acre)", x="Longitude (m)", y="Latitude (m)", title = "Sample Yield Monitor Data")
```

```{r}
ggplot(pred.dat, aes(x, CRDresid)) + geom_point(aes(colour = block),size = 3) + geom_line(aes(colour = block),size = 2) + scale_colour_manual(values=cbPalette) + facet_wrap(~block, nrow = 4)
```

```{r}
ggplot(pred.dat, aes(y, CRDresid)) + geom_point(aes(colour = block), size = 2) + stat_smooth(aes(group=block,colour=block),method = "lm", formula = x ~ poly(y, 3), se=FALSE, size = 1) + facet_wrap(~x, nrow = 4)
```

Compare residuals.

```{r}
qqnorm(trend1.lm$residuals)
qqnorm(trend2.lm$residuals)
qqnorm(trend3.lm$residuals)
qqnorm(nnx.lm$residuals)
qqnorm(nny.lm$residuals)
qqnorm(nnxy.lm$residuals)
qqnorm(nns.lm$residuals)
```

```{r}
ggplot(pred.dat, aes(x, Trend3resid)) + geom_point(aes(colour = block),size = 3) + geom_line(aes(colour = block),size = 2) + scale_colour_manual(values=cbPalette) + facet_wrap(~block, nrow = 4)
```

               
```{r}
ggplot(pred.dat, aes(x, RowColresid)) + geom_point(aes(colour = block),size = 3) + geom_line(aes(colour = block),size = 2) + scale_colour_manual(values=cbPalette) + facet_wrap(~block, nrow = 4)
```

```{r}
library(gridExtra)

row.dat <- subset(pred.dat,pred.dat$block==3)
row.dat <- subset(row.dat,row.dat$x<6)
#tbl12.3.row1 <- subset(tbl12.3.row1,tbl12.3.row1$rep==1)
row.dat <- row.dat[order(row.dat$x),]
midpoints <- data.frame(
  x = row.dat$x[2:4],
  y=c((row.dat$CRDresid[1]+row.dat$CRDresid[3])/2,
      (row.dat$CRDresid[2]+row.dat$CRDresid[4])/2,
      (row.dat$CRDresid[3]+row.dat$CRDresid[5])/2),
  lbl = c("covariate 2","covariate 3","covariate 4")
      )

```

<<row_poly,fig=TRUE,echo=false,width=6,height=7>>=
grid.arrange(
  arrangeGrob(
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ 1, se=FALSE, size = 1) ,
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x, se=FALSE, size = 1) ,
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x + I(x^2), se=FALSE, size = 1) ,
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x + I(x^2)+I(x^3), se=FALSE, size = 1),
nrow=4))
@

<<row_overfit,fig=TRUE,echo=false,width=6,height=7>>=
grid.arrange(
  arrangeGrob(
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x + I(x^2), se=FALSE, size = 1) ,
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x + I(x^2)+I(x^3), se=FALSE, size = 1) ,
ggplot(tbl12.3.row1, aes(x, resid)) + geom_point(colour = "black",size = 3) + stat_smooth(method = "lm", formula = y ~ x + I(x^2)+I(x^3)+I(x^4), se=FALSE, size = 1),
nrow=3))
@

```{r}
grid.arrange(
  arrangeGrob(
ggplot(row.dat, aes(x, CRDresid)) + geom_point(colour = "black",size = 3),
ggplot(row.dat, aes(x, CRDresid)) + geom_point(colour = "black",size = 3) + 
  geom_segment(x =row.dat$x[1], y = row.dat$CRDresid[1], xend = row.dat$x[3], yend = row.dat$CRDresid[3],linetype="dashed") +
  geom_segment(x =row.dat$x[2], y = row.dat$CRDresid[2], xend = row.dat$x[4], yend = row.dat$CRDresid[4],linetype="dashed") +
  geom_segment(x =row.dat$x[3], y = row.dat$CRDresid[3], xend = row.dat$x[5], yend = row.dat$CRDresid[5],linetype="dotted"),
  ggplot(row.dat, aes(x, CRDresid)) + geom_point(colour = "black",size = 3) + 
    geom_segment(x =row.dat$x[1], y = row.dat$CRDresid[1], xend = row.dat$x[3], yend = row.dat$CRDresid[3],linetype="dashed") +
    geom_segment(x =row.dat$x[2], y = row.dat$CRDresid[2], xend = row.dat$x[4], yend = row.dat$CRDresid[4],linetype="dashed") +
    geom_segment(x =row.dat$x[3], y = row.dat$CRDresid[3], xend = row.dat$x[5], yend = row.dat$CRDresid[5],linetype="dotted") + geom_text(data = midpoints, aes(x =x ,y = y, label = lbl))
      ))
```

<<>>=
library(nlme)
yield.gls <- gls(yield ~ trt,data=tbl12.3)

yield.lin.gls <- update(yield.gls, corr = corLin(form = ~ x + y))
yield.rat.gls <- update(yield.gls, corr = corRatio(form = ~ x + y,nugget=TRUE))
yield.sph.gls <- update(yield.gls, corr = corSpher(form = ~ x + y,nugget=TRUE))
yield.exp.gls <- update(yield.gls, corr = corExp(form = ~ x + y,nugget=TRUE))
yield.gaus.gls <- update(yield.gls, corr = corGaus(form = ~ x + y,nugget=TRUE))

comp.tbl <- anova(yield.lin.gls, yield.rat.gls, yield.sph.gls, yield.exp.gls, yield.gaus.gls)
corr.list <- list(yield.lin.gls, yield.rat.gls, yield.sph.gls, yield.exp.gls, yield.gaus.gls)
best.corr  <- corr.list[[which(comp.tbl$AIC==min(comp.tbl$AIC))]]
@

<<best_corr_variogram,fig=TRUE,echo=false,width=6,height=7>>=
plot(Variogram(best.corr, form = ~ x + y), main = "Variogram of Residuals")
@


