---
title: "What Do We Mean When We Say 'p'"
author: "Peter Claussen"
date: "5/27/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

The American Statistical Assocation released a position statement on the use of p-values in 2016, generally cautioning against the use of p-values. In 2019, the (other) ASA published as special issue, headlined by the editorial "Moving to a World Beyond 'p<0.05'".

In that context, we review Fisher's commentary on the meaning and use of probability, with regard to the interpretation of the null hypothesis in the context of on farm trials. How do Fisher's thoughts on statistical inference translate from small-plot experiments to large data-driven participatory trials, in a post p-value world? How does the introduction of spatial modeling change our understanding of p-value, when moving from small-plot to on farm trials?

```{r}
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```



# East Quarter

```{r}
load(file="../../2017/Workshop/Case Study 2/Strips.Rda")
```

```{r,fig.width=8,fig.height=4, EastQuarterProduct}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r}

#EastQuarter.dat$ObjId <- as.numeric(as.character(EastQuarter.dat$ObjId))
#EastQuarter.dat <- EastQuarter.dat[!is.na(EastQuarter.dat$ObjId),]
#EastQuarter.dat$Pass <- 1
#Pass <- 1
#for(i in 2:dim(EastQuarter.dat)[1]) {
#  if(EastQuarter.dat$ObjId[i] > (EastQuarter.dat$ObjId[i-1]+2)) {
#    Pass <- Pass + 1
#  }
#  EastQuarter.dat$Pass[i] <- Pass
#}
#EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
#levels(EastQuarter.dat$Pass)

EastQuarter.dat$Pass <- floor(EastQuarter.dat$Northing/6)+1
EastQuarter.dat$Pair <- floor((EastQuarter.dat$Pass+1)/2)
EastQuarter.dat$Direction <- "Easterly"
EastQuarter.dat$Direction[EastQuarter.dat$Heading>100] <- "Westerly"
EastQuarter.dat$Direction <- as.factor(EastQuarter.dat$Direction)

#EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] <- EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] + 400
EastQuarter.dat$PassNo <- EastQuarter.dat$Pass

EastQuarter.dat$Block <- ceiling(EastQuarter.dat$Pair/2)
EastQuarter.dat$Strip <- EastQuarter.dat$Pair %/% EastQuarter.dat$Block
EastQuarter.dat$Block <- as.factor(EastQuarter.dat$Block)
EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
EastQuarter.dat$Pair <- as.factor(EastQuarter.dat$Pair)
EastQuarter.dat$Strip <- as.factor(EastQuarter.dat$Strip)

```




```{r,fig.width=8,fig.height=4, EastQuarterPass}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pass),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pass", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```


```{r,fig.width=8,fig.height=4, EastQuarterPair}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pair),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pair", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterDirection}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Direction),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Direction", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterBlock}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Block),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Block", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterStrip}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Strip),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Strip", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

# One dimensional analysis

Strips as experimental units

```{r}
means.dat <- with(EastQuarter.dat, data.frame(
  Pass = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,1],
  Yield = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Product = aggregate(as.numeric(Product) ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Northing = aggregate(Northing ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2]
))
means.dat
means.dat$Product <- levels(EastQuarter.dat$Product)[means.dat$Product]
```

```{r}
ggplot(EastQuarter.dat, aes(x=Northing, y=Yield)) + 
geom_boxplot(aes(group=Pass,color=Product)) + geom_jitter(width = 0.2,size=0.2) +
scale_colour_manual(values=cbPalette) +
labs(colour = "Yield", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```



```{r}
ggplot(means.dat, aes(x=Northing, y=Yield, color=Product,fill=Product)) +
  geom_bar(stat="identity") + scale_colour_manual(values=cbPalette) + scale_fill_manual(values=cbPalette)
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Product, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Product,colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```





```{r}
#levels(as.factor(EastQuarter.dat$Swath))
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pair, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

## Smoothing

Assume that most error is sampling error, so we produce LOESS smoothed curves.
```{r}
Travel <- abs(EastQuarter.dat$Easting[2:dim(EastQuarter.dat)[1]] - EastQuarter.dat$Easting[1:(dim(EastQuarter.dat)[1]-1)])
hist(Travel)
Travel <- Travel[Travel<5]
hist(Travel)
mean(Travel)
```

Create a data frame of passes, one observation for every 2 meters, excluding ends
```{r}
LOESS.basis <- rep(seq(2,398,by=2))
total.passes <- max(EastQuarter.dat$PassNo)
Smoothed.dat <- data.frame(
  Yield = rep(0,total.passes*length(LOESS.basis)),
  Easting = rep(LOESS.basis,total.passes),
  PassNo = rep(1:total.passes,each=length(LOESS.basis)),
  Pair = rep(0,total.passes*length(LOESS.basis)),
  Product = rep(levels(EastQuarter.dat$Product),total.passes*length(LOESS.basis)/2),
  Northing = rep(0,total.passes*length(LOESS.basis))
)
#for(i in 1:max(EastQuarter.dat$PassNo)) {
for(i in 1:total.passes) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  current.loess <- loess(Yield ~ Easting,data=current.pass)
  current.smoothed <- predict(current.loess, data.frame(Easting = LOESS.basis))
  Smoothed.dat$Yield[Smoothed.dat$PassNo==i] <- current.smoothed
  Smoothed.dat$Pair[Smoothed.dat$PassNo==i] <- current.pass$Pair[1]
  Smoothed.dat$Product[Smoothed.dat$PassNo==i] <- current.pass$Product[1]
  Smoothed.dat$Northing[Smoothed.dat$PassNo==i] <- mean(current.pass$Northing)
}
Smoothed.dat$Pass <- as.factor(Smoothed.dat$PassNo)
```
```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```


```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r}
#head(EastQuarter.dat)
```


# Permutations
Possible combinations of pairs
$$
\frac{14!}{7!(14!-7!)}
$$
Lady tasting tea example:
```{r}
fac8 <- factorial(8)
fac4 <- factorial(4)
fac8/(fac4*fac4)
```

Note that
```{r}
2/70
```

```{r}
fac12 <- factorial(12)
fac6 <- factorial(6)

fac12/(fac6*fac6)
```

Note the relationship between rank sum permutations
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3111167/pdf/bjc2011157a.pdf

Iterating over each possible combination, 000000 111111 to 111111 000000

000000 111111
000001 011111
000010 011111
000100 011111

Modified from 
```{r}
binary <- function(x,digits=32) {
  i <- 0
  string <- rep(0,digits)
  while(x > 0) {
    string[digits - i] <- x %% 2
    x <- x %/% 2
    i <- i + 1 
  }
  string
}
```


```{r}
permutations <- fac12/(fac6*fac6)
randomizations <- matrix(0,nrow=permutations,ncol=12)
idx <- 1
for(i in 1:(2^12)) {
  trts <- binary(i,12)
  if(sum(trts) == 6) {
    randomizations[idx,] <- trts
    idx <- idx+1
  }
}
head(randomizations)
tail(randomizations)
```

```{r}
pair.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Pair),mean,na.rm=TRUE)
Strip <- 1:12
Product <- rep(c(1,0), 6)
summary(lm(pair.means ~ Strip))

#product.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Product),mean,na.rm=TRUE)
product.means <- tapply(pair.means,list(Product),mean,na.rm=TRUE)
product.means
product.sd <- tapply(pair.means,list(Product),sd,na.rm=TRUE)
product.sd
mean(pair.means)
sd(pair.means)

product.diff <- product.means[1]-product.means[2]
product.diff
```


Rememer that our $t$ statistic is

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sigma / \sqrt{n}}
$$

With two sd, we can write

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sqrt{\sigma^2_1/n_1 + \sigma^2_2/n_2}}
$$

```{r}
product.diff / sqrt(sum(product.sd^2/6))
```

```{r}
summary(aov(pair.means ~ as.factor(Product)))
qt(1-0.05/2,10)
```

```{r}
2*(1-pt(product.diff / sqrt(sum(product.sd^2/6)),10))
```

```{r}
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(pair.means,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=30)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



## Permuations by position

```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
Prob$Diff <- 0
Prob$SD <- 0
Prob$SE <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.sd <- tapply(obs$Yield,list(obs$Product),sd,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  Prob$Diff[i] <- product.diff
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  Prob$P[i] <- 2*sum(diffs>product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
  #Prob$SD[i] <- sd(pair.means)
  #pooled SD
  Prob$SD[i] <- sqrt(sum(product.sd^2)/2)
  Prob$SE[i] <- sqrt(sum(product.sd^2/6))
}
```

```{r}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") #+ylim(125, 275)
```



```{r,fig.width=8,fig.height=8}
#Prob$Z <- Prob$Diff/(Prob$SE/sqrt(6))
Prob$Z <- Prob$Diff/Prob$SE
Prob$PZ <- 2*(1-pt(Prob$Z,10))
par(mfrow=c(2,2))
plot(Diff ~ Easting,data=Prob,type='l',main='Treatment Differences')
plot(P ~ Easting,data=Prob,type='l',main='Probability')
lines(PZ ~ Easting,data=Prob,type='l',col='blue')
abline(h=0.05,col='red')
plot(SD ~ Easting,data=Prob,type='l',main='Standard Deviation')
plot(Z ~ Easting,data=Prob,type='l',main='t Value')
abline(h=qt(1-0.05/2,10),col='blue')
```

```{r}

```

```{r,fig.width=6,fig.height=9}
par(mfrow=c(3,1))
plot(P ~ SD,data=Prob)
plot(P ~ Diff,data=Prob)
plot(P ~ Z,data=Prob)
abline(h=0.05,col='red')
abline(v=qt(1-0.05/2,10),col='blue')
plot(P ~ PZ,data=Prob)
```



### From ISA

```{r}
Yield <- c(44.8,48.6,51.8,46.9,46.4,47.9,53.9,52.8,60.9,57.9,60.9,58.1)
Treatment <- c('Untreated','Priaxor','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated')
Strip <- 1:12
Pair <- as.factor(ceiling(Strip/2))
summary(lm(Yield ~ Strip))
```

using the lm permutation library
```{r}
library(lmPerm)
summary(aovp(Yield ~ Treatment))
summary(aovp(Yield ~ Treatment + Pair))
summary(aovp(Yield ~ Treatment + Pair,perm="Exact"))
```

We start using the same randomizations as our previous example - this assumes that any strip in the field could have been either untreated or Priaxor treated.

```{r}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```

In the event, strips were randomized in pairs. Thus, we have $2^n = 2^6 = 64$ possible randomizations. We recompute by

```{r}
randomizations <- matrix(0,nrow=64,ncol=12)
pair.trt <- matrix(c(0,1,1,0),nrow=2)
idx <- binary(3,6)
as.vector(t(pair.trt[idx+1,]))
for(i in 1:64) {
  idx <- binary(i-1,6)
  randomizations[i,] <- as.vector(t(pair.trt[idx+1,]))
}
colSums(randomizations)
rowSums(randomizations)
```

```{r}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  sum(diffs>=product.diff)
  Prob$P[i] <- 2*sum(diffs>=product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
}

plot(P ~ Easting,data=Prob)
abline(h=0.05,col='red')
```


# Functional

Create a matrix of passes, 1 row per second

```{r}
pass.length <- tapply(EastQuarter.dat$Yield, list(EastQuarter.dat$Pass),length)
pass.length
time.points <- max(pass.length)
time.points
pass.mat <- matrix(NA,nrow=time.points,ncol=max(EastQuarter.dat$PassNo))
for(i in 1:max(EastQuarter.dat$PassNo)) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  direction <- order(current.pass$Easting)
  pass.mat[1:dim(current.pass)[1],i] <- t(current.pass$Yield[direction])
}
```

First, we need to create a set of functions.  How many observations per pass?

```{r}

library(fda)
time <- 1:time.points
test.mat <- pass.mat[1:min(pass.length),1:12]
#passes.fda <- smooth.basisPar(argvals=time, y=pass.mat, lambda=1)
```

```{r}
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=40)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=400)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4000)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
```


```{r}

summary(aov(Yield ~ Product + Block+Pair+Pass,data= EastQuarter.dat))
library(nlme)
summary(lme(Yield ~ Product + Block, random = ~ 1 | Pass,data= EastQuarter.dat))
summary(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))

summary(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))

summary(aov(Yield ~ Block+Product + Error(Product:Block), data= EastQuarter.dat))
```

# Paired vs unpaired tests
https://en.wikipedia.org/wiki/Paired_difference_test


# Planning

Suppose we have a field where we might test strips, and that we have yield monitor data.

```{r}
load(file="../../2017/Workshop/Case Study 1/Pooled.Rda")
```

Corn2013.dat,Corn2015.dat,Soybean2014.dat,Soybean2016.dat

Trim between 50 and 350 
```{r}
uniformity.dat <- subset(Soybean2016.dat,Soybean2016.dat$Easting>50)
uniformity.dat <- subset(uniformity.dat,uniformity.dat$Easting<350)
uniformity.dat$Gap <- c(0,uniformity.dat$Seconds[2:dim(uniformity.dat)[1]] -uniformity.dat$Seconds[1:(dim(uniformity.dat)[1]-1)])
hist(uniformity.dat$Gap)
uniformity.dat$PassNo <- 0
Pass <- 1
head(uniformity.dat)
for(i in 1:dim(uniformity.dat)[1]) {
  if(uniformity.dat$Gap[i]>5) {
    Pass <- Pass+1
  }
  uniformity.dat$PassNo[i] <- Pass
}
#uniformity.dat$Pass <- as.factor(uniformity.dat$Pass)
```


```{r,fig.width=8,fig.height=4, UniformitySwath}
ggplot(uniformity.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = as.factor(PassNo)),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Swath", x="Longitude (m)", y="Latitude (m)", title = "Uniformity 2016")
```

```{r}
uniformity.dat <- uniformity.dat[!(uniformity.dat$PassNo %in% c(2,3,6,8,9,10)),]
```

```{r,fig.width=8,fig.height=4, UniformitySwathSubset}
uniformity.dat$Pass <- as.factor(uniformity.dat$Pass)
ggplot(uniformity.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = as.factor(Pass)),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Swath", x="Longitude (m)", y="Latitude (m)", title = "Uniformity 2016")
```


Repeat interpolation from part 1

```{r}
LOESS.basis <- rep(seq(min(uniformity.dat$Easting),max(uniformity.dat$Easting),by=2))
total.passes <- length(levels(uniformity.dat$Pass))
SmoothedU.dat <- data.frame(
  Yield = rep(0,total.passes*length(LOESS.basis)),
  Easting = rep(LOESS.basis,total.passes),
  PassNo = rep(levels(uniformity.dat$Pass),each=length(LOESS.basis)),
  Northing = rep(0,total.passes*length(LOESS.basis))
)

for(i in levels(uniformity.dat$Pass)) {
  current.pass <- uniformity.dat[uniformity.dat$Pass==i,]
  current.loess <- loess(Yield ~ Easting,data=current.pass)
  current.smoothed <- predict(current.loess, data.frame(Easting = LOESS.basis))
  SmoothedU.dat$Yield[SmoothedU.dat$PassNo==i] <- current.smoothed
  SmoothedU.dat$Northing[SmoothedU.dat$PassNo==i] <- mean(current.pass$Northing)
}
SmoothedU.dat$Pass <- as.factor(SmoothedU.dat$PassNo)
```

```{r}
ggplot(uniformity.dat,aes(Easting,Yield))+
  geom_point(aes(colour = Pass),size=.1) +
  #scale_colour_manual(values=cbPalette)+ 
  stat_smooth(aes(group=Pass, colour = Pass))+
  labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "Middle")
```

```{r}
ggplot(SmoothedU.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Pass),size=.2) + 
#scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "") #+  ylim(125, 275)
```

```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$SD <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- SmoothedU.dat[SmoothedU.dat$Easting==l,]
  product.sd <- sd(obs$Yield,na.rm=TRUE)
  Prob$SD[i] <- product.sd
}
Prob$R1 <- Prob$SD^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R2 <- (Prob$SD/4)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R3 <- (Prob$SD/8)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
```




```{r,fig.width=8,fig.height=8}
par(mfrow=c(2,1))
plot(SD ~ Easting, data=Prob)
plot(R1 ~ Easting, data=Prob,ylim=c(0,50),type='l')
lines(R2 ~ Easting, data=Prob,col='red')
lines(R3 ~ Easting, data=Prob,col='blue')
abline(h=6)
```



```{r}
SmoothedU.dat <- SmoothedU.dat[!(SmoothedU.dat$PassNo %in% c(1,4,19,20)),]
```


```{r}
ggplot(SmoothedU.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Pass),size=.2) + 
#scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "") #+  ylim(125, 275)
```

```{r}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$SD <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- SmoothedU.dat[SmoothedU.dat$Easting==l,]
  product.sd <- sd(obs$Yield,na.rm=TRUE)
  Prob$SD[i] <- product.sd
}
Prob$R1 <- Prob$SD^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R2 <- (Prob$SD/4)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R3 <- (Prob$SD/8)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
```




```{r,fig.width=8,fig.height=8}
par(mfrow=c(2,1))
plot(SD ~ Easting, data=Prob)
plot(R1 ~ Easting, data=Prob,ylim=c(0,20),type='l')
lines(R2 ~ Easting, data=Prob,col='red')
lines(R3 ~ Easting, data=Prob,col='blue')
abline(h=5)
```

# Two dimensions


References:
Comments on the Neyman–Fisher Controversy and Its Consequences
