---
title: "What Do We Mean When We Say 'p'"
author: "Peter Claussen"
date: "5/27/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

The American Statistical Assocation released a position statement on the use of p-values in 2016, generally cautioning against the use of p-values. In 2019, the (other) ASA published as special issue, headlined by the editorial "Moving to a World Beyond 'p<0.05'".

In that context, we review Fisher's commentary on the meaning and use of probability, with regard to the interpretation of the null hypothesis in the context of on farm trials. How do Fisher's thoughts on statistical inference translate from small-plot experiments to large data-driven participatory trials, in a post p-value world? How does the introduction of spatial modeling change our understanding of p-value, when moving from small-plot to on farm trials?


Statistical Methods for Researchers.
The arrangement of field experiments. ABBAABBA arrangement p 89.
What did Fisher mean by "inverse probability" in 1912--1922?
Comments on the Neyman–Fisher Controversy and Its Consequences

```{r}
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```

```{r}

arm.trt <- c(33.834, 25.741, 37.814, 29.72, 33.357, 25.263, 37.336, 29.243, 31.65, 23.556, 35.629, 27.536, 31.172, 23.079, 35.152, 27.059)
arm.unt <- c(27.059, 35.152, 23.079, 31.172, 27.536, 35.629, 23.556, 31.65, 29.243, 37.336, 25.263, 33.357, 29.72, 37.814, 25.741, 33.834)
arm.mean <- c(30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464, 30.4464)
arm.sd <- c(14.1292, 13.0837, 9.2464, 15.1271, 14.41, 12.5934, 10.1806, 15.0457, 15.0457, 10.1806, 12.5934, 14.41, 15.1271, 9.2464, 13.0837, 14.1292)
arm.diff <- c(6.7750, 9.4115, 14.7345, 1.4520, 5.8203, 10.3662, 13.7798, 2.4067, 2.4067, 13.7798, 10.3662, 5.8203, 1.4520, 14.7345, 9.4115, 6.7750)
arm.diff <- arm.trt - arm.unt
#arm.diff <- 9.4115 (31%), 14.7345 (48%), 1.4520 (4%), 5.8203 (19%), 10.3662 (34%), 13.7798 (45%), 2.4067 (7%), 2.4067 (7%), 13.7798 (45%), 10.3662 (34%), 5.8203 (19%), 1.4520 (4%), 14.7345 (48%), 9.4115 (31%), 6.7750 (22%))
arm.F <- c(0.46, 1.035, 5.079, 0.018, 0.326, 1.355, 3.664, 0.051, 0.051, 3.664, 1.355, 0.326, 0.018, 5.079, 1.035, 0.46)
arm.pF <- c(0.5463, 0.3839, 0.1096, 0.9006, 0.6078, 0.3285, 0.1515, 0.8356, 0.8356, 0.1515, 0.3285, 0.6078, 0.9006, 0.1096, 0.3839, 0.5463)
```

```{r}
hist(arm.diff)
hist(arm.F)
```


```{r}
arm.diff
diff.ranks <- length(arm.diff) - rank(arm.diff)+1
diff.ranks
(diff.ranks[1]-1)/length(diff.ranks)
abs.diff.ranks <- length(arm.diff) - rank(abs(arm.diff))+1
1-abs.diff.ranks[1]/length(abs.diff.ranks)
rank(arm.F)
rank(arm.F)[1]/length(arm.F)

t.value <- abs(arm.diff)/(arm.sd*sqrt(2/4))
t.value
p.t <- 2*(1-pt(t.value,df=3))
p.t
arm.pF
```

```{r}
arm.sd[1]
arm.diff[1]
quantiles <- seq(arm.diff[1]-4*arm.sd[1],arm.diff[1]+4*arm.sd[1],length=100)
t.dat <- data.frame(Quantile = quantiles, PDF = dt(quantiles,3))
norm.dat <- data.frame(Quantile = quantiles, PDF = dnorm(quantiles,mean=arm.diff[1],sd=arm.sd[1]))
norm.dat$CDF <- norm.dat$PDF
sum = norm.dat$PDF[1]

quantiles <- seq(0-4*arm.sd[1],0+4*arm.sd[1],length=100)
null.dat <- data.frame(Quantile = quantiles, PDF = dnorm(quantiles,mean=0,sd=arm.sd[1]))
null.dat$CDF <- null.dat$PDF
for(i in 2:length(quantiles)) {
  norm.dat$CDF <- norm.dat$CDF[i-1] +  norm.dat$PDF[i]
  null.dat$CDF <- null.dat$CDF[i-1] +  null.dat$PDF[i]
}
print(q.points <- c(0,arm.diff[1]))
print(l.points <- dnorm(q.points,mean=arm.diff[1],sd=arm.sd[1]))
shade.dat <- null.dat[abs(null.dat$Quantile) > arm.diff[1],]
shade2.dat <- null.dat[null.dat$Quantile > arm.diff[1],]
ggplot(norm.dat, aes(Quantile,PDF)) + 
geom_line(aes(color='L(y|mu,sigma)')) + 
  geom_line(aes(color='L(y|0,sigma)'),data=null.dat) + 
#labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
  geom_segment(aes(x = Quantile, y = 0, xend = Quantile, yend = PDF, colour = "P(>y)"), data = shade.dat) +
  geom_point(aes(x=arm.diff[1], y = l.points[2], colour = "L(MLE(y))")) +
   geom_point(aes(x=0, y = l.points[1], colour = "L(H0)")) +
scale_colour_manual(values=cbPalette)
l.points
#ggplot()
#pooled.dat <- rbind()
#plot(quantiles,dnorm(quantiles),col='gray',ylim=c(0,0.4),type='l')
#lines(quantiles,dt(quantiles,3),col='red')

#abline(v=c(t.value[1],-t.value[1]),col='blue')
```

```{r}
l.points[2]/l.points[1]
LR <- l.points[1]/l.points[2]
LR
-2*log(LR)
pchisq(LR,df=1)
```

```{r}

quantiles <- seq(-4,4,by=0.1)
t.dat <- data.frame(Quantile = quantiles, PDF = dt(quantiles,3))
norm.dat <- data.frame(Quantile = quantiles, PDF = dnorm(quantiles))
sum = 0
norm.dat$CDF <- norm.dat$PDF
sum = norm.dat$PDF[1]
for(i in 2:length(quantiles)) {
  norm.dat$CDF[i] <- norm.dat$CDF[i-1] +  norm.dat$PDF[i]
}
shade.dat <- norm.dat[abs(norm.dat$Quantile) > t.value[1],]
shade2.dat <- norm.dat[norm.dat$Quantile > t.value[1],]
ggplot(norm.dat, aes(Quantile,PDF)) + 
geom_line(color=cbPalette[1]) + 
#labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
  geom_segment(aes(x = Quantile, y = 0, xend = Quantile, yend = PDF, colour = "P(>t)"), data = shade.dat) +
  geom_point(aes(x = t.value[1], y = dnorm(t.value[1]), colour = "L(t)")) +
scale_colour_manual(values=cbPalette)
```


```{r}
norm.pdf <- function(y,mean,var) {
  n <- length(y)
  c1 <- 2 * pi * var
  c1 <- c1^(-n/2)
  ss <- (y-mean)^2
  return(c1*exp(-sum(ss/(2*var))))
}

quantiles <- seq(arm.diff[1]-4*arm.sd[1],arm.diff[1]+4*arm.sd[1],length=100)
dnorm(quantiles[1],mean=arm.diff[1],sd=arm.sd[1])
norm.pdf(quantiles[1],mean=arm.diff[1],var=arm.sd[1]^2)

control <-  c(5.511537,34.27445,37.97378,30.4757)
trt <- c(37.88459, 18.35549, 39.88316,39.21226)
diffs <- trt - control
sd(diffs)
norm.pdf(diffs,mean=arm.diff[1],var=arm.sd[1]^2)

#apply(quantiles,1,norm.pdf,var=arm.sd[1]^2)
#apply(quantiles,1,norm.pdf,y=diffs,var=arm.sd[1]^2)

norm.dat <- data.frame(Quantile = quantiles)
norm.dat$PDF <- 0
for(i in 1:length(quantiles)) {
  norm.dat$PDF[i] <- norm.pdf(diffs,mean=quantiles[i],var=arm.sd[1]^2)
}

norm.pdf(diffs,mean=arm.diff[1],var=arm.sd[1]^2)
norm.pdf(diffs,mean=0,var=arm.sd[1]^2)

ggplot(norm.dat, aes(Quantile,PDF)) + 
geom_line(aes(color='L(y|mu,sigma)')) + 
#  geom_line(aes(color='L(y|0,sigma)'),data=null.dat) + 
#labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
#  geom_segment(aes(x = Quantile, y = 0, xend = Quantile, yend = PDF, colour = "P(>y)"), data = shade.dat) +
#  geom_point(aes(x=arm.diff[1], y = l.points[2], colour = "L(MLE(y))")) +
#   geom_point(aes(x=0, y = l.points[1], colour = "L(H0)")) +
scale_colour_manual(values=cbPalette)

```


```{r}
arm.sd[1]
arm.diff[1]
quantiles <- seq(arm.diff[1]-4*arm.sd[1],arm.diff[1]+4*arm.sd[1],length=100)
t.dat <- data.frame(Quantile = quantiles, PDF = dt(quantiles,3))
norm.dat <- data.frame(Quantile = quantiles, PDF = dnorm(quantiles,mean=arm.diff[1],sd=arm.sd[1]))
norm.dat$CDF <- norm.dat$PDF
sum = norm.dat$PDF[1]

quantiles <- seq(0-4*arm.sd[1],0+4*arm.sd[1],length=100)
null.dat <- data.frame(Quantile = quantiles, PDF = dnorm(quantiles,mean=0,sd=arm.sd[1]))
null.dat$CDF <- null.dat$PDF
for(i in 2:length(quantiles)) {
  norm.dat$CDF[i] <- norm.dat$CDF[i-1] +  norm.dat$PDF[i]
  null.dat$CDF[i] <- null.dat$CDF[i-1] +  null.dat$PDF[i]
}
print(q.points <- c(0,arm.diff[1]))
print(l.points <- dnorm(q.points,mean=arm.diff[1],sd=arm.sd[1]))
shade.dat <- null.dat[abs(null.dat$Quantile) > arm.diff[1],]
shade2.dat <- null.dat[null.dat$Quantile > arm.diff[1],]
ggplot(norm.dat, aes(Quantile,PDF)) + 
geom_line(aes(color='L(y|mu,sigma)')) + 
  geom_line(aes(color='L(y|0,sigma)'),data=null.dat) + 
#
  geom_segment(aes(x = Quantile, y = 0, xend = Quantile, yend = PDF, colour = "P(>y)"), data = shade.dat) +
  geom_point(aes(x=arm.diff[1], y = l.points[2], colour = "L(MLE(y))")) +
   geom_point(aes(x=0, y = l.points[1], colour = "L(H0)")) +
scale_colour_manual(values=cbPalette) +
  labs(colour = "Function", x="y", y="Likelihood", title = "Likelihood Functions")
l.points
```

# East Quarter

```{r,eval=FALSE}
load(file="../../2017/Workshop/Case Study 2/Strips.Rda")
```

```{r,fig.width=8,fig.height=4, EastQuarterProduct,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,eval=FALSE}
#EastQuarter.dat$ObjId <- as.numeric(as.character(EastQuarter.dat$ObjId))
#EastQuarter.dat <- EastQuarter.dat[!is.na(EastQuarter.dat$ObjId),]
#EastQuarter.dat$Pass <- 1
#Pass <- 1
#for(i in 2:dim(EastQuarter.dat)[1]) {
#  if(EastQuarter.dat$ObjId[i] > (EastQuarter.dat$ObjId[i-1]+2)) {
#    Pass <- Pass + 1
#  }
#  EastQuarter.dat$Pass[i] <- Pass
#}
#EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
#levels(EastQuarter.dat$Pass)

EastQuarter.dat$Pass <- floor(EastQuarter.dat$Northing/6)+1
EastQuarter.dat$Pair <- floor((EastQuarter.dat$Pass+1)/2)
EastQuarter.dat$Direction <- "Easterly"
EastQuarter.dat$Direction[EastQuarter.dat$Heading>100] <- "Westerly"
EastQuarter.dat$Direction <- as.factor(EastQuarter.dat$Direction)

#EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] <- EastQuarter.dat$Pass[EastQuarter.dat$Heading>100] + 400
EastQuarter.dat$PassNo <- EastQuarter.dat$Pass

EastQuarter.dat$Block <- ceiling(EastQuarter.dat$Pair/2)
EastQuarter.dat$Strip <- EastQuarter.dat$Pair %/% EastQuarter.dat$Block
EastQuarter.dat$Block <- as.factor(EastQuarter.dat$Block)
EastQuarter.dat$Pass <- as.factor(EastQuarter.dat$Pass)
EastQuarter.dat$Pair <- as.factor(EastQuarter.dat$Pair)
EastQuarter.dat$Strip <- as.factor(EastQuarter.dat$Strip)

```




```{r,fig.width=8,fig.height=4, EastQuarterPass,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pass),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pass", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```


```{r,fig.width=8,fig.height=4, EastQuarterPair,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Pair),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Pair", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterDirection,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Direction),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Direction", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterBlock,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Block),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Block", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterStrip,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Strip),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Strip", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

# One dimensional analysis

Strips as experimental units

```{r,eval=FALSE}
means.dat <- with(EastQuarter.dat, data.frame(
  Pass = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,1],
  Yield = aggregate(Yield ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Product = aggregate(as.numeric(Product) ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2],
  Northing = aggregate(Northing ~ Pass,EastQuarter.dat,mean,na.rm=TRUE)[,2]
))
means.dat
means.dat$Product <- levels(EastQuarter.dat$Product)[means.dat$Product]
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(x=Northing, y=Yield)) + 
geom_boxplot(aes(group=Pass,color=Product)) + geom_jitter(width = 0.2,size=0.2) +
scale_colour_manual(values=cbPalette) +
labs(colour = "Yield", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```



```{r,eval=FALSE}
ggplot(means.dat, aes(x=Northing, y=Yield, color=Product,fill=Product)) +
  geom_bar(stat="identity") + scale_colour_manual(values=cbPalette) + scale_fill_manual(values=cbPalette)
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Product, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Product,colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```





```{r,eval=FALSE}
#levels(as.factor(EastQuarter.dat$Swath))
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(method=lm, formula = y ~ 1, aes(group=Pair, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pass, colour = Product),se=FALSE) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```

## Smoothing

Assume that most error is sampling error, so we produce LOESS smoothed curves.
```{r,eval=FALSE}
Travel <- abs(EastQuarter.dat$Easting[2:dim(EastQuarter.dat)[1]] - EastQuarter.dat$Easting[1:(dim(EastQuarter.dat)[1]-1)])
hist(Travel)
Travel <- Travel[Travel<5]
hist(Travel)
mean(Travel)
```

Create a data frame of passes, one observation for every 2 meters, excluding ends
```{r,eval=FALSE}
LOESS.basis <- rep(seq(2,398,by=2))
total.passes <- max(EastQuarter.dat$PassNo)
Smoothed.dat <- data.frame(
  Yield = rep(0,total.passes*length(LOESS.basis)),
  Easting = rep(LOESS.basis,total.passes),
  PassNo = rep(1:total.passes,each=length(LOESS.basis)),
  Pair = rep(0,total.passes*length(LOESS.basis)),
  Product = rep(levels(EastQuarter.dat$Product),total.passes*length(LOESS.basis)/2),
  Northing = rep(0,total.passes*length(LOESS.basis))
)
#for(i in 1:max(EastQuarter.dat$PassNo)) {
for(i in 1:total.passes) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  current.loess <- loess(Yield ~ Easting,data=current.pass)
  current.smoothed <- predict(current.loess, data.frame(Easting = LOESS.basis))
  Smoothed.dat$Yield[Smoothed.dat$PassNo==i] <- current.smoothed
  Smoothed.dat$Pair[Smoothed.dat$PassNo==i] <- current.pass$Pair[1]
  Smoothed.dat$Product[Smoothed.dat$PassNo==i] <- current.pass$Product[1]
  Smoothed.dat$Northing[Smoothed.dat$PassNo==i] <- mean(current.pass$Northing)
}
Smoothed.dat$Pass <- as.factor(Smoothed.dat$PassNo)
```
```{r,eval=FALSE}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r,eval=FALSE}
ggplot(EastQuarter.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Product),size=.2) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter")
```


```{r,eval=FALSE}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") +
  ylim(125, 275)
```


```{r,eval=FALSE}
#head(EastQuarter.dat)
```


# Permutations
Possible combinations of pairs
$$
\frac{14!}{7!(14!-7!)}
$$
Lady tasting tea example:
```{r}
fac8 <- factorial(8)
fac4 <- factorial(4)
fac8/(fac4*fac4)
```

Note that
```{r}
2/70
```

```{r}
fac12 <- factorial(12)
fac6 <- factorial(6)

fac12/(fac6*fac6)
```

Note the relationship between rank sum permutations
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3111167/pdf/bjc2011157a.pdf

Iterating over each possible combination, 000000 111111 to 111111 000000

000000 111111
000001 011111
000010 011111
000100 011111

Modified from 
```{r}
binary <- function(x,digits=32) {
  i <- 0
  string <- rep(0,digits)
  while(x > 0) {
    string[digits - i] <- x %% 2
    x <- x %/% 2
    i <- i + 1 
  }
  string
}
```


```{r}
permutations <- fac12/(fac6*fac6)
randomizations <- matrix(0,nrow=permutations,ncol=12)
idx <- 1
for(i in 1:(2^12)) {
  trts <- binary(i,12)
  if(sum(trts) == 6) {
    randomizations[idx,] <- trts
    idx <- idx+1
  }
}
head(randomizations)
tail(randomizations)
```

```{r,eval=FALSE}
pair.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Pair),mean,na.rm=TRUE)
Strip <- 1:12
Product <- rep(c(1,0), 6)
summary(lm(pair.means ~ Strip))

#product.means <- tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Product),mean,na.rm=TRUE)
product.means <- tapply(pair.means,list(Product),mean,na.rm=TRUE)
product.means
product.sd <- tapply(pair.means,list(Product),sd,na.rm=TRUE)
product.sd
mean(pair.means)
sd(pair.means)

product.diff <- product.means[1]-product.means[2]
product.diff
```


Rememer that our $t$ statistic is

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sigma / \sqrt{n}}
$$

With two sd, we can write

$$
t = \frac{\bar{y}_1 - \bar{y}_2}{\sqrt{\sigma^2_1/n_1 + \sigma^2_2/n_2}}
$$

```{r,eval=FALSE}
product.diff / sqrt(sum(product.sd^2/6))
```

```{r,eval=FALSE}
summary(aov(pair.means ~ as.factor(Product)))
qt(1-0.05/2,10)
```

```{r,eval=FALSE}
2*(1-pt(product.diff / sqrt(sum(product.sd^2/6)),10))
```

```{r,eval=FALSE}
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(pair.means,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=30)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



## Permuations by position

```{r,eval=FALSE}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
Prob$Diff <- 0
Prob$SD <- 0
Prob$SE <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.sd <- tapply(obs$Yield,list(obs$Product),sd,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  Prob$Diff[i] <- product.diff
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  Prob$P[i] <- 2*sum(diffs>product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
  #Prob$SD[i] <- sd(pair.means)
  #pooled SD
  Prob$SD[i] <- sqrt(sum(product.sd^2)/2)
  Prob$SE[i] <- sqrt(sum(product.sd^2/6))
}
```

```{r,eval=FALSE}
ggplot(Smoothed.dat, aes(Easting,Yield)) + 
#geom_point(aes(colour = Product),size=.1) + 
scale_colour_manual(values=cbPalette) + stat_smooth(aes(group=Pair, colour = Product)) +
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "East Quarter") #+ylim(125, 275)
```



```{r,fig.width=8,fig.height=8,eval=FALSE}
#Prob$Z <- Prob$Diff/(Prob$SE/sqrt(6))
Prob$Z <- Prob$Diff/Prob$SE
Prob$PZ <- 2*(1-pt(Prob$Z,10))
par(mfrow=c(2,2))
plot(Diff ~ Easting,data=Prob,type='l',main='Treatment Differences')
plot(P ~ Easting,data=Prob,type='l',main='Probability')
lines(PZ ~ Easting,data=Prob,type='l',col='blue')
abline(h=0.05,col='red')
plot(SD ~ Easting,data=Prob,type='l',main='Standard Deviation')
plot(Z ~ Easting,data=Prob,type='l',main='t Value')
abline(h=qt(1-0.05/2,10),col='blue')
```

```{r,eval=FALSE}

```

```{r,fig.width=6,fig.height=9,eval=FALSE}
par(mfrow=c(3,1))
plot(P ~ SD,data=Prob)
plot(P ~ Diff,data=Prob)
plot(P ~ Z,data=Prob)
abline(h=0.05,col='red')
abline(v=qt(1-0.05/2,10),col='blue')
plot(P ~ PZ,data=Prob)
```



### From ISA

```{r,eval=FALSE}
Yield <- c(44.8,48.6,51.8,46.9,46.4,47.9,53.9,52.8,60.9,57.9,60.9,58.1)
Treatment <- c('Untreated','Priaxor','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated','Priaxor','Untreated')
Strip <- 1:12
Pair <- as.factor(ceiling(Strip/2))
summary(lm(Yield ~ Strip))
```

using the lm permutation library
```{r,eval=FALSE}
library(lmPerm)
summary(aovp(Yield ~ Treatment))
summary(aovp(Yield ~ Treatment + Pair))
summary(aovp(Yield ~ Treatment + Pair,perm="Exact"))
```

We start using the same randomizations as our previous example - this assumes that any strip in the field could have been either untreated or Priaxor treated.

```{r,eval=FALSE}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```

In the event, strips were randomized in pairs. Thus, we have $2^n = 2^6 = 64$ possible randomizations. We recompute by

```{r,eval=FALSE}
randomizations <- matrix(0,nrow=64,ncol=12)
pair.trt <- matrix(c(0,1,1,0),nrow=2)
idx <- binary(3,6)
as.vector(t(pair.trt[idx+1,]))
for(i in 1:64) {
  idx <- binary(i-1,6)
  randomizations[i,] <- as.vector(t(pair.trt[idx+1,]))
}
colSums(randomizations)
rowSums(randomizations)
```

```{r,eval=FALSE}
product.means <- tapply(Yield,list(Treatment),mean,na.rm=TRUE)
product.diff <- product.means[1]-product.means[2]
permutations <- dim(randomizations)[1]
diffs <- rep(0,permutations)

for(i in 1:permutations) {
  means <- tapply(Yield,list(randomizations[i,]), mean)
  diffs[i] <- means[1] - means[2]
}
hist(diffs,breaks=32)
abline(v=product.diff,col='red')
sum(diffs>product.diff)
sum(diffs>product.diff)/length(diffs)
which.max(diffs)
product.diff
diffs[which.max(diffs)]
```



```{r,eval=FALSE}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$P <- 1
Prob$Max <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- Smoothed.dat[Smoothed.dat$Easting==l,]
  pair.means <- tapply(obs$Yield,list(obs$Pair),mean,na.rm=TRUE)
  product.means <- tapply(obs$Yield,list(obs$Product),mean,na.rm=TRUE)
  product.diff <- product.means[1]-product.means[2]
  diffs <- rep(0,permutations)

  for(j in 1:permutations) {
    means <- tapply(pair.means,list(randomizations[j,]), mean)
    diffs[j] <- means[1] - means[2]
  }
  sum(diffs>=product.diff)
  Prob$P[i] <- 2*sum(diffs>=product.diff)/length(diffs)
  Prob$Max[i] <- which.max(diffs)
}

plot(P ~ Easting,data=Prob)
abline(h=0.05,col='red')
```


# Functional

Create a matrix of passes, 1 row per second

```{r,eval=FALSE}
pass.length <- tapply(EastQuarter.dat$Yield, list(EastQuarter.dat$Pass),length)
pass.length
time.points <- max(pass.length)
time.points
pass.mat <- matrix(NA,nrow=time.points,ncol=max(EastQuarter.dat$PassNo))
for(i in 1:max(EastQuarter.dat$PassNo)) {
  current.pass <- EastQuarter.dat[EastQuarter.dat$PassNo==i,]
  direction <- order(current.pass$Easting)
  pass.mat[1:dim(current.pass)[1],i] <- t(current.pass$Yield[direction])
}
```

First, we need to create a set of functions.  How many observations per pass?

```{r,eval=FALSE}

library(fda)
time <- 1:time.points
test.mat <- pass.mat[1:min(pass.length),1:12]
#passes.fda <- smooth.basisPar(argvals=time, y=pass.mat, lambda=1)
```

```{r,eval=FALSE}
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=40)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=400)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
passes.fda <- smooth.basisPar(argvals=1:min(pass.length), y=test.mat, lambda=4000)
summary(passes.fda)
plot(passes.fda$fd, xlab="time", ylab="Yield",  main="Passes" )
```


```{r,eval=FALSE}

summary(aov(Yield ~ Product + Block+Pair+Pass,data= EastQuarter.dat))
library(nlme)
summary(lme(Yield ~ Product + Block, random = ~ 1 | Pass,data= EastQuarter.dat))
summary(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product*Block, random = ~ 1 | Pass,data= EastQuarter.dat))

summary(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))
anova(lme(Yield ~ Product, random = ~ 1 | Block/Pair/Pass,data= EastQuarter.dat))

summary(aov(Yield ~ Block+Product + Error(Product:Block), data= EastQuarter.dat))
```

# Paired vs unpaired tests
https://en.wikipedia.org/wiki/Paired_difference_test


# Planning

Suppose we have a field where we might test strips, and that we have yield monitor data.

```{r,eval=FALSE}
load(file="../../2017/Workshop/Case Study 1/Pooled.Rda")
```

Corn2013.dat,Corn2015.dat,Soybean2014.dat,Soybean2016.dat

Trim between 50 and 350 
```{r,eval=FALSE}
uniformity.dat <- subset(Soybean2016.dat,Soybean2016.dat$Easting>50)
uniformity.dat <- subset(uniformity.dat,uniformity.dat$Easting<350)
uniformity.dat$Gap <- c(0,uniformity.dat$Seconds[2:dim(uniformity.dat)[1]] -uniformity.dat$Seconds[1:(dim(uniformity.dat)[1]-1)])
hist(uniformity.dat$Gap)
uniformity.dat$PassNo <- 0
Pass <- 1
head(uniformity.dat)
for(i in 1:dim(uniformity.dat)[1]) {
  if(uniformity.dat$Gap[i]>5) {
    Pass <- Pass+1
  }
  uniformity.dat$PassNo[i] <- Pass
}
#uniformity.dat$Pass <- as.factor(uniformity.dat$Pass)
```


```{r,fig.width=8,fig.height=4, UniformitySwath,eval=FALSE}
ggplot(uniformity.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = as.factor(PassNo)),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Swath", x="Longitude (m)", y="Latitude (m)", title = "Uniformity 2016")
```

```{r,eval=FALSE}
uniformity.dat <- uniformity.dat[!(uniformity.dat$PassNo %in% c(2,3,6,8,9,10)),]
```

```{r,fig.width=8,fig.height=4, UniformitySwathSubset,eval=FALSE}
uniformity.dat$Pass <- as.factor(uniformity.dat$Pass)
ggplot(uniformity.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = as.factor(Pass)),size=2) + 
#scale_colour_manual(values=cbPalette) +
labs(colour = "Swath", x="Longitude (m)", y="Latitude (m)", title = "Uniformity 2016")
```


Repeat interpolation from part 1

```{r,eval=FALSE}
LOESS.basis <- rep(seq(min(uniformity.dat$Easting),max(uniformity.dat$Easting),by=2))
total.passes <- length(levels(uniformity.dat$Pass))
SmoothedU.dat <- data.frame(
  Yield = rep(0,total.passes*length(LOESS.basis)),
  Easting = rep(LOESS.basis,total.passes),
  PassNo = rep(levels(uniformity.dat$Pass),each=length(LOESS.basis)),
  Northing = rep(0,total.passes*length(LOESS.basis))
)

for(i in levels(uniformity.dat$Pass)) {
  current.pass <- uniformity.dat[uniformity.dat$Pass==i,]
  current.loess <- loess(Yield ~ Easting,data=current.pass)
  current.smoothed <- predict(current.loess, data.frame(Easting = LOESS.basis))
  SmoothedU.dat$Yield[SmoothedU.dat$PassNo==i] <- current.smoothed
  SmoothedU.dat$Northing[SmoothedU.dat$PassNo==i] <- mean(current.pass$Northing)
}
SmoothedU.dat$Pass <- as.factor(SmoothedU.dat$PassNo)
```

```{r,eval=FALSE}
ggplot(uniformity.dat,aes(Easting,Yield))+
  geom_point(aes(colour = Pass),size=.1) +
  #scale_colour_manual(values=cbPalette)+ 
  stat_smooth(aes(group=Pass, colour = Pass))+
  labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "Middle")
```

```{r,eval=FALSE}
ggplot(SmoothedU.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Pass),size=.2) + 
#scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "") #+  ylim(125, 275)
```

```{r,eval=FALSE}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$SD <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- SmoothedU.dat[SmoothedU.dat$Easting==l,]
  product.sd <- sd(obs$Yield,na.rm=TRUE)
  Prob$SD[i] <- product.sd
}
Prob$R1 <- Prob$SD^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R2 <- (Prob$SD/4)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R3 <- (Prob$SD/8)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
```




```{r,fig.width=8,fig.height=8,eval=FALSE}
par(mfrow=c(2,1))
plot(SD ~ Easting, data=Prob)
plot(R1 ~ Easting, data=Prob,ylim=c(0,50),type='l')
lines(R2 ~ Easting, data=Prob,col='red')
lines(R3 ~ Easting, data=Prob,col='blue')
abline(h=6)
```



```{r,eval=FALSE}
SmoothedU.dat <- SmoothedU.dat[!(SmoothedU.dat$PassNo %in% c(1,4,19,20)),]
```


```{r,eval=FALSE}
ggplot(SmoothedU.dat, aes(Easting,Yield)) + 
geom_point(aes(colour = Pass),size=.2) + 
#scale_colour_manual(values=cbPalette) + 
labs(colour = "Variety", x="Longitude (m)", y="Yield", title = "") #+  ylim(125, 275)
```

```{r,eval=FALSE}
Prob <- data.frame(
  Easting = LOESS.basis
)
Prob$SD <- 0
for(i in 1:length(LOESS.basis)) {
  l <- LOESS.basis[i]
  obs <- SmoothedU.dat[SmoothedU.dat$Easting==l,]
  product.sd <- sd(obs$Yield,na.rm=TRUE)
  Prob$SD[i] <- product.sd
}
Prob$R1 <- Prob$SD^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R2 <- (Prob$SD/4)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
Prob$R3 <- (Prob$SD/8)^2 * (qnorm(1-0.05/2)-qnorm(0.2))^2
```




```{r,fig.width=8,fig.height=8,eval=FALSE}
par(mfrow=c(2,1))
plot(SD ~ Easting, data=Prob)
plot(R1 ~ Easting, data=Prob,ylim=c(0,20),type='l')
lines(R2 ~ Easting, data=Prob,col='red')
lines(R3 ~ Easting, data=Prob,col='blue')
abline(h=5)
```

# Two dimensions


