---
title: "nonadditivity.gei"
author: "Peter Claussen"
date: "September 16, 2015"
output: html_document
---

```{r}
source("../R/gei.table.to.frame.R")
source("../R/nonadditivity.gei.R")
source("../R/heterogeneity.gei.R")
```

```{r}
sorghum.mat <- matrix(
  c(12.3, 19.6, 25.7, 30.4,
    13.7, 16.9, 27.0, 31.5,
    17.8, 20.0, 26.3, 35.9,
    12.1, 17.4, 36.9, 43.4,
    6.9, 18.8, 35.0, 53.0),
  nrow=5, byrow=TRUE
)
rownames(sorghum.mat) <- paste("T",as.character(c(5:9)*10),sep="")
colnames(sorghum.mat) <- paste("H",as.character(c(1:4)*20),sep="")

sorghum.dat <- gei.table.to.frame(sorghum.mat,GinRows=TRUE,TreatmentName="Treatment",TrialName="Trial")
```

```{r}
sorghum.het <- heterogeneity.gei(sorghum.dat,TreatmentName="Treatment",TrialName="Trial")
print.heterogeneity.gei(sorghum.het)
```

```{r}
options(contrasts = c("contr.SAS", "contr.poly"))
sorghum.het <- heterogeneity.gei(sorghum.dat,TreatmentName="Treatment",TrialName="Trial")
print.heterogeneity.gei(sorghum.het)
options(contrasts = c("contr.treatment", "contr.poly"))
```

### Test Statistic

Use the lm residual and d.f.

0.963562536*(sqrt((5-2)/(1-0.963562536)))
summary(aov(sorghum.het$heterogeneous.lm))
resid <- sorghum.het$heterogeneous.lm$residuals
sorghum.het$heterogeneous.lm$df.residual
var <- sum(resid*resid)
het.sd <- sqrt(var/sorghum.het$heterogeneous.lm$df.residual)
(het.sd/sqrt(sorghum.het$heterogeneous.lm$df.residual))
#(het.sd/sqrt(5))/??? = 0.155380043

2.23963177505/0.155380043
crit.t <- qt(1-0.025,sorghum.het$heterogeneous.lm$df.residual)

Let T= (mX - m0) / (S/sqrt(n)) where mX is the mean and S the sample standard deviation (sd) of X_1, X_2, …, X_n which are i.i.d.

mX <- -1.042596098
S <- het.sd
-1.042596098/(het.sd/sqrt(sorghum.het$heterogeneous.lm$df.residual))
TreatmentT50:eTrial  -1.042596098   0.155380043  -6.70997 0.00015114 ***
TreatmentT60:eTrial  -0.989684221   0.155380043  -6.36944 0.00021607 ***
TreatmentT70:eTrial  -1.023640287   0.155380043  -6.58798 0.00017152 ***
TreatmentT80:eTrial  -0.430384159   0.155380043  -2.76988 0.02430116 *  
  
