---
title: "Working with GIS data"
author: "Peter Claussen"
date: "2/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

There seems to be an explosion of players in the market offering digital agronomic services. At their core, many of these services are based on a single core task - integrating field map data with geogrophic and weather data to provide tools for planning and forecast. But what is the nature of these data, and how can they be integrated?

In this webinar, we use an example for our family farm to demonstrate integrating data geospatial data from the United States Geological Survey, the National Resource Conservation Service and the 
United States Fish and Wildlife Service with yield monitor data to answer a land management problem - are there low yield areas in section that should be allowed to revert to wetland or be replaced with grass waterways?

This webinar with demonstrate basic use of the open source software for GIS data QGIS, and discus the most common file formate - shapefiles - associated with GIS data.


Promise - Precision ag allows us to make very site-specific decisions about land management.
Opportunity - Yield monitor data is provided in GIS format, which allows give us access to a wealth of geological data
Challenge - GIS data set can be very large, require multiple files, are available from a variety of sources and are measured over range of scales.

The problem

# R libraries
```{r}
library(shapefiles)
```

# Region

From QGIS, we can determine the bounds of our area of interest
-97.611 - -97.592
44.082 - 44.096

From
44.082,-97.611 
44.096,-97.592
Create box from coordinates in TMN


# Imagery - NAIP Plus (1 meter to 1 foot)
 FSA 10:1 NAIP Imagery m_4409760_nw_14_1_20140813_20141113 3.75 x 3.75 minute JPEG2000 from The National Map
 
Landsat Explorer
http://landsatexplorer.esri.com


Google Earth Pro

Images titled MonthYear

#Scales

#Region
## Soils

soils_CRA_sd_3551929_09
soils_GSMCLIP_sd_3551929_07

#State
## Soils
gsmsoilmu_a_sd.shp
```{r}
path <- '~/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/wss_aoi_2018-08-09_17-22-37/spatial/soilmu_a_aoi'
soilmu_a_aoi <- read.shapefile(path)
library(maptools)
#shape <- readShapePoints(path)
shape <- readShapePoly(path)
#readShapePoly is deprecated; use rgdal::readOGR or sf::st_read
plot(shape)
```

```{r,SoilMapPlot}
library(rgdal)
#file.exists("~/Work/git/statistics/test_cases/claussen/Harvest/2016/Stevens Middle-Soybeans.shp")
ogrInfo("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/wss_aoi_2018-08-09_17-22-37/spatial/soilmu_a_aoi.shp")
ogrListLayers("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/wss_aoi_2018-08-09_17-22-37/spatial/soilmu_a_aoi.shp")
soilmu.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/wss_aoi_2018-08-09_17-22-37/spatial/soilmu_a_aoi.shp")
plot(soilmu.ogr)
```

wss_gsmsoil_SD_[2016-10-13]
##Geography
`geology_GEOLOGY_sd_3551929_01`
## Land Use
`land_use_land_cover_NASS_CDL_sd_3551929_04`

# Hydrographic Unit

`hydrologic_units_WBDHU12_sd097_3551929_02`

```{r,HydrographicUnitPlot}
wbdhu12.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/GDGOrder/hydrologic_units_WBDHU12_sd097_3551929_02/wbdhu12_a_sd097.shp")
plot(wbdhu12.ogr)
```


```{r,WatershedPlot}
watershed.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/HU8_10160011_Watershed/HU8_10160011_Watershed.shp")
plot(watershed.ogr)
```

## Flowline

```{r,FlowlinePlot}
#nhdflowline.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/NHD_H_10160011_HU8_Shape/NHDFlowline.shp")
#plot(nhdflowline.ogr)
```


```{r,ContourPlot}
#elev_contour.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/ELEV_Watertown_W_SD_1X1_Shape/Elev_Contour.shp")
#plot(elev_contour.ogr)
```


# Wetlands

```{r,WetlandsPlot}
#wetlands.ogr <- readOGR("/Users/peter/Work/git/statistics/design_documents/yield_monitor_data/webinar2018/HU8_10160011_Watershed/HU8_10160011_Wetlands.shp")
#plot(wetlands.ogr)
```
# Map Indexes

# County
soils_SSURGSDM_sd097_3551929_06
VECTOR_Howard_SD_7_5_Min_Shape
wss_aoi_2018-02-27_12-02-38

# Data

## Shapefile
Geometry - shp
Data - dbf
vector, raster, point

Convert line to point
 Vector > Geometry Tools > Extract Nodes
 https://gis.stackexchange.com/questions/225019/extracting-coordinates-from-line-shapefile/225116
 
## Yield Monitor Data


Topography

Elev_Contour
NHD_Flowline
Soil Map Units

Downloaded from https://viewer.nationalmap.gov/basic/#productSearch
USGS Topo Map Vector Data
Elev_Contour.shp

USGS National Hydrography Dataset (NHD) Best Resolution HU8-9 20180206 for HU-8 Subbasin Shapefile Model Version 2.2.1

https://gdg.sc.egov.usda.gov
https://gdg.sc.egov.usda.gov/GDGHome_DirectDownLoad.aspx

Soils
https://nrcs.app.box.com/v/soils/file/255251313287
SD097 - Miner County


Wetlands
https://www.fws.gov/wetlands/data/Data-Download.html

https://www.fws.gov/wetlands/data/mapper.html


https://www.nrcs.usda.gov/wps/portal/nrcs/surveylist/soils/survey/state/?stateId=SD
Survey from 1984
CfA - Clarno-Bonilla loams, 0-3% slope
Organic matter high in bonilla (IIc-3) , moderate in Clarno (IIe-2)

EgD - Ethan-Clarno, 9-15% slopes


Ethan soil is lower organic than Clarno, capability VIe-3
Clarno has moderate organic magtter, capability IVe-1


HdA Houdek-Dudley complex

Houdek - IIc-2, Dudley - IVs-2
Dudley - sodium affected subsoil, dense claypan

CkB - Clarno-Ethan complex

https://earthexplorer.usgs.gov/logout/expire

Land Capability Classes
http://resources.arcgis.com/en/communities/soils/02ms00000005000000.htm

Data sets (8/9/18)

From WSS
https://www.nrcs.usda.gov/wps/portal/nrcs/surveylist/soils/survey/state/?stateId=SD
wss_aoi_2018-08-09_17-22-37.zip
From John Deere
1533853561938
From
NRCS
SD097

From FWS

From TMN
VECTOR_Howard_SD_7_5_Min_Shape
NLCD2011_LC_South_Dakota
NHD_H_10160011_HU8_Shape
ELEV_Watertown_W_SD_1X1_Shape


Data Aggregators
https://www.agrible.com/


Other topics
Weather maps and real-time forecasts

