---
title: "ARM ST Analysis in R"
author: "Peter Claussen"
date: "November 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

We use ST-Intro as an example. The first step is to create an R data table. In the initial release, we exported to a data file and read from that file. More recently, as we've added additional R analysis, we instead embed the data in the R script.

```{r,eval=FALSE}
st.tab <- data.frame(
Trial=as.factor(c('A', 'A', 'A', 'A', 'A', 'A', 'A', 'A', 'A', 'A', 'A', 'A', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'B', 'C', 'C', 'C', 'C', 'C', 'C', 'C',
'C', 'C', 'C', 'C', 'C', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'D', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'E', 'F', 'F', 'F', 'F',
'F', 'F', 'F', 'F', 'F', 'F', 'F', 'F', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'G', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'H', 'I',
'I', 'I', 'I', 'I', 'I', 'I', 'I', 'I', 'I', 'I', 'I')), 
Treatment=as.factor(c(1, 2, 3, 4, 4, 3, 1, 2, 2, 1, 4, 3, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 2, 3, 4, 3, 1, 4, 2, 4, 3, 2, 1, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4)), 
RepNo=as.factor(c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3)), 
Plot.Mean=c(3.25, 3.16, 3.13, 3.22, 2.96, 2.99, 3.20, 2.71, 2.87, 2.69, 3.12, 2.87, 2.35, 2.25, 2.53, 2.10, 2.69, 2.15, 2.09, 2.15, 2.34, 2.67, 2.61, 2.45, 3.05, 3.07,
3.16, 3.24, 2.71, 3.03, 3.22, 3.23, 3.08, 3.05, 2.81, 3.13, 2.47, 2.41, 2.54, 2.39, 2.75, 2.55, 3.01, 2.65, 3.07, 2.60, 2.43, 2.20, 2.87, 2.97, 2.70, 2.47,
2.57, 2.76, 2.81, 3.06, 3.05, 2.74, 3.04, 3.21, 3.21, 3.30, 3.44, 2.93, 3.19, 3.05, 3.10, 3.37, 3.43, 3.46, 3.19, 3.70, 3.18, 3.13, 3.14, 2.65, 2.61, 2.75,
3.21, 2.67, 2.88, 3.01, 2.68, 2.64, 3.70, 3.38, 3.28, 3.12, 2.95, 3.05, 3.37, 3.42, 3.43, 3.27, 3.38, 3.74, 3.16, 2.29, 2.31, 2.37, 2.5, 2.66, 2.91, 2.52,
2.65, 2.49, 2.34, 2.51),
StyTreatment=as.factor(c(1, 2, 3, 4, 4, 3, 1, 2, 2, 1, 4, 3, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 2, 3, 4, 3, 1, 4, 2, 4, 3, 2, 1, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4)), 
CritTrtNo=as.factor(c(1, 2, 3, 4, 4, 3, 1, 2, 2, 1, 4, 3, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 2, 3, 4, 3, 1, 4, 2, 4, 3, 2, 1, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4))
)
st.tab$Trial <- as.factor(st.tab$Trial)
st.tab$Treatment <- as.factor(st.tab$Treatment)
st.tab$RepNo <- as.factor(st.tab$RepNo)
```

```{r,echo=FALSE}
st.tab <- data.frame(
Trial=as.factor(c('Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou',
'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou',
'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou',
'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Angaradebou', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi',
'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi',
'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi',
'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Badeggi', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda',
'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda',
'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda',
'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagauda', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou',
'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou',
'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Bagou', 'Ballah', 'Ballah',
'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah',
'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah',
'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'Ballah', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu',
'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu',
'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu',
'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu', 'BirninKudu',
'BirninKudu', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani',
'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani',
'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani', 'Dalabani',
'Dalabani', 'Dalabani', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa',
'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa',
'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damboa', 'Damongo', 'Damongo', 'Damongo',
'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo',
'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo',
'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Damongo', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja',
'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja',
'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja',
'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Danja', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba',
'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba',
'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba', 'Ejiba',
'Ejiba', 'Ejiba', 'Ejiba', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura',
'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura',
'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Ejura', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza',
'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza',
'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza',
'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Gwoza', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne',
'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne',
'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne',
'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1',
'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1',
'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne1',
'Ikenne1', 'Ikenne1', 'Ikenne1', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2',
'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2',
'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2', 'Ikenne2',
'Ikenne2', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin',
'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin',
'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ilorin', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina',
'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina',
'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Ina',
'Ina', 'Ina', 'Ina', 'Ina', 'Ina', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa',
'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa',
'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Kadawa', 'Katibougou',
'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou',
'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou',
'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou',
'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Katibougou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou',
'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou',
'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Ketou', 'Kishi',
'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi',
'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi',
'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Kishi', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa',
'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa',
'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa',
'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2',
'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2',
'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2', 'Mokwa2',
'Mokwa2', 'Mokwa2', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala',
'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala',
'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala',
'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Nyankpala', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi',
'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi',
'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi', 'Okeoyi',
'Okeoyi', 'Okeoyi', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka',
'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka',
'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka', 'Saminaka',
'Saminaka', 'Saminaka', 'Saminaka', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou',
'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou',
'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Sekou', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe',
'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe',
'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe',
'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tsafe', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu',
'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu',
'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Tumu', 'Wa', 'Wa',
'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa',
'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa', 'Wa',
'Wa', 'Wa', 'Wa', 'Wa', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako',
'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako',
'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Waminako',
'Waminako', 'Waminako', 'Waminako', 'Waminako', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria',
'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria',
'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1',
'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1',
'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1',
'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria1', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2',
'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2',
'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2',
'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zaria2', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru',
'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru',
'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru', 'Zuru')), 
Treatment=as.factor(c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16,
16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1,
1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2,
2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3,
3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4,
4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5,
5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6,
6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7,
7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8,
8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9,
9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10,
10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10,
11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11,
11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 13, 11, 12, 3, 6, 14, 10, 1, 2, 16, 15, 4, 8, 9, 5, 7, 1, 12, 13, 9, 5, 11, 8, 15, 7, 14, 3,
16, 4, 2, 6, 10, 4, 7, 2, 11, 6, 9, 12, 16, 5, 1, 15, 13, 14, 8, 10, 3, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13,
13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13,
14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14,
14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16)), 
RepNo=as.factor(c(1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1,
2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4,
1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3,
4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2,
3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1,
2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4,
1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3,
4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2,
3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1,
2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4,
1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3,
4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,
1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1,
2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4,
1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3,
4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4)),
Plot.Mean=c(4.26000022888184, 3.51999998092651, 3.41000008583069, 4.23999977111816, 3.72000002861023, 2.79999995231628, 3.91000008583069, 3.25, 4.38000011444092, 3.89000010490417, 3.47000002861023, 3.05999994277954, 3.90000009536743, 3.50999999046326, 3.40000009536743, 4.15000009536743, 3.86999988555908, 3.82999992370605, 3.20000004768372, 2.98000001907349, 4.38000011444092, 4.32000017166138, 4.55000019073486, 2.38000011444092, 3.90000009536743, 3.90000009536743,
3.88000011444092, 2.58999991416931, 4.32000017166138, 3.72000002861023, 3.80999994277954, 2.39000010490417, 6.05000019073486, 3.84999990463257, 3.57999992370605, 3.10999989509583, 6.48999977111816, 3.96000003814697, 4.26000022888184, 3.44000005722046, 4.59000015258789, 3.73000001907349, 4.09999990463257, 3.84999990463257, 4.5, 4.40000009536743, 3.07999992370605, 4.57999992370605, 4.61999988555908, 3.83999991416931, 2.25, 4.09000015258789, 3.96000003814697,
3.75, 3.20000004768372, 2.24000000953674, 4.21000003814697, 2.63000011444092, 4.1399998664856, 3.35999989509583, 5.88000011444092, 3.17000007629395, 3.48000001907349, 2.42000007629395, 3.05999994277954, 3.8199999332428, 4.17999982833862, 4.26999998092651, 3.76999998092651, 4.30999994277954, 3.51999998092651, 3.54999995231628, 1.25999999046326, 1.50999999046326, 1.87999999523163, 1.62999999523163, 2.00999999046326, 2.26999998092651, 2.02999997138977,
2.25, 3.08999991416931, 4.05000019073486, 3.52999997138977, 3.52999997138977, 3.11999988555908, 3.48000001907349, 3.36999988555908, 3.30999994277954, 3.71000003814697, 3.79999995231628, 4.07000017166138, 3.80999994277954, 3.11999988555908, 2.92000007629395, 3.34999990463257, 3.51999998092651, 3.89000010490417, 4.23999977111816, 4.21000003814697, 4.61999988555908, 3.5699999332428, 3.80999994277954, 3.84999990463257, 3.80999994277954, 2.88000011444092,
2.75999999046326, 3.11999988555908, 3.07999992370605, 3.76999998092651, 3.8199999332428, 3.84999990463257, 3.80999994277954, 3.73000001907349, 4.34999990463257, 3.80999994277954, 4.23000001907349, 1.25999999046326, 1.62000000476837, 1.61000001430511, 1.87999999523163, 6.01999998092651, 5.84000015258789, 5.6100001335144, 5.17999982833862, 1.60000002384186, 1.86000001430511, 1.50999999046326, 1.26999998092651, 3.26999998092651, 5.63000011444092, 4.17999982833862,
4, 4.19999980926514, 3.67000007629395, 5.09999990463257, 4.42999982833862, 2.75, 5.53000020980835, 3.99000000953674, 4.42999982833862, 2.11999988555908, 3.65000009536743, 4.94999980926514, 6.07000017166138, 5.34999990463257, 5.40999984741211, 4.8899998664856, 4.46000003814697, 2.44000005722046, 3.45000004768372, 2.25999999046326, 3.01999998092651, 2.84999990463257, 3.77999997138977, 3.25, 4.57999992370605, 3.86999988555908, 3.01999998092651, 6.3899998664856,
5.34999990463257, 5.98999977111816, 2.73000001907349, 3.21000003814697, 5.03999996185303, 5.34000015258789, 3.22000002861023, 4.69000005722046, 5.44999980926514, 2.72000002861023, 3.88000011444092, 5.90000009536743, 3.73000001907349, 6.6100001335144, 8.06999969482422, 3.89000010490417, 3.09999990463257, 3.40000009536743, 3.86999988555908, 1.80999994277954, 3.23000001907349, 3.40000009536743, 4.57999992370605, 3.33999991416931, 4.67999982833862, 2.16000008583069,
3.53999996185303, 3.95000004768372, 4.21000003814697, 3.07999992370605, 4.94999980926514, 4.71000003814697, 4.86999988555908, 1.75, 3.88000011444092, 2.69000005722046, 2.34999990463257, 2.57999992370605, 1.39999997615814, 2.33999991416931, 1.75999999046326, 1.6599999666214, 2.89000010490417, 4.67000007629395, 2.58999991416931, 2.91000008583069, 1.38999998569489, 2.59999990463257, 2.77999997138977, 1.85000002384186, 2.32999992370605, 1.4099999666214,
1.75, 2.25, 3.72000002861023, 3.38000011444092, 2.47000002861023, 2.47000002861023, 2.13000011444092, 2.09999990463257, 2.80999994277954, 2.9300000667572, 4.09999990463257, 2.9300000667572, 3.11999988555908, 2.79999995231628, 2.80999994277954, 2.80999994277954, 2.54999995231628, 2.10999989509583, 2.94000005722046, 3.25999999046326, 2.6800000667572, 2.33999991416931, 2.46000003814697, 4.1100001335144, 2.32999992370605, 4.11999988555908, 3.83999991416931,
2.79999995231628, 2.89000010490417, 1.75999999046326, 1.75, 1.8400000333786, 2.55999994277954, 1.75, 2.57999992370605, 2.46000003814697, 2.34999990463257, 2.98000001907349, 2.33999991416931, 2.23000001907349, 2.22000002861023, 1.63999998569489, 2.47000002861023, 2.08999991416931, 2.21000003814697, 1.32000005245209, .310000002384186, .939999997615814, 1.69000005722046, .699999988079071, .189999997615814, 1.08000004291534, .569999992847443, 1.69000005722046,
.259999990463257, .889999985694885, 1.01999998092651, 1.77999997138977, .5, .569999992847443, .889999985694885, .629999995231628, .629999995231628, .759999990463257, .709999978542328, 1.5900000333786, .629999995231628, 1.33000004291534, 1.21000003814697, .819999992847443, .449999988079071, 1.32000005245209, 1.62999999523163, 1.37999999523163, .189999997615814, 1.08000004291534, .680000007152557, .689999997615814, .689999997615814, 1.39999997615814,
1.82000005245209, 1.07000005245209, 1.19000005722046, 1.82000005245209, 1.50999999046326, 1.62999999523163, .689999997615814, .819999992847443, 1.12999999523163, 2.88000011444092, .379999995231628, 1.33000004291534, 1.74000000953674, .310000002384186, .629999995231628, .889999985694885, .629999995231628, .560000002384186, .259999990463257, .379999995231628, 1.64999997615814, 1.87999999523163, 1.1599999666214, 1.64999997615814, 1.07000005245209, 1,
.310000002384186, .769999980926514, 1.51999998092651, 1.38999998569489, 2.67000007629395, 2.73000001907349, 5.15000009536743, .360000014305115, 3.15000009536743, 2.1800000667572, 4.90999984741211, 3.75999999046326, 1.21000003814697, 1.82000005245209, 5.51999998092651, .239999994635582, 2.1800000667572, 2.11999988555908, 3.45000004768372, 2.42000007629395, .360000014305115, .239999994635582, 2.78999996185303, 3.64000010490417, 2.42000007629395, 1.63999998569489,
3.88000011444092, 0, 2.73000001907349, 1.45000004768372, 2.84999990463257, 3.94000005722046, 2.73000001907349, 2.35999989509583, 4.90999984741211, 4.48000001907349, 2.78999996185303, 2.54999995231628, 3.26999998092651, 3.94000005722046, 4.90999984741211, 3.15000009536743, 6.30000019073486, 3.88000011444092, 1.58000004291534, 1.45000004768372, 4.23999977111816, 2.67000007629395, 2.91000008583069, 2.05999994277954, 6.3600001335144, 2.24000000953674,
.479999989271164, 1.45000004768372, 6.23999977111816, 3.88000011444092, 1.51999998092651, .970000028610229, 2.29999995231628, 1.58000004291534, .970000028610229, .970000028610229, 3.39000010490417, 2.67000007629395, 1.45000004768372, 1.82000005245209, 2.42000007629395, 2.85999989509583, 4.76000022888184, 4.01000022888184, 4.05999994277954, 4.17999982833862, 2.70000004768372, 2.09999990463257, 2.57999992370605, 2.78999996185303, 4.15999984741211, 3.45000004768372,
2.28999996185303, 3.15000009536743, 2.38000011444092, 4.65000009536743, 4.30000019073486, 4.40999984741211, 3.32999992370605, 3.96000003814697, 3.22000002861023, .46000000834465, 1.30999994277954, 2.79999995231628, 3.3199999332428, 4.88000011444092, 3.64000010490417, 3.35999989509583, 4.13000011444092, 3.98000001907349, 2.01999998092651, 3.14000010490417, 2.70000004768372, 3.53999996185303, 5.15999984741211, 3.70000004768372, 3.60999989509583, 2,
6.19999980926514, 5.1399998664856, 1.83000004291534, 3.85999989509583, 5.36999988555908, 4.6100001335144, 2.74000000953674, 3.11999988555908, 5.17000007629395, 3.40000009536743, 6.09000015258789, 3.1800000667572, 2.48000001907349, 3.99000000953674, 3.04999995231628, 3.5699999332428, 3.19000005722046, 4.19999980926514, 5.01000022888184, 5.07999992370605, 4.23000001907349, 4.28000020980835, 3.27999997138977, .400000005960464, 2.00999999046326, 1.21000003814697,
4.05000019073486, .670000016689301, .850000023841858, .119999997317791, .239999994635582, .239999994635582, .119999997317791, 0, .180000007152557, .400000005960464, .180000007152557, .0599999986588955, 0, .850000023841858, .550000011920929, .0799999982118607, .850000023841858, .970000028610229, 1.45000004768372, 0, .910000026226044, 1.21000003814697, 0, .189999997615814, .0799999982118607, .479999989271164, 0, .790000021457672, .300000011920929, 1.0900000333786,
.479999989271164, .0599999986588955, .270000010728836, 1.75999999046326, .970000028610229, .0599999986588955, .550000011920929, 1.38999998569489, .550000011920929, 1.70000004768372, .300000011920929, 1.45000004768372, .239999994635582, 1.38999998569489, .119999997317791, 2.35999989509583, 0, .479999989271164, .360000014305115, .360000014305115, .360000014305115, .0799999982118607, .180000007152557, .0700000002980232, .300000011920929, .0799999982118607,
.0700000002980232, 1.33000004291534, .239999994635582, .270000010728836, .300000011920929, .550000011920929, 0, 0, .389999985694885, 3.74000000953674, 4.57999992370605, 4.09999990463257, 2.41000008583069, 3.10999989509583, 2.99000000953674, 2.40000009536743, 3.00999999046326, 3.70000004768372, 5.76000022888184, 3.92000007629395, 4.78000020980835, 4.17000007629395, 4.65999984741211, 3.41000008583069, 3.74000000953674, 3.02999997138977, 3.51999998092651,
2.1800000667572, 3.51999998092651, 3.26999998092651, 2.42000007629395, 2.78999996185303, 2.91000008583069, 3.25, 2.91000008583069, 4.48000001907349, 3.49000000953674, 5.15000009536743, 5.6399998664856, 5.40000009536743, 3.19000005722046, 4.40999984741211, 4.53999996185303, 5.51999998092651, 3.30999994277954, 5.11999988555908, 4.15000009536743, 5.73000001907349, 4.26999998092651, 4.15000009536743, 4.6100001335144, 4, 3.02999997138977, 4.11999988555908,
3.39000010490417, 3.85999989509583, 4.6100001335144, 3.90000009536743, 5.23999977111816, 4.51000022888184, 2.55999994277954, 2.99000000953674, 3.82999992370605, 4.82000017166138, 2.03999996185303, 4.73000001907349, 3.39000010490417, 3.75999999046326, 3.64000010490417, 1.70000004768372, 3.88000011444092, 3.15000009536743, 1.94000005722046, 1.21000003814697, .479999989271164, .730000019073486, .730000019073486, .119999997317791, 0, 0, 0, .119999997317791,
.850000023841858, .360000014305115, 1.58000004291534, .119999997317791, .239999994635582, .119999997317791, .479999989271164, 0, .610000014305115, 1.94000005722046, 1.21000003814697, .119999997317791, .730000019073486, .610000014305115, .119999997317791, .119999997317791, .529999971389771, .610000014305115, .970000028610229, .360000014305115, .360000014305115, 0, .239999994635582, 1.33000004291534, .730000019073486, .610000014305115, 1.82000005245209,
.479999989271164, .970000028610229, 1.33000004291534, .119999997317791, 0, .239999994635582, .239999994635582, .239999994635582, .850000023841858, 1.45000004768372, 3.02999997138977, 1.0900000333786, .119999997317791, 1.0900000333786, .360000014305115, .119999997317791, .239999994635582, 0, .970000028610229, .850000023841858, .479999989271164, .119999997317791, .239999994635582, .119999997317791, 0, .360000014305115, 0, 1.45000004768372, 2.34999990463257,
2.24000000953674, 2.03999996185303, 1.73000001907349, 1.61000001430511, 2.23000001907349, 2.21000003814697, 1.89999997615814, 1.91999995708466, 1.61000001430511, 1.50999999046326, 2.50999999046326, 2, 3.02999997138977, 1.12000000476837, 2.09999990463257, 1.67999994754791, 2.13000011444092, 1.82000005245209, 1.82000005245209, 2.39000010490417, 1.19000005722046, 2.58999991416931, 2.33999991416931, 1.70000004768372, 2, 1.82000005245209, 1.92999994754791,
2.20000004768372, 2.33999991416931, 2.78999996185303, 1.9099999666214, 3.21000003814697, 2.5, 1.89999997615814, 1.79999995231628, 3.17000007629395, 2.02999997138977, 2.28999996185303, 1.71000003814697, 2.09999990463257, 1.9099999666214, 2, 1.9099999666214, 2.30999994277954, 2.5, 2.08999991416931, 1.21000003814697, 2.19000005722046, 1.99000000953674, 1.83000004291534, 1.78999996185303, 1.91999995708466, 2.28999996185303, 1.80999994277954, 2.3199999332428,
1.71000003814697, 2.02999997138977, 1.79999995231628, 1.70000004768372, 2.36999988555908, 2.19000005722046, 2.51999998092651, 1.30999994277954, 4.6399998664856, 6.55000019073486, 3.78999996185303, 2.30999994277954, 4.65999984741211, 3.32999992370605, 3.53999996185303, 3.33999991416931, 5.1100001335144, 4.55999994277954, 2.5, 3.53999996185303, 4.90999984741211, 3.69000005722046, 6.23999977111816, 4.34000015258789, 4.03000020980835, 3.63000011444092,
1.79999995231628, 1.92999994754791, 3.91000008583069, 2.48000001907349, 3.54999995231628, 2.40000009536743, 5.07999992370605, 3.79999995231628, 3.11999988555908, 4.84000015258789, 3.40000009536743, 3.89000010490417, 3.47000002861023, 2.80999994277954, 5.57999992370605, 3.41000008583069, 3.54999995231628, 4.80000019073486, 3.86999988555908, 4.15000009536743, 4.6399998664856, 4.30000019073486, 5.73000001907349, 3.27999997138977, 4.05999994277954, 4.69000005722046,
5.13000011444092, 2.44000005722046, 5.17000007629395, 3.03999996185303, 4.73999977111816, 4.5, 4.53999996185303, 4.92000007629395, 3.94000005722046, 4.78000020980835, 2.89000010490417, 3.97000002861023, 3.94000005722046, 3.32999992370605, 2.60999989509583, 5.59000015258789, 2.86999988555908, 3.58999991416931, 2.83999991416931, 2.59999990463257, 1.14999997615814, .730000019073486, 1.45000004768372, 1.21000003814697, 1.51999998092651, .479999989271164,
.670000016689301, .610000014305115, 1.87999999523163, 2.05999994277954, .850000023841858, .239999994635582, .910000026226044, .419999986886978, 1.33000004291534, .239999994635582, 1.33000004291534, .730000019073486, 1.0900000333786, 2.29999995231628, .670000016689301, 1.87999999523163, .180000007152557, .550000011920929, .730000019073486, .419999986886978, 1.26999998092651, .419999986886978, 1.0900000333786, .629999995231628, .970000028610229, .730000019073486,
1.58000004291534, .550000011920929, 1.70000004768372, 2.42000007629395, 1.82000005245209, .790000021457672, 1.26999998092651, .910000026226044, .970000028610229, .610000014305115, 1.45000004768372, .790000021457672, .610000014305115, 1.75999999046326, 2.67000007629395, 1.21000003814697, 1.26999998092651, .239999994635582, 1.02999997138977, 1.26999998092651, 1.63999998569489, .119999997317791, 1.26999998092651, .479999989271164, 3.75999999046326, 1.94000005722046,
.850000023841858, .850000023841858, .479999989271164, 2.24000000953674, 2.11999988555908, 2, 3.97000002861023, 3.70000004768372, 3.19000005722046, 4.26000022888184, 3.54999995231628, 3.27999997138977, 4.03999996185303, 4.48999977111816, 4.98000001907349, 5.28999996185303, 3.67000007629395, 3.76999998092651, 4.30000019073486, 4.13000011444092, 4.30999994277954, 4.80000019073486, 2.46000003814697, 2.45000004768372, 1.98000001907349, 4, 4.44000005722046,
4.23999977111816, 3.84999990463257, 3.75999999046326, 3.17000007629395, 4.21000003814697, 3.50999999046326, 3.66000008583069, 4.28999996185303, 4.34999990463257, 4.84999990463257, 5.8600001335144, 4.17000007629395, 4.23999977111816, 4.34999990463257, 4.8899998664856, 4.57000017166138, 2.71000003814697, 4.3899998664856, 4.42999982833862, 4.69000005722046, 5.23000001907349, 4.28000020980835, 5.23999977111816, 5.48000001907349, 5.40000009536743, 4.71999979019165,
3.90000009536743, 4.1100001335144, 4.3899998664856, 3.0699999332428, 3.63000011444092, 3.64000010490417, 5.46000003814697, 5.09000015258789, 3.95000004768372, 3.45000004768372, 4.07000017166138, 3.60999989509583, 3.25, 4.59999990463257, 4.23999977111816, 4.05999994277954, 4.65999984741211, 1.10000002384186, 2.42000007629395, 2.58999991416931, 2.91000008583069, 2.00999999046326, 1.69000005722046, 2.75999999046326, 2.08999991416931, 2.98000001907349,
2.96000003814697, 3.53999996185303, 2.78999996185303, 2.91000008583069, 2.70000004768372, 2.52999997138977, 3.25, 2.0699999332428, 1.97000002861023, 1.5900000333786, 1.85000002384186, 2.30999994277954, 2.44000005722046, 2.41000008583069, 1.89999997615814, 2.67000007629395, 2.39000010490417, 2.92000007629395, 3.16000008583069, 2.57999992370605, 2.41000008583069, 3.54999995231628, 3.11999988555908, 3.54999995231628, 3.48000001907349, 3.05999994277954,
3.1800000667572, 2.65000009536743, 2.64000010490417, 3.3199999332428, 2.86999988555908, 3.44000005722046, 2.27999997138977, 3.13000011444092, 3.96000003814697, 3.46000003814697, 2.5699999332428, 4.07999992370605, 3.26999998092651, 2.53999996185303, 3, 3.02999997138977, 3.02999997138977, 2.90000009536743, 3.00999999046326, 2.50999999046326, 3.23000001907349, 2.14000010490417, 3.01999998092651, 3.46000003814697, 2.79999995231628, 2.83999991416931, 1.61000001430511,
.959999978542328, 2.30999994277954, .5, 1.88999998569489, .980000019073486, 1.14999997615814, .610000014305115, .959999978542328, 1.17999994754791, 1.19000005722046, 1.61000001430511, 1.10000002384186, .759999990463257, 1.1599999666214, 1.29999995231628, .860000014305115, .779999971389771, 1.92999994754791, .689999997615814, .779999971389771, .610000014305115, 1.46000003814697, 1.10000002384186, 1.54999995231628, 1.25999999046326, 1.60000002384186,
.899999976158142, 1.97000002861023, 1.27999997138977, 1.51999998092651, 1.17999994754791, 1.45000004768372, 1.37000000476837, 1.39999997615814, 1.20000004768372, .970000028610229, .850000023841858, 1.53999996185303, 1.03999996185303, 1.47000002861023, 1.86000001430511, 1.9099999666214, 1.46000003814697, 1.63999998569489, 1.25, 1.36000001430511, 1.14999997615814, 1.6599999666214, 1.24000000953674, 1.48000001907349, 1.14999997615814, .850000023841858,
.449999988079071, 1.52999997138977, .769999980926514, .790000021457672, .870000004768372, 1.00999999046326, .740000009536743, 1.11000001430511, .970000028610229, 1.25, 1.13999998569489, 1.00999999046326, .740000009536743, 1.32000005245209, 2.82999992370605, 4.19999980926514, 1.85000002384186, 5.30000019073486, 3.3199999332428, 1.5, 6, 3.91000008583069, 4.46000003814697, 5.40000009536743, 5.15999984741211, 4.3899998664856, 2.42000007629395, 3.89000010490417,
4.57000017166138, 7.38000011444092, 2.92000007629395, 1.64999997615814, 2.47000002861023, 5.67999982833862, 3.65000009536743, .419999986886978, 4.40000009536743, 6.76000022888184, 2.60999989509583, 2.46000003814697, 3.25999999046326, 4.80999994277954, 4.57999992370605, 2.3199999332428, 7.44000005722046, 7.76000022888184, 6.1399998664856, 6.40000009536743, 4.98999977111816, 8.05000019073486, 6.28000020980835, 4.82000017166138, 7.03000020980835, 7.78999996185303,
3.92000007629395, 5.23999977111816, 5.23999977111816, 3.60999989509583, 3.30999994277954, 2.84999990463257, 4.57000017166138, 6.05000019073486, 6.48000001907349, 3.52999997138977, 2.39000010490417, 7.21999979019165, .670000016689301, 3, 5.26000022888184, 3.24000000953674, 4.65000009536743, 2.95000004768372, 4.73999977111816, 5.36999988555908, 4.44000005722046, 3.88000011444092, 4.55000019073486, 4.90999984741211, 4.28999996185303, 4.71000003814697,
4.23999977111816, 4.38000011444092, 5.01000022888184, 4.07999992370605, 4.09999990463257, 4.3899998664856, 4.03000020980835, 5.1399998664856, 4.42999982833862, 4.17999982833862, 4.82000017166138, 4.46000003814697, 4.13000011444092, 2.89000010490417, 3.79999995231628, 3.99000000953674, 4.05000019073486, 3.86999988555908, 3.92000007629395, 4.73000001907349, 4.63000011444092, 3.32999992370605, 3.79999995231628, 3.71000003814697, 2.60999989509583, 4.63000011444092,
3.84999990463257, 5.01999998092651, 4.28000020980835, 4.71000003814697, 5.96000003814697, 5.28999996185303, 5.13000011444092, 3.70000004768372, 5.1399998664856, 4.96999979019165, 5.71999979019165, 3.92000007629395, 4.32000017166138, 5.90000009536743, 4.75, 3.54999995231628, 4, 5.23000001907349, 4.55000019073486, 5.26999998092651, 4.53000020980835, 4.48000001907349, 4.19000005722046, 4.1100001335144, 4.03000020980835, 3.73000001907349, 3.35999989509583,
3.70000004768372, 3.9300000667572, 3.94000005722046, 4.82999992370605, 4.76000022888184, 4.96000003814697, 5.53999996185303, 3.94000005722046, 5.6399998664856, 3.02999997138977, 4.11999988555908, 4.48000001907349, 3.02999997138977, 2.67000007629395, 2.42000007629395, 3.64000010490417, 3.26999998092651, 3.39000010490417, 4.73000001907349, 4.3600001335144, 4.48000001907349, 4.6100001335144, 3.39000010490417, 3.64000010490417, 3.02999997138977, 3.64000010490417,
3.15000009536743, 3.02999997138977, 4.3600001335144, 1.21000003814697, 3.15000009536743, 1.94000005722046, 3.39000010490417, 2.67000007629395, 2.91000008583069, 2.67000007629395, 2.42000007629395, 2.42000007629395, 3.02999997138977, 4.3600001335144, 4.48000001907349, 3.02999997138977, 4.84999990463257, 3.15000009536743, 4.48000001907349, 3.39000010490417, 4.6100001335144, 3.51999998092651, 5.09000015258789, 3.64000010490417, 4.3600001335144, 4.48000001907349,
2.78999996185303, 1.94000005722046, 3.39000010490417, 3.15000009536743, 4.48000001907349, 3.02999997138977, 3.64000010490417, 4.48000001907349, 2.67000007629395, 4.23999977111816, 3.88000011444092, 3.88000011444092, 1.94000005722046, 3.39000010490417, 3.02999997138977, 4.73000001907349, 3.15000009536743, 1.45000004768372, .970000028610229, 3.64000010490417, 5.44999980926514, 3.36999988555908, 3.05999994277954, 4, 1.3400000333786, 5.28999996185303,
2.83999991416931, 2.3199999332428, 2.27999997138977, 3.22000002861023, 4.92999982833862, 3.98000001907349, 2.5, 2.88000011444092, 3.67000007629395, 3.41000008583069, 4.07999992370605, 5.25, 2.07999992370605, 3, 3.03999996185303, 3.76999998092651, 3.46000003814697, 3.22000002861023, 2.59999990463257, 2.98000001907349, 2.33999991416931, 3.27999997138977, 3.15000009536743, 2.8199999332428, 4.17999982833862, 3.25, 2.4300000667572, 1.55999994277954, 3.04999995231628,
3.89000010490417, 2.58999991416931, 4.05000019073486, 2.98000001907349, 4.01999998092651, 3.67000007629395, 4.32000017166138, 4.59000015258789, 4.69000005722046, 2.20000004768372, 5.26999998092651, 4.8600001335144, 2.69000005722046, 1.5900000333786, 5.67999982833862, 2.05999994277954, 1.30999994277954, 1.73000001907349, 3.61999988555908, 3.21000003814697, 2.1800000667572, 2.36999988555908, 4.15000009536743, 3.98000001907349, 2.27999997138977, 2.67000007629395,
3.04999995231628, 2.9300000667572, 1.82000005245209, 5.03999996185303, 1.69000005722046, .389999985694885, 1.4099999666214, 1.57000005245209, 1.54999995231628, 1.4099999666214, .920000016689301, 1.28999996185303, 1.70000004768372, 1.70000004768372, 1.28999996185303, .910000026226044, 1.72000002861023, .779999971389771, 1.41999995708466, 1.55999994277954, 2.32999992370605, 1.51999998092651, 1.44000005722046, 1.57000005245209, 1.57000005245209, .649999976158142,
1.55999994277954, 1.38999998569489, 1.69000005722046, 1.70000004768372, 1.04999995231628, 1.80999994277954, 1.57000005245209, 1.13999998569489, 1.16999995708466, 1.67999994754791, 1.79999995231628, 1.54999995231628, 2.47000002861023, 2.35999989509583, 2.61999988555908, 1.44000005722046, 1.67999994754791, 1.4099999666214, 1.55999994277954, 1.94000005722046, 2.05999994277954, 1.71000003814697, 2.23000001907349, 1.71000003814697, 2.05999994277954, 1.70000004768372,
1.27999997138977, 2.21000003814697, 1.95000004768372, 1.89999997615814, 1.54999995231628, 2.86999988555908, 1.44000005722046, 1.79999995231628, .779999971389771, 1.66999995708466, 1.29999995231628, 1.82000005245209, 1.94000005722046, 1.28999996185303, 1.4099999666214, 1.55999994277954, 2.79999995231628, 5.28999996185303, 4.76000022888184, 6.36999988555908, 2.02999997138977, 4.67000007629395, 1.79999995231628, 4.92000007629395, 3.9300000667572, 3.28999996185303,
4.80999994277954, 3.78999996185303, 3.25, 1.4099999666214, 4.36999988555908, 3.70000004768372, 2.79999995231628, 1.00999999046326, 5.15999984741211, 5.30999994277954, 1.6599999666214, 4.57000017166138, 5.46999979019165, 4.6399998664856, 3.88000011444092, 4.55999994277954, 4.19000005722046, 3.6800000667572, 2.96000003814697, 4.21000003814697, 3.8199999332428, 4.05000019073486, 5.19999980926514, 4.46999979019165, 4.07999992370605, 2.6800000667572, 5.71000003814697,
5.09000015258789, 4.07000017166138, 4.69999980926514, 1.64999997615814, 3.78999996185303, 3.30999994277954, 5.40999984741211, 5.07999992370605, 4.98000001907349, 6.6100001335144, 6.3600001335144, 2.79999995231628, .980000019073486, 4.32999992370605, 4.42000007629395, 2.97000002861023, 6.05000019073486, 4.53999996185303, 3.5699999332428, 2.05999994277954, 2.05999994277954, 2.04999995231628, 4.88000011444092, 3.66000008583069, 2.90000009536743, 1.51999998092651,
3.15000009536743, 4.07000017166138, 5.65000009536743, 4.42000007629395, 5.36999988555908, 4.48999977111816, 4.11999988555908, 6.32999992370605, 5.61999988555908, 5.07000017166138, 5.53000020980835, 3.23000001907349, 4.48000001907349, 3.20000004768372, 6.78999996185303, 3.51999998092651, 6.8899998664856, 4.1100001335144, 5.65000009536743, 5.30000019073486, 4.75, 3.97000002861023, 5.40000009536743, 6.23999977111816, 6.6399998664856, 4.28999996185303,
4.09999990463257, 5.17000007629395, 2.74000000953674, 2.9300000667572, 6.84999990463257, 6.1100001335144, 6.90000009536743, 3.47000002861023, 6.05000019073486, 4.84000015258789, 4.48999977111816, 4.59000015258789, 4.38000011444092, 6.65999984741211, 6.76000022888184, 6.44000005722046, 6.15000009536743, 5.69999980926514, 6.38000011444092, 5.53000020980835, 5.82999992370605, 6.1100001335144, 6.46000003814697, 3.19000005722046, 6.96000003814697, 4.44000005722046,
7.21000003814697, 3.58999991416931, 4.48000001907349, 3.51999998092651, 4.21999979019165, 3.27999997138977, 3.40000009536743, 6.42000007629395, 6.51000022888184, 3.08999991416931, 5.03999996185303, 4.40999984741211, 2.55999994277954, 2.86999988555908, 1.48000001907349, 2.55999994277954, 2.17000007629395, 1.37999999523163, 2.76999998092651, 2.77999997138977, 2.40000009536743, 1.87999999523163, 1.63999998569489, 1.87000000476837, 1.00999999046326, 2.5,
3.83999991416931, 1.38999998569489, 1.37999999523163, 1.64999997615814, 1.38999998569489, 1.51999998092651, .990000009536743, 3.05999994277954, 1.49000000953674, 1.11000001430511, 1.61000001430511, 2.16000008583069, 2.55999994277954, 1.76999998092651, 2.33999991416931, 2.77999997138977, 2.82999992370605, 3.58999991416931, 1.12000000476837, 3.99000000953674, 1.64999997615814, 1.12000000476837, 2.25999999046326, 3.91000008583069, 2.48000001907349, 2.95000004768372,
2.16000008583069, 1.60000002384186, 1.88999998569489, 2.5, 2.38000011444092, 1.51999998092651, 1.8400000333786, 2.32999992370605, 1.50999999046326, 1.48000001907349, 1.27999997138977, .990000009536743, .990000009536743, 1.37000000476837, .990000009536743, 2.23000001907349, 2.91000008583069, 1.35000002384186, 1.12000000476837, 2.28999996185303, .879999995231628, 2.55999994277954, 2.74000000953674, 3.08999991416931, 1.6599999666214, 5.30000019073486,
4.59000015258789, 4.63000011444092, 5.21000003814697, 3.97000002861023, 4.59000015258789, 3.41000008583069, 4.09999990463257, 4.34000015258789, 4.46000003814697, 3.41000008583069, 5.21000003814697, 5.71000003814697, 4.46000003814697, 5.21000003814697, 5.3600001335144, 4.82000017166138, 4.59000015258789, 3.60999989509583, 3.97000002861023, 4.21999979019165, 4.34000015258789, 4.21999979019165, 5.09000015258789, 4.46000003814697, 4.59000015258789, 3.90000009536743,
4.09000015258789, 5.11999988555908, 4.46000003814697, 2.79999995231628, 6.44999980926514, 3.85999989509583, 4.34999990463257, 3.28999996185303, 5.46000003814697, 4.3899998664856, 4.46000003814697, 4.76000022888184, 3.36999988555908, 4.28999996185303, 4.46000003814697, 4.46999979019165, 4.96000003814697, 4.01999998092651, 4.59000015258789, 4.96000003814697, 4.82000017166138, 4.46999979019165, 4.51000022888184, 4.40999984741211, 6.19999980926514, 4.46000003814697,
4.51000022888184, 3.80999994277954, 4.34000015258789, 5.46000003814697, 4.59000015258789, 5, 6.44999980926514, 2.84999990463257, 4.59000015258789, 4.34000015258789, 3.75999999046326, 5.30000019073486, 4.59000015258789, 4.63000011444092, 5.21000003814697, 3.97000002861023, 4.59000015258789, 3.41000008583069, 4.09999990463257, 4.34000015258789, 4.46000003814697, 3.41000008583069, 5.21000003814697, 5.71000003814697, 4.46000003814697, 5.21000003814697,
5.3600001335144, 4.82000017166138, 4.59000015258789, 3.60999989509583, 3.97000002861023, 4.21999979019165, 4.34000015258789, 4.21999979019165, 5.09000015258789, 4.46000003814697, 4.59000015258789, 3.90000009536743, 4.09000015258789, 5.11999988555908, 4.46000003814697, 2.79999995231628, 6.44999980926514, 3.85999989509583, 4.34999990463257, 3.28999996185303, 5.46000003814697, 4.3899998664856, 4.46000003814697, 4.76000022888184, 3.36999988555908, 4.28999996185303,
4.46000003814697, 4.46999979019165, 4.96000003814697, 4.01999998092651, 4.59000015258789, 4.96000003814697, 4.82000017166138, 4.46999979019165, 4.51000022888184, 4.40999984741211, 6.19999980926514, 4.46000003814697, 4.51000022888184, 3.80999994277954, 4.34000015258789, 5.46000003814697, 4.59000015258789, 5, 6.44999980926514, 2.84999990463257, 4.59000015258789, 4.34000015258789, 3.75999999046326, 7.96999979019165, 9.82999992370605, 9.60000038146973,
9.6899995803833, 11.1999998092651, 8.93000030517578, 9.09000015258789, 9.32999992370605, 11.0200004577637, 10.1000003814697, 10.5900001525879, 10.1300001144409, 9.78999996185303, 11.1800003051758, 11.8699998855591, 9.72000026702881, 9.69999980926514, 9.4399995803833, 8.60000038146973, 7.69000005722046, 10.8599996566772, 9.68000030517578, 9.9399995803833, 9.38000011444092, 8.78999996185303, 7.96999979019165, 7.59000015258789, 8.32999992370605, 11.6899995803833,
11.960000038147, 11.8900003433228, 10.5600004196167, 12.4799995422363, 11.4700002670288, 10.9700002670288, 10.1899995803833, 11.8999996185303, 11.0299997329712, 10.8400001525879, 10.7399997711182, 9.39000034332275, 9.9399995803833, 11.0100002288818, 9.63000011444092, 10.8000001907349, 9.01000022888184, 10.2799997329712, 10.2700004577637, 11.1300001144409, 6.86999988555908, 8.55000019073486, 11.3299999237061, 7.86999988555908, 10.0900001525879, 10.1899995803833,
7.92999982833862, 10.75, 11.3199996948242, 12.039999961853, 9.72999954223633, 8.96000003814697, 9, 8.88000011444092, 6.67999982833862, 2.22000002861023, 3.07999992370605, 2.21000003814697, 1.17999994754791, 1.78999996185303, 2.58999991416931, 1.57000005245209, 2.22000002861023, 1.41999995708466, 3.75, 2.74000000953674, 2.24000000953674, 2.5, 3.22000002861023, 2.59999990463257, 3.11999988555908, 2.22000002861023, 3.26999998092651, 1.17999994754791,
2.57999992370605, 1.55999994277954, 4.30999994277954, 4.15000009536743, .790000021457672, 2.97000002861023, 4.03000020980835, 2.23000001907349, 1.44000005722046, 2.32999992370605, 4.36999988555908, 1.60000002384186, 2.60999989509583, 2.65000009536743, 4.73999977111816, 2.8199999332428, 2.6800000667572, 3.38000011444092, 4.13000011444092, 3.92000007629395, 2.42000007629395, 1.57000005245209, 3.61999988555908, 3.14000010490417, 1.91999995708466, 3.13000011444092,
4.42999982833862, 1.58000004291534, 2.08999991416931, 4.40999984741211, 3.29999995231628, 2.15000009536743, 1.70000004768372, 1.49000000953674, 2.75, 2.64000010490417, 1.71000003814697, 2.35999989509583, 4.73000001907349, 3.69000005722046, 2.89000010490417, 2.35999989509583, 2.59999990463257, 1.57000005245209, 1.69000005722046, 1.45000004768372, .850000023841858, 1.21000003814697, .850000023841858, 1.70000004768372, 1.82000005245209, 1.82000005245209,
1.45000004768372, 1.58000004291534, 1.21000003814697, 2.42000007629395, 1.82000005245209, 1.45000004768372, .610000014305115, .610000014305115, 1.45000004768372, 1.70000004768372, 1.82000005245209, 1.21000003814697, 1.82000005245209, .970000028610229, 1.58000004291534, .850000023841858, 1.82000005245209, .850000023841858, 1.45000004768372, 1.82000005245209, 1.33000004291534, 1.21000003814697, 1.21000003814697, 1.21000003814697, .970000028610229, 1.45000004768372,
1.33000004291534, 2.42000007629395, .970000028610229, 1.70000004768372, 1.21000003814697, 1.21000003814697, 1.21000003814697, .610000014305115, .730000019073486, 1.82000005245209, 1.21000003814697, .850000023841858, 2.05999994277954, 1.21000003814697, .970000028610229, 1.58000004291534, 1.21000003814697, 1.0900000333786, 1.70000004768372, 1.33000004291534, 1.33000004291534, 1.21000003814697, 1.45000004768372, 1.70000004768372, 1.33000004291534, 1.21000003814697,
1.82000005245209, 1.70000004768372, 1.21000003814697, 1.82000005245209, 1.21000003814697, 5.09000015258789, 4.3600001335144, 0, 3.88000011444092, 3.88000011444092, 3.02999997138977, 1.45000004768372, 3.39000010490417, 6.30000019073486, 3.64000010490417, 3.88000011444092, 3.26999998092651, 4.84999990463257, 2.67000007629395, 4.23999977111816, 3.64000010490417, 4.84999990463257, 4.23999977111816, 3.26999998092651, 3.39000010490417, 4.96999979019165,
5.44999980926514, 1.82000005245209, 4.6100001335144, 2.67000007629395, 3.64000010490417, 3.02999997138977, 3.39000010490417, 3.15000009536743, 2.78999996185303, 3.02999997138977, 4, 6.05999994277954, 3.15000009536743, 3.88000011444092, 3.26999998092651, 7.51999998092651, 2.91000008583069, 2.78999996185303, 3.15000009536743, 8.47999954223633, 5.44999980926514, 4.84999990463257, 3.88000011444092, 4, 4.6100001335144, 4.84999990463257, 4.3600001335144,
3.39000010490417, 3.64000010490417, 3.02999997138977, 3.88000011444092, 4.23999977111816, 3.39000010490417, 3.88000011444092, 3.39000010490417, 4.3600001335144, 4.84999990463257, 3.64000010490417, 3.02999997138977, 8.72999954223633, 3.02999997138977, 2.42000007629395, 5.44999980926514, 4.23000001907349, 1.92999994754791, .389999985694885, .639999985694885, 1.41999995708466, .769999980926514, 1.02999997138977, .129999995231628, .899999976158142, 1.14999997615814,
1.27999997138977, .519999980926514, 2.96000003814697, 2.05999994277954, 1.4099999666214, 1.79999995231628, 3.33999991416931, 1.79999995231628, 3.07999992370605, 2.88000011444092, 1.53999996185303, .509999990463257, 2.05999994277954, .389999985694885, 1.92999994754791, 1.66999995708466, 1.53999996185303, 3.58999991416931, 3.07999992370605, 1.61000001430511, 3.22000002861023, 2.8199999332428, 2.05999994277954, 1.66999995708466, 2.55999994277954, 3.21000003814697,
4.09999990463257, 2.5699999332428, 2.44000005722046, 1.1599999666214, 1.92999994754791, 1.92999994754791, 1.92999994754791, 2.8199999332428, 2.69000005722046, 1.4099999666214, 1.92999994754791, 1.1599999666214, 1.79999995231628, 1.79999995231628, .769999980926514, 1.4099999666214, .899999976158142, 1.53999996185303, .509999990463257, 2.04999995231628, .899999976158142, 2.04999995231628, .639999985694885, 1.92999994754791, 2.19000005722046, 1.27999997138977,
1.14999997615814, 2.45000004768372, 1.45000004768372, .850000023841858, 1.21000003814697, .850000023841858, 1.70000004768372, 1.82000005245209, 1.82000005245209, 1.45000004768372, 1.58000004291534, 1.21000003814697, 2.42000007629395, 1.82000005245209, 1.33000004291534, .610000014305115, 1.82000005245209, 1.45000004768372, 1.70000004768372, 1.82000005245209, 1.21000003814697, 1.82000005245209, .970000028610229, 1.58000004291534, .850000023841858, 1.82000005245209,
.850000023841858, 1.45000004768372, 1.82000005245209, 1.33000004291534, 1.21000003814697, 1.21000003814697, 1.21000003814697, .970000028610229, 1.45000004768372, 1.33000004291534, 2.42000007629395, .970000028610229, 1.70000004768372, 1.21000003814697, 1.33000004291534, 1.21000003814697, .610000014305115, .730000019073486, 1.82000005245209, 1.21000003814697, .850000023841858, 2.05999994277954, 1.21000003814697, .970000028610229, 1.58000004291534, 1.21000003814697,
.610000014305115, 1.70000004768372, 1.33000004291534, 1.33000004291534, 1.21000003814697, 1.45000004768372, 1.70000004768372, 1.33000004291534, 1.21000003814697, 1.82000005245209, 1.70000004768372, 1.21000003814697, 1.82000005245209, 1.21000003814697, 8.52000045776367, 7.28999996185303, 7.28999996185303, 7.28999996185303, 8.09000015258789, 6.78000020980835, 7.84999990463257, 6.78000020980835, 6.73999977111816, 7.17000007629395, 8.22999954223633, 7.17000007629395,
8.88000011444092, 9.47999954223633, 7.51999998092651, 9.47999954223633, 7.71999979019165, 6.09000015258789, 6.03000020980835, 6.09000015258789, 7.1100001335144, 6.90999984741211, 7.23999977111816, 6.90999984741211, 6.46000003814697, 6.69000005722046, 5.01000022888184, 6.69000005722046, 9.38000011444092, 7.05999994277954, 10.3100004196167, 7.05999994277954, 7.75, 8.0600004196167, 7.25, 8.0600004196167, 8.34000015258789, 8.02000045776367, 8.5600004196167,
8.02000045776367, 9.02999973297119, 8.48999977111816, 8.48999977111816, 8.48999977111816, 7.23000001907349, 7.90999984741211, 8.47999954223633, 7.90999984741211, 7.26000022888184, 6.73000001907349, 6.86999988555908, 6.73000001907349, 6.94999980926514, 7.03999996185303, 7.63000011444092, 7.03999996185303, 7.15000009536743, 7.80000019073486, 5.53999996185303, 7.80000019073486, 7.71000003814697, 4.09000015258789, 5.94999980926514, 4.09000015258789, 8.18000030517578,
7.25, 8.52999973297119, 7.78999996185303, 7.1399998664856, 8.75, 10.1099996566772, 8.44999980926514, 7.90999984741211, 10.1099996566772, 9.57999992370605, 10.25, 7.23000001907349, 7.61999988555908, 9.02000045776367, 10.8699998855591, 3.28999996185303, 9.42000007629395, 5.46000003814697, 6.98000001907349, 7.44000005722046, 9.72999954223633, 8.34000015258789, 9.97999954223633, 9.39000034332275, 9.92000007629395, 6.98000001907349, 5.1399998664856, 11.4300003051758,
6.5, 12.1499996185303, 10.1800003051758, 9.68000030517578, 10.1199998855591, 11.0500001907349, 10.3500003814697, 8.40999984741211, 8.02999973297119, 9.48999977111816, 7.69999980926514, 11.039999961853, 10.0299997329712, 9.06999969482422, 10.0900001525879, 11.3500003814697, 9.63000011444092, 10.2799997329712, 10.1199998855591, 9.5600004196167, 9.14999961853027, 9.03999996185303, 10.1899995803833, 7.3899998664856, 8.84000015258789, 9.52999973297119,
9.35000038146973, 8.35999965667725, 7.88000011444092, 10.4099998474121, 7.94000005722046, 5.32000017166138, 7.59999990463257, 6.28000020980835, 4.76999998092651, 2.05999994277954, 2.42000007629395, 2.29999995231628, 4.96999979019165, 3.64000010490417, 2.05999994277954, 4.42000007629395, 2.24000000953674, 3.75999999046326, 1.45000004768372, 4.11999988555908, 5.57999992370605, 2.54999995231628, 1.0900000333786, 5.32999992370605, 3.26999998092651, 3.26999998092651,
.970000028610229, 3.88000011444092, 3.26999998092651, 3.64000010490417, 3.88000011444092, 3.64000010490417, 4, 2.42000007629395, 2.29999995231628, 2.1800000667572, .239999994635582, 1.0900000333786, 4.11999988555908, 4.96999979019165, 4.11999988555908, 4.96999979019165, 2.91000008583069, 6.30000019073486, 2.05999994277954, 4.6100001335144, 2.54999995231628, 4.73000001907349, 3.88000011444092, 4.11999988555908, 1.94000005722046, 4.3600001335144, 4.3600001335144,
5.21000003814697, 4.23999977111816, 4, 4.48000001907349, 4.23999977111816, .850000023841858, 3.26999998092651, 4.73000001907349, .479999989271164, 1.21000003814697, 2.91000008583069, .670000016689301, 4.6100001335144, 1.21000003814697, 3.88000011444092, 3.15000009536743, 4.48000001907349, 2.91000008583069, 0, 1.72000002861023, 1.45000004768372, .850000023841858, 1.21000003814697, .970000028610229, 1.70000004768372, 1.82000005245209, 1.82000005245209,
1.45000004768372, 1.58000004291534, 1.0900000333786, 1.82000005245209, 1.82000005245209, 1.21000003814697, .970000028610229, 1.21000003814697, 1.33000004291534, 1.70000004768372, 1.82000005245209, 1.0900000333786, 1.82000005245209, .970000028610229, 1.58000004291534, .850000023841858, .730000019073486, .850000023841858, 1.45000004768372, 1.82000005245209, 1.33000004291534, 1.58000004291534, 1.21000003814697, 1.45000004768372, .970000028610229, 1.45000004768372,
1.33000004291534, .610000014305115, .970000028610229, 1.70000004768372, 1.0900000333786, 1.33000004291534, 1.21000003814697, .610000014305115, .730000019073486, 1.82000005245209, 1.21000003814697, .850000023841858, 1.94000005722046, 1.21000003814697, .970000028610229, 1.58000004291534, 1.21000003814697, .479999989271164, 1.70000004768372, 1.33000004291534, 1.33000004291534, 1.21000003814697, 1.45000004768372, 1.70000004768372, 1.33000004291534, 1.33000004291534,
1.82000005245209, 1.21000003814697, 1.21000003814697, 1.82000005245209, 1.21000003814697), 
StyTreatment=as.factor(c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16,
16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16,
1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1,
2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2,
3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3,
4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4,
5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5,
6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6,
7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7,
8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8,
9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9,
10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10,
10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11,
11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 13, 11, 12, 3, 6, 14, 10, 1, 2, 16, 15, 4, 8, 9, 5, 7, 1, 12, 13, 9, 5, 11, 8, 15, 7, 14,
3, 16, 4, 2, 6, 10, 4, 7, 2, 11, 6, 9, 12, 16, 5, 1, 15, 13, 14, 8, 10, 3, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12,
13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13,
13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14,
14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16)),
CritTrtNo=as.factor(c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16,
16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1,
1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2,
2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3,
3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4,
4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5,
5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6,
6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7,
7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8,
8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9,
9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10,
10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10,
11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11,
11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 13, 11, 12, 3, 6, 14, 10, 1, 2, 16, 15, 4, 8, 9, 5, 7, 1, 12, 13, 9, 5, 11, 8, 15, 7, 14, 3,
16, 4, 2, 6, 10, 4, 7, 2, 11, 6, 9, 12, 16, 5, 1, 15, 13, 14, 8, 10, 3, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13,
13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13,
14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14,
14, 15, 15, 15, 15, 16, 16, 16, 16, 1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 6, 6, 6, 6, 7, 7, 7, 7, 8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 11, 11, 11, 11, 12, 12, 12, 12, 13, 13, 13, 13, 14, 14, 14, 14, 15, 15, 15, 15, 16, 16, 16, 16))
)
st.tab$Trial <- as.factor(st.tab$Trial)
st.tab$Treatment <- as.factor(st.tab$Treatment)
st.tab$RepNo <- as.factor(st.tab$RepNo)
```
# Utility functions

We use one function to compute a generalized inverse. We'll need this for computing variance-covariance matrices.

```{r}
pseudoinverse <- function(A) {
  svdRes <- svd(A)
  D <- svdRes$d
  tol <- 1/ (.Machine$integer.max)
  D[abs(D)<tol] <- 0
  Dinv <- D
  Dinv[Dinv>0] <- 1/Dinv[Dinv>0]
  Dinv <- diag(Dinv)
  V <- svdRes$v
  V[abs(V)<tol] <- 0
  U <- svdRes$u
  U[abs(U)<tol] <- 0
  return(V%*%Dinv%*%t(U))
}
```

# Standard AOV

Start with a standard analysis of variance of a linear model. 

```{r}
st.lm <- lm(Plot.Mean ~ Trial*Treatment + Trial:RepNo, data=st.tab,x=TRUE)
aov.tbl<-anova(st.lm)
print(summary(st.lm))
print(aov.tbl)
```

For now, we'll skip model diagnostics - we may generally assume that the basic linear model is appropriate, and that later analysis provide insight in cases of non-heterogeneous variances or non-normal data. Instead, we proceed directly to analysis of variance. I use anova to produce a data frame that we will build upon.

Create a standard AOV table

```{r}
AOVRowNames <- c('Trial','Rep in Trial','Treatment','Treatment x Trial','Residual', 'Nonadditivity', 'Nonadditivity Residual', 'Stability', 'Stability Residual' )
AOVRows <- length(AOVRowNames)
AOVTable <- data.frame(DF=rep(NA,AOVRows),SS=rep(NA,AOVRows),MS=rep(NA,AOVRows),F=rep(NA,AOVRows),P=rep(NA,AOVRows),Var=rep(NA,AOVRows))
row.names(AOVTable) <- AOVRowNames
```

```{r}
AOVTable['Treatment',] <- aov.tbl['Treatment',]
AOVTable['Trial',] <- aov.tbl['Trial',]
AOVTable['Residual',] <- aov.tbl['Residuals',]
AOVTable['Treatment x Trial',] <- aov.tbl['Trial:Treatment',]
AOVTable['Rep in Trial',] <- aov.tbl['Trial:RepNo',]
#clear Var column, will be copied from DF
AOVTable[,'Var'] <- NA
```

If trials are random, we need to change the test:

```{r}
AOVTable['Treatment','F'] <- AOVTable['Treatment','MS'] / AOVTable['Treatment x Trial','MS']
AOVTable['Treatment','P'] <- 1-pf(AOVTable['Treatment','F'], AOVTable['Treatment','DF'], AOVTable['Treatment x Trial','DF'])
AOVTable['Rep in Trial','F'] <- AOVTable['Rep in Trial','MS'] / AOVTable['Treatment x Trial','MS']
AOVTable['Rep in Trial','P'] <- 1-pf(AOVTable['Rep in Trial','F'], AOVTable['Rep in Trial','DF'], AOVTable['Treatment x Trial','DF'])
```

Calculate variances from expected mean squares. McIntosh provided a table with this form,

Source | d.f. | Fixed | Mixed
-------|------|-------|-------
Trial  | $e-1$ | $\sigma_{\epsilon} ^2 + rt \theta _E ^2$ | $\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2 + rt \sigma _E ^2$
Replicate in Trial  | $e(r-1)$ | $\sigma_{\epsilon} ^2 + t \sigma _B ^2$ | $\sigma_{\epsilon} ^2 + t \sigma _{B} ^2$
Treatment | $t-1$ | $\sigma_{\epsilon} ^2 + re \theta _T ^2$ | $\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2 + rt \theta _T ^2$
Trial $\times$ Treatment | $te-1$ | $\sigma_{\epsilon} ^2 + r \theta _{E \times T} ^2$ | $\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2$ 
Error | $t r e-1$ | $\sigma_{\epsilon} ^2$ | $\sigma_{\epsilon} ^2$


but, as we see below, the corresponding mixed model analysis implies this from:


Source | d.f. | Fixed | Mixed
-------|------|-------|-------
Trial  | $e-1$ | $\sigma_{\epsilon} ^2 + rt \theta _E ^2$ | $\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2  + t \sigma _B ^2 + rt \sigma _E ^2$
Replicate in Trial  | $e(r-1)$ | $\sigma_{\epsilon} ^2 + t \sigma _B ^2$ | $\sigma_{\epsilon} ^2 + t \sigma _{B} ^2$
Treatment | $t-1$ | $\sigma_{\epsilon} ^2 + re \theta _T ^2$ | $\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2 + rt \theta _T ^2$
Trial $\times$ Treatment | $te-1$ | $\sigma_{\epsilon} ^2 + r \theta _{E \times T} ^2$ | $\sigma_{\epsilon} ^2 + n \sigma _{E \times T} ^2$ 
Error | $t r e-1$ | $\sigma_{\epsilon} ^2$ | $\sigma_{\epsilon} ^2$


```{r}
treatments <-AOVTable['Treatment','DF']+1
trials <- AOVTable['Trial','DF']+1
blocks <- AOVTable['Rep in Trial','DF'] + trials
reps <- (blocks/trials)
```


```{r}
TrialMS <- AOVTable['Trial','MS']
BlockMS <- AOVTable['Rep in Trial','MS']
ErrorMS <- AOVTable['Residual','MS']
InteractionMS <- AOVTable['Treatment x Trial','MS']
#AOVTable['Trial','Var'] <- (TrialMS - BlockMS)/(treatments)
```

If we want to duplicate SAS proc mixed analysis, this is the variance estimate

```{r}
AOVTable['Trial','Var'] <- (TrialMS - InteractionMS - BlockMS + ErrorMS)/(treatments*reps)
```

That is,
$$
\begin{aligned}
TrialMS &= \sigma_{\epsilon} ^2 +r \sigma _{E \times T} ^2 + t \sigma _B ^2 + rt \sigma _E ^2 \\
rt \sigma _E ^2 &=TrialMS - (\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2 + t \sigma _B ^2) \\
&= TrialMS - (\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2 + \sigma_{\epsilon} ^2 - \sigma_{\epsilon} ^2 + t \sigma _B ^2)\\
&= TrialMS - (\sigma_{\epsilon} ^2 + r \sigma _{E \times T} ^2) - (\sigma_{\epsilon} ^2 + t \sigma _B ^2) + \sigma_{\epsilon} ^2 \\
&= TrialMS - InteractionMS - BlockMS + ErrorMS
\end{aligned}
$$

```{r}
AOVTable['Rep in Trial','Var'] <- (BlockMS - ErrorMS)/(treatments)
AOVTable['Treatment x Trial','Var'] <- (InteractionMS - ErrorMS)/reps
AOVTable['Residual','Var'] <- ErrorMS
#AOVTable['Replicate','Var'] <- (AOVTable['Replicate','MS']-ERRORA)/(treatments*timepoints)
#AOVTable['Error Treatment','Var'] <- (ERRORA - ERRORB)/timepoints
#AOVTable['Residuals','Var'] <- ERRORB

cat('Preliminary ANOVA', '\n')
print(AOVTable)
```

Compare with mixed effects
```{r}
library(lme4)
st.lmer <- lmer(Plot.Mean ~ Treatment + (1 | Trial/RepNo) + (1 | Trial:Treatment), data=st.tab)
summary(st.lmer)
```


We'll want contrasts matrices to create linear contrast matrices for least square means.

Now we extend the analysis to compute means. If the data are balanced, we can do simple means tables, but for now, assume missing plots. We'll later add checks for missing treatment by trial cells.

We want a contrast matrix of the form 
$$ 
L=1 | L_e| L_t|L_{(et)}|L_{(b(t))} 
$$
were the number of rows in L match treatments times trials and the number of columns in $L$ match $\hat{\mathbf{\beta}}$, where $\hat{\mathbf{\beta}}$ is the OLS estimate for $y=X\mathbf{\beta}}$ and $X$ is the model matrix.

```{r}
C.e <- match.fun(st.lm$contrasts[['Trial']])(trials)
C.t <- match.fun(st.lm$contrasts[['Treatment']])(treatments)
C.r <- match.fun(st.lm$contrasts[['Trial']])(reps)

C.full.t <- match.fun(st.lm$contrasts[['Treatment']])(treatments,contrasts=FALSE)
C.full.e <- match.fun(st.lm$contrasts[['Trial']])(trials,contrasts=FALSE)
C.full.r <- match.fun(st.lm$contrasts[['Trial']])(reps,contrasts=FALSE)
C.full.b <- kronecker(C.full.r,C.full.e)
```

```{r}
coeffs <- st.lm$coefficients
L.t <- kronecker(C.t,rep(1,trials))
L.e <- kronecker(rep(1,treatments),C.e)
L.r <-  t(rep(1,reps-1)) %x% rep(1,treatments) %x% C.full.e
L.r <- L.r/(reps)
L.te = C.t %x% C.e
```

```{r}
L.txt <- cbind(rep(1,treatments*trials),L.e,L.t, L.te, L.r)
txt.lsmeans.tbl <- t(matrix(L.txt %*% coeffs,nrow=treatments,byrow=TRUE))
txt.lsmeans.tbl
tapply(st.tab$Plot.Mean,list(st.tab$Trial,st.tab$Treatment),mean)
```


```{r}
trt.means <- colMeans(txt.lsmeans.tbl)
trial.means <- rowMeans(txt.lsmeans.tbl)
means.tbl <- data.frame(trt=as.integer(levels(st.tab$Treatment)),arith=tapply(st.tab$Plot.Mean, list(st.tab$Treatment),mean),lsmean=trt.means)
```

# Treatment Comparisons

Having produced linear coefficients to compute treatment means, we can now create linear combinations for differences. We use a function developed for repeated measures. This requires a covariance matrix.


Now produce the covariances


```{r}
Design <- list(Treatment=C.full.t[as.numeric(st.tab$Treatment),],
               Trial=C.full.e[as.numeric(st.tab$Trial),],
               Interaction=(C.full.t %x% C.full.e)[as.numeric(st.tab$Treatment:st.tab$Trial),],
               Replicate=C.full.b[as.numeric(st.tab$Trial:st.tab$RepNo),],
               I=diag(1,dim(st.tab)[1]), G=NA, R=NA, V=NA)
```

```{r}
Design$R <- Design$I * AOVTable['Residual','Var']
Design$G <- Design$Replicate %*% (diag(1, dim(Design$Replicate)[2]) * AOVTable['Rep in Trial','Var'])  %*% t(Design$Replicate)
Design$G <- Design$G + Design$Trial %*% (diag(1, dim(Design$Trial)[2]) * AOVTable['Trial','Var'])  %*% t(Design$Trial)
Design$G <- Design$G + Design$Interaction %*% (diag(1, dim(Design$Interaction)[2]) * AOVTable['Treatment x Trial','Var'])  %*% t(Design$Interaction)
Design$V <- Design$G + Design$R
```


```{r}
V.inv <- pseudoinverse(Design$V)
Covariance <- pseudoinverse((t(Design$Treatment) %*% V.inv %*% Design$Treatment))

L.rows <- dim(Covariance)[1]

StandardErrors=matrix(0, nrow = L.rows, ncol = L.rows)
se.idx <- 1
for (i in 1: (L.rows-1)) {
  for (j in (i+1):L.rows) {
    err <- sqrt((Covariance[i,i] + Covariance[j,j] - Covariance[i,j]- Covariance[j,i]))
    StandardErrors[i,j] <- err
    StandardErrors[j,i] <- err
    se.idx <- se.idx + 1
  }
}
Covariance
StandardErrors
```

# Non-additivity

```{r}
grandmean <- mean(unlist(txt.lsmeans.tbl))
trial.effects <- trial.means-grandmean
trt.effects <- trt.means-grandmean
st.tab$TreatmentIdx <- as.numeric(st.tab$Treatment)
st.tab$TrialIdx <- as.numeric(st.tab$Trial)
st.tab$a <- trt.effects[st.tab$TreatmentIdx]
st.tab$b <- trial.effects[st.tab$TrialIdx]
tdf.st.lm <- lm(Plot.Mean ~ Trial + Treatment + Trial:RepNo + a:b,data=st.tab)
print(summary(tdf.st.lm))
tdf.st.tbl <- anova(tdf.st.lm)
print(tdf.st.tbl)
```



We need to rearrange the means table to a form than be be used to regress treatment by trial means against trial means.

```{r}
txt.lsmeans.tbl <- t(txt.lsmeans.tbl)
table.dim <- dim(txt.lsmeans.tbl)
print(cnames <- colnames(txt.lsmeans.tbl))
print(rnames <- rownames(txt.lsmeans.tbl))
if(!is.data.frame(txt.lsmeans.tbl)) {
  table.dat <- data.frame(txt.lsmeans.tbl)
}
```

```{r}
table.dat <- stack(table.dat)
if(is.null(cnames)) {
  table.dat$ind <- rep(1:table.dim[2],each=table.dim[1])
}
if(is.null(rnames)) {
  rnames <- 1:table.dim[1]
}
table.dat$newrow <- as.factor(rep(rnames,table.dim[2]))
colnames(table.dat) <- c('Plot.Mean','Trial','Treatment')
table.dat[,c('Treatment','Trial')] <- lapply(table.dat[,c('Treatment','Trial')] , factor)

  
table.dat$a <- trt.effects[table.dat$Treatment]
table.dat$b <- trial.effects[table.dat$Trial]

tdf.tbl.lm <- lm(Plot.Mean ~ Trial + Treatment + a:b,data=table.dat)
print(summary(tdf.tbl.lm))
tdf.tbl <-anova(tdf.tbl.lm)
```


Some graphs:
```{r}
table.dat$a.bar <- mean(trt.effects)
table.dat$b.bar <- mean(trial.effects)
table.dat$y.bar <- table.dat$a+table.dat$b
table.dat$y.bar <- table.dat$a*table.dat$b
mu <- mean(table.dat$Plot.Mean)
table.dat$mu <- (table.dat$Plot.Mean-mu) - table.dat$y.bar
plot(y.bar ~ b,data=table.dat)
plot(Plot.Mean ~ b,data=table.dat)
plot(Plot.Mean ~ I(a*b),data=table.dat)

plot(mu ~ y.bar,data=table.dat)
abline(coef(lm(mu ~ y.bar,data=table.dat)))

lm(Plot.Mean ~ y.bar,data=table.dat)
lm(Plot.Mean ~ a:b,data=table.dat)


```



Decompose treatment by trial interation into a 1 df non-additivity component and a residual.

```{r}
AOVTable['Nonadditivity',] <- tdf.st.tbl['a:b',]
AOVTable['Nonadditivity','Var'] <- NA
AOVTable['Nonadditivity Residual',] <- AOVTable['Treatment x Trial',]-AOVTable['Nonadditivity',]
AOVTable['Nonadditivity Residual','MS'] <- AOVTable['Nonadditivity Residual','SS']/AOVTable['Nonadditivity Residual','DF'] 
AOVTable['Nonadditivity Residual','Var'] <- AOVTable['Nonadditivity Residual','MS']

Fval <- AOVTable['Nonadditivity','MS']/AOVTable['Nonadditivity Residual','MS']
AOVTable['Nonadditivity','F'] <- Fval
AOVTable['Nonadditivity','P'] <- 1 - pf(Fval, AOVTable['Nonadditivity','DF'], AOVTable['Nonadditivity Residual','DF'])

Fval <- AOVTable['Nonadditivity Residual','MS']/AOVTable['Residual','MS']
AOVTable['Nonadditivity Residual','F'] <- Fval
AOVTable['Nonadditivity Residual','P'] <- 1 - pf(Fval, AOVTable['Nonadditivity Residual','DF'], AOVTable['Residual','DF'])
AOVTable
```



```{r}
het.st.lm <- lm(Plot.Mean ~ Trial + Treatment + Trial:RepNo + Treatment:b,data=st.tab)
print(summary(het.st.lm))
print(anova(het.st.lm))
het.tbl.lm <- lm(Plot.Mean ~ Trial + Treatment + Treatment:b,data=st.tab)
print(summary(het.tbl.lm))
print(anova(het.tbl.lm))
het0.tbl.lm <- lm(Plot.Mean ~ 0+Treatment + Treatment:b,data=table.dat)
print(summary(het0.tbl.lm))
print(anova(het0.tbl.lm))
het.st.tbl <- anova(het.st.lm)
```

Similarly, decompose stability of slopes

```{r}
AOVTable['Stability',] <- het.st.tbl['Treatment:b',]
AOVTable['Stability','Var'] <- NA
AOVTable['Stability Residual',] <- AOVTable['Treatment x Trial',]-AOVTable['Stability',]
AOVTable['Stability Residual','MS'] <- AOVTable['Stability Residual','SS']/AOVTable['Stability Residual','DF'] 
AOVTable['Stability Residual','Var'] <- AOVTable['Stability Residual','MS']

Fval <- AOVTable['Stability','MS']/AOVTable['Stability Residual','MS']
AOVTable['Stability','F'] <- Fval
AOVTable['Stability','P'] <- 1 - pf(Fval, AOVTable['Stability','DF'], AOVTable['Stability Residual','DF'])

Fval <- AOVTable['Stability Residual','MS']/AOVTable['Residual','MS']
AOVTable['Stability Residual','F'] <- Fval
AOVTable['Stability Residual','P'] <- 1 - pf(Fval, AOVTable['Stability Residual','DF'], AOVTable['Residual','DF'])
AOVTable
```

Slopes for each treatment, relative to trial mean.

```{r}
tdf.coef <- summary(tdf.tbl.lm)$coefficients
tdf.coef <- tdf.coef['a:b',c(1,1:dim(tdf.coef)[2])]

tdf.coef

Coefficients.tbl <- summary(het0.tbl.lm)$coefficients

CoefRows <- dim(Coefficients.tbl)[1]
CoefTrts <- CoefRows/2
Coefficients.tbl <- Coefficients.tbl[(CoefTrts+1):CoefRows,c(1,1:dim(Coefficients.tbl)[2])]
Coefficients.tbl <- rbind(tdf.coef,Coefficients.tbl)

colnames(Coefficients.tbl) <- c('Slope','Relative Slope', 'SE','t','P')
row.names(Coefficients.tbl)[1] <- 'a:b'
```

At this point, the slope is an absolute slope. We want to convert the slope to be relative to unity (1), so subtract and recalculate a t value. We want degrees of freedom

```{r}
Coefficients.tbl[,'Relative Slope'] <- (Coefficients.tbl[,'Slope']-1)
Coefficients.tbl[,'t'] <- Coefficients.tbl[,'Relative Slope']/Coefficients.tbl[,'SE']
Coefficients.tbl[,'P'] <- pt(abs(Coefficients.tbl[,'t']),AOVTable['Stability Residual','DF'],lower.tail=FALSE)
Coefficients.tbl['a:b','P'] <- pt(abs(Coefficients.tbl['a:b','t']),AOVTable['Nonadditivity Residual','DF'],lower.tail=FALSE)
Coefficients.tbl
```