---
title: "Changes in Wheat Yields"
output: html_document
---

```{r}
library(ggplot2)
library(gridExtra)
library(maps)
```

We start our analysis centered on the USDA NAS data set at http://quickstats.nass.usda.gov

Program : SURVEY
Sector : CROPS
Group : FIELD CROPS
Commodity : WHEAT
Category : YIELD
Data Item : WHEAT, WINTER - YIELD, MEASURED in BU / ACRE
Domain : TOTAL
Location : COUNTY
State : KANSAS, NEBRASKA, NORTH DAKOTA, OKLAHOMA, SOUTH DAKOTA, TEXAS
Period Type: ANNUAL
Period: YEAR

Note that there are data for insect damage, etc.

all available years
36000+ records

Examine the raw data.

```{r}
county.yield.dat <- read.csv("./data/usda/69C9E26C-F285-325A-9443-6668747878F8.csv", header = TRUE)
county.yield.plot <- ggplot(county.yield.dat, aes(Year,Value)) 
county.yield.plot <- county.yield.plot + scale_colour_brewer(palette="Set1") 
#county.yield.plot <- county.yield.plot + geom_point(aes(color=Ag.District),size=2,alpha = 0.3)
county.yield.plot <- county.yield.plot + geom_smooth(aes(group= State,color=State),weight=10,se = FALSE,method="loess",span = 0.6)
county.yield.plot
```

We have a county labelled OTHER (COMBINED) COUNTIES

```{r}
levels(county.yield.dat$County)
county.yield.dat <- subset(county.yield.dat, county.yield.dat$County != "OTHER (COMBINED) COUNTIES")
```

Note the number of missing years.

Agricultural district, otherwise same as above
```{r}
district.yield.dat <- read.csv("./data/usda/D545A01D-F19A-3E58-AE85-E2D79BBBBCB5.csv", header = TRUE)
district.yield.plot <- ggplot(district.yield.dat, aes(Year,Value)) 
district.yield.plot <- district.yield.plot + scale_colour_brewer(palette="Set1") 
#district.yield.plot <- district.yield.plot + geom_point(aes(color=Ag.District),size=2,alpha = 0.3)
district.yield.plot <- district.yield.plot + geom_smooth(aes(group= State,color=State),weight=10,se = FALSE,method="loess",span = 0.6)
district.yield.plot
```

and states, but from 1910 onward. Note this includes for later values actual and forecast yields


```{r}
state.yield.dat <- read.csv("./data/usda/B1926239-B043-3DBC-B92F-C4BB7F081392.csv", header = TRUE)
state.yield.plot <- ggplot(state.yield.dat, aes(Year,Value)) 
state.yield.plot <- state.yield.plot + scale_colour_brewer(palette="Set1") 
#state.yield.plot <- state.yield.plot + geom_point(aes(color=Ag.District),size=2,alpha = 0.3)
state.yield.plot <- state.yield.plot + geom_smooth(aes(group= State,color=State),weight=10,se = FALSE,method="loess",span = 0.6)
state.yield.plot
```

Finally, all wheat, national level. This goes back to 1866-2010

```{r}
national.yield.dat <- read.csv("./data/usda/4C586F51-45F8-317B-A4AB-6792AB49A6A2.csv", header = TRUE)
national.yield.plot <- ggplot(national.yield.dat, aes(Year,Value)) 
national.yield.plot <- national.yield.plot + scale_colour_brewer(palette="Set1") 
#national.yield.plot <- national.yield.plot + geom_point(aes(color=Ag.District),size=2,alpha = 0.3)
national.yield.plot <- national.yield.plot + geom_smooth(weight=10,se = FALSE,method="loess",span = 0.6)
national.yield.plot
```


Trial maps use lower case state names
```{r}
county.yield.dat$StateUpper <- county.yield.dat$State
county.yield.dat$State <- tolower(as.character(county.yield.dat$State))
county.yield.dat$State <- as.factor(county.yield.dat$State)
county.yield.dat$CountyUpper <- county.yield.dat$County
county.yield.dat$County <- tolower(as.character(county.yield.dat$County))
county.yield.dat$County <- as.factor(county.yield.dat$County)
```

I've decided to compare early, mid and late century trends. I'll use functions to simplify this, so I might more easily shift ranges later. We'll use the most recent 30 years (2014-1984), the early period ends at 1944, and we'll skip 5 years on either side

```{r}
early.f <- function(year) {
  return((year<1945)&(year>1923))
}
mid.f <- function(year) {
  return((year<1980)&(year>1948))
}
late.f <- function(year) {
  return((year<2020)&(year>1983))
}
county.early.dat <- subset(county.yield.dat,early.f(county.yield.dat$Year))
county.mid.dat <- subset(county.yield.dat,mid.f(county.yield.dat$Year))
county.late.dat <- subset(county.yield.dat,late.f(county.yield.dat$Year))
```




```{r}
grid.arrange(arrangeGrob(
  ggplot(county.early.dat, aes(Year,Value)) + geom_smooth(aes(group=State,color=State),weight=10,se = FALSE,method="lm"),
  ggplot(county.mid.dat, aes(Year,Value)) + geom_smooth(aes(group=State,color=State),weight=10,se = FALSE,method="lm"),
  ggplot(county.late.dat, aes(Year,Value)) + geom_smooth(aes(group=State,color=State),weight=10,se = FALSE,method="lm"),
   as.table=TRUE,
   ncol=1))
```


For comparison, also downloaded spring wheat data. All data. 
```{r}
county.spring.dat <- read.csv("./data/usda/1F443E55-9EB0-3CF3-AFD0-E133A50C559C.csv", header = TRUE)
county.spring.dat <- subset(county.spring.dat,county.spring.dat$State %in% levels(state.yield.dat$State))
county.spring.plot <- ggplot(county.spring.dat, aes(Year,Value)) 
county.spring.plot <- county.spring.plot + scale_colour_brewer(palette="Set1") 
county.spring.plot <- county.spring.plot + geom_smooth(aes(group= State,color=State),se = FALSE)
county.spring.plot
```




Bushels per acre, different cropping systems

```{r}
county.system.dat <- read.csv("./data/usda/9534B497-6FB0-31CC-9521-0ABD4EF91ED0.csv", header = TRUE)
county.system.dat$ItemLevel <- as.factor(as.numeric(county.system.dat$Data.Item))
#subset out spring wheat
county.system.dat <- subset(county.system.dat,county.system.dat$ItemLevel %in% c(9,10))
county.system.dat$ItemLevel <- "All"

county.system.dat$ItemLevel[county.system.dat$Data.Item=="WHEAT, WINTER, NON-IRRIGATED - YIELD, MEASURED IN BU / ACRE"] <- "Non-I"
#county.system.dat$ItemLevel[county.system.dat$Data.Item=="WHEAT, WINTER, NON-IRRIGATED, CONTINUOUS CROP - YIELD, MEASURED IN BU / ACRE"] <- "Cont."
#county.system.dat$ItemLevel[county.system.dat$Data.Item=="WHEAT, WINTER, NON-IRRIGATED, FOLLOWING SUMMER FALLOW - YIELD, MEASURED IN BU / ACRE"] <- "Fallow"
county.system.dat$ItemLevel <- as.factor(county.system.dat$ItemLevel)
#levels(county.system.dat$ItemLevel)
#levels(county.system.dat$Data.Item)
county.system.plot <- ggplot(county.system.dat, aes(Year,Value)) 
county.system.plot <- county.system.plot + geom_smooth(aes(group= ItemLevel,color=ItemLevel),se = FALSE)
county.system.plot
```




### HWW RPN
```{r}
rpn.dat <- read.csv("./data/wwheat/Statistics.csv", header = TRUE)
rpn.dat <- subset(rpn.dat,rpn.dat$Assessment=="GY")
rpn.dat <- subset(rpn.dat,rpn.dat$Statistic=="Mean")
rpn.dat$Value <- as.numeric(as.character(rpn.dat$Value))
rpn.dat$Trial <- as.factor(rpn.dat$Trial)
head(rpn.dat)

#convert to bu/acre
#Wheat/soybeans (60# bu)
#1 kilogram/hectare (kg/ha) = .0149 (.015) 
#bushels/acre
#1 bushel/acre = 67.25 (67) kilograms/hectare
rpn.dat$Value <- rpn.dat$Value * 0.0149

state.abbr <- c("ND","SD","NE","KS","OK","TX")
state.abbr.map <- c("north dakota","south dakota","nebraska","kansas","oklahoma","texas")
names(state.abbr.map) <- state.abbr 


#subset by state
locations.dat <- read.csv("./data/wwheat/Locations.csv", header = TRUE)
locations.dat <- subset(locations.dat, locations.dat$State %in% c("ND","SD","NE","KS","OK","TX"))
locations.dat$State <- as.character(locations.dat$State)
locations.dat$State <- state.abbr.map[locations.dat$State]

# this lets us map location name to a county and state
statecounty.map <- as.character(paste(locations.dat$State,locations.dat$County,sep=","))
locations.dat$statecounty <- statecounty.map
names(statecounty.map) <- as.character(locations.dat$Name)
#statecounty.map <- as.character(locations.dat$Name)
#names(statecounty.map) <- as.character(paste(locations.dat$State,locations.dat$County,sep=", "))
```

Now, generate an index
```{r}
county.yield.dat$statecounty <- as.character(paste(county.yield.dat$State,county.yield.dat$County,sep=","))
yield.gap.dat <- subset(county.yield.dat,county.yield.dat$statecounty %in% statecounty.map)
head(county.yield.dat)
head(yield.gap.dat)
```

Map nursery yield means to county means
```{r}
rpn.dat$statecounty <- statecounty.map[as.character(rpn.dat$Location)]
yield.gap.dat$statecountyyear <- paste(yield.gap.dat$statecounty,yield.gap.dat$Year)
rpn.dat$statecountyyear <- paste(rpn.dat$statecounty,rpn.dat$Cycle)
actual <- yield.gap.dat$Value
names(actual) <- as.character(yield.gap.dat$statecountyyear)
rpn.dat$Actual <- actual[rpn.dat$statecountyyear]

rpn.dat$Actual <- as.numeric(as.character(rpn.dat$Actual))
rpn.dat$Value <- as.numeric(as.character(rpn.dat$Value))
rpn.dat <- subset(rpn.dat,!is.na(rpn.dat$Actual))

rpn.dat$Year <- as.factor(rpn.dat$Cycle)

rpn.dat$Location <- as.factor(rpn.dat$Location)

yield.gap.plot <- ggplot(rpn.dat, aes(Value,Actual),xlab="Nursery Average",ylab="County Average")
yield.gap.plot <- yield.gap.plot + geom_point(aes(color=Year)) + geom_smooth(aes(group= Year,color=Year),se = FALSE,method="lm")
yield.gap.plot

gap.frame <- data.frame(
  Year =  c(rpn.dat$Cycle,rpn.dat$Cycle),
  Source = c(rep("Nursery",length(rpn.dat$Value)),rep("County",length(rpn.dat$Value))),
  Yield = c(rpn.dat$Value,rpn.dat$Actual)
)
gap.frame$Source <- as.factor(gap.frame$Source)
yield.gap2.plot <- ggplot(gap.frame, aes(Year,Yield))
#yield.gap2.plot <- yield.gap2.plot + geom_point(aes(color=Source)) + geom_smooth(aes(group=Source,color=Source),se = FALSE,method="lm")
yield.gap2.plot <- yield.gap2.plot + geom_point(aes(color=Source)) + geom_smooth(aes(group=Source,color=Source),se = FALSE)
yield.gap2.plot
```

Compute the gap
```{r}
nursery.counts <- tapply(rpn.dat$Value,list(rpn.dat$Location),length)
rpn.dat$Gap <- rpn.dat$Value - rpn.dat$Actual
rpn.dat$GapPercent <- 100*rpn.dat$Actual/rpn.dat$Value
rpn.dat$Count <- nursery.counts[rpn.dat$Location]
```

Some of the nurseries are irrigated; remove those
```{r}
rpn.dat$Irrigated <- FALSE
irrigated <- c("Bushland (Irr)","Goodwell","Goodwell (Irr)","Hugoton (Irr)","Imperial (Irr)")

rpn.dat$Irrigated[rpn.dat$Location%in%irrigated] <- TRUE

rpn.dat$Location <- as.factor(as.character(rpn.dat$Location))
levels(rpn.dat$Location)

rpndry.dat <- subset(rpn.dat, !rpn.dat$Irrigated)

rpndry.dat$Location <- as.factor(as.character(rpndry.dat$Location))
levels(rpndry.dat$Location)

yield.gap3.plot <- ggplot(rpndry.dat, aes(Value,Actual),xlab="Nursery Average",ylab="County Average")
yield.gap3.plot <- yield.gap3.plot + geom_point(aes(color=Year)) + geom_smooth(aes(group= Year,color=Year),se = FALSE,method="lm")
yield.gap3.plot

gap.frame <- data.frame(
  Year =  c(rpndry.dat$Cycle,rpndry.dat$Cycle),
  Source = c(rep("Nursery",length(rpndry.dat$Value)),rep("County",length(rpndry.dat$Value))),
  Yield = c(rpndry.dat$Value,rpndry.dat$Actual)
)
gap.frame$Source <- as.factor(gap.frame$Source)
yield.gap4.plot <- ggplot(gap.frame, aes(Year,Yield))
#yield.gap2.plot <- yield.gap2.plot + geom_point(aes(color=Source)) + geom_smooth(aes(group=Source,color=Source),se = FALSE,method="lm")
yield.gap4.plot <- yield.gap4.plot + geom_point(aes(color=Source)) + geom_smooth(aes(group=Source,color=Source),se = FALSE,method="lm")
yield.gap4.plot

yield.gap3a.plot <- ggplot(rpndry.dat, aes(Value,Actual),xlab="Nursery Average",ylab="County Average")
yield.gap3a.plot <- yield.gap3a.plot + geom_point(aes(color=Trial)) + geom_smooth(aes(group= Trial,color=Trial),se = FALSE,method="lm")
yield.gap3a.plot

```

Plot the actual gap by year

```{r}
rpndry.dat <- subset(rpndry.dat,rpndry.dat$Count>10)
summary(lm(Gap ~ Location + Cycle, data=rpndry.dat))
summary(lm(GapPercent ~ Location + Cycle, data=rpndry.dat))

summary(lm(Gap ~ Trial + Cycle, data=rpndry.dat))
summary(lm(GapPercent ~ Trial + Cycle, data=rpndry.dat))

yield.gap5.plot <- ggplot(rpndry.dat, aes(Cycle,Gap),xlab="Year",ylab="Gap")
yield.gap5.plot <- yield.gap5.plot + geom_point(aes(color=Location)) + geom_smooth(aes(group= Location,color=Location),se = FALSE,method="lm")
yield.gap5.plot

yield.gap6.plot <- ggplot(rpndry.dat, aes(Cycle,GapPercent),xlab="Year",ylab="Gap Percent")
yield.gap6.plot <- yield.gap6.plot + geom_point(aes(color=Location)) + geom_smooth(aes(group= Location,color=Location),se = FALSE,method="lm")
yield.gap6.plot

yield.gap6b.plot <- ggplot(rpndry.dat, aes(Cycle,GapPercent),xlab="Year",ylab="Gap Percent")
yield.gap6b.plot <- yield.gap6b.plot + geom_point(aes(color=Trial)) + geom_smooth(aes(group=Trial,color=Trial),se = FALSE,method="lm")
yield.gap6b.plot

gap.lm <- lm(Gap ~ 0 + Location + Location:Cycle, data=rpndry.dat)
gapper.lm <- lm(GapPercent ~ 0 + Location + Location:Cycle, data=rpndry.dat)
summary(gap.lm)
summary(gapper.lm)
```

Get the coefficients so we can map regression estimates
```{r}
labels <- attr(gap.lm$terms, "term.labels")
rpn.estimates <- gap.lm$coefficients[gap.lm$assign == 1]
rpn.year.estimates <- gap.lm$coefficients[gap.lm$assign == 2]
length(rpn.estimates)
length(rpn.year.estimates)
names(rpn.estimates) <- gap.lm$xlevels[[1]]
names(rpn.year.estimates) <- gap.lm$xlevels[[1]]
locations.dat$gapintercept <- rpn.estimates[as.character(locations.dat$Name)]
locations.dat$gapslope <- rpn.year.estimates[as.character(locations.dat$Name)]
```

```{r}
gapplot.dat <- subset(locations.dat, !is.na(locations.dat$gapslope))
norm.slopes <- gapplot.dat$gapslope/max(abs(1.05*gapplot.dat$gapslope))
pos.slopes <- norm.slopes
neg.slopes <- -norm.slopes
neg.slopes[neg.slopes<0] <- 0
pos.slopes[pos.slopes<0] <- 0

gapplot.dat$statecounty <- as.character(gapplot.dat$statecounty)

map.colors <- colorRampPalette(c('lightblue','darkblue'))(100)[floor(pos.slopes*100)+1]
neg.colors <- colorRampPalette(c('pink','red'))(100)[floor(neg.slopes*100)+1]
map.colors[norm.slopes<0] <-neg.colors[norm.slopes<0] 
map("county", regions = gapplot.dat$statecounty, col = map.colors, fill = TRUE, lty = 1, lwd= 1)
#map("county", regions = counties.dat$statecounty, col = "black", fill = FALSE, lty = 1, lwd = 1, add=TRUE)
```
Now we actually analyze county yield data. Note we need to redo subset since we've since
appended statecounty index
```{r}
county.early.dat <- subset(county.yield.dat,early.f(county.yield.dat$Year))
county.mid.dat <- subset(county.yield.dat,mid.f(county.yield.dat$Year))
county.late.dat <- subset(county.yield.dat,late.f(county.yield.dat$Year))


late.counts <- tapply(county.late.dat$Value,list(county.late.dat$statecounty),length)
county.late.dat$Count <- late.counts[county.late.dat$statecounty]
county.late.dat <- subset(county.late.dat,county.late.dat$Count>9)

late.lm <- lm(Value ~ Year,data=county.late.dat)
```

```{r}
late.state.lm <- lm(Value ~ 0 + State + State:Year,data=county.late.dat)
#summary(late.state.lm)

late.county.lm <- lm(Value ~ 0 + statecounty + statecounty:Year,data=county.late.dat)
#summary(late.county.lm)
```

```{r}
map.values <- function(values,regions,scale=NA) {
  if(is.na(scale)) {
    scale <- 1/max(abs(1.05*values))
  }
norm.slopes <- values*scale
pos.slopes <- norm.slopes
neg.slopes <- -norm.slopes
neg.slopes[neg.slopes<0] <- 0
pos.slopes[pos.slopes<0] <- 0


map.colors <- colorRampPalette(c('lightblue','darkblue'))(100)[floor(pos.slopes*100)+1]
neg.colors <- colorRampPalette(c('pink','red'))(100)[floor(neg.slopes*100)+1]
map.colors[norm.slopes<0] <-neg.colors[norm.slopes<0] 
map("county", regions = regions, col = map.colors, fill = TRUE, lty = 1, lwd= 1)
#map("county", regions = county.late.dat$statecounty, col = "black", fill = FALSE, lty = 1, lwd = 1, add=TRUE)
}

extract.county.estimates <- function(fitted.model,term=1) {
  labels <- attr(fitted.model$terms, "term.labels")
  estimates <- fitted.model$coefficients[fitted.model$assign == term]
  names(estimates) <- fitted.model$xlevels[[1]]
  return(estimates)
}
```

```{r}
rpn.late.estimates <- extract.county.estimates(late.county.lm,term=1)
rpn.late.year.estimates <- extract.county.estimates(late.county.lm,term=2)

common.scale <- max(abs(1.05*rpn.late.year.estimates))
#rpn.late.year.estimates <- late.county.lm$coefficients[late.county.lm$assign == 2]
length(rpn.late.estimates)
length(rpn.late.year.estimates)
#names(rpn.late.year.estimates) <- late.county.lm$xlevels[[1]]
county.late.dat$intercept <- rpn.late.estimates[as.character(county.late.dat$statecounty)]
county.late.dat$slope <- rpn.late.year.estimates[as.character(county.late.dat$statecounty)]
```



A quick double check on the model, compare with individual lm
```{r}
summary(lm(Value ~ Year,data=subset(county.late.dat,county.late.dat$statecounty=="kansas,allen")))
summary(lm(Value ~ Year,data=subset(county.late.dat,county.late.dat$statecounty=="kansas,anderson")))
summary(lm(Value ~ Year,data=subset(county.late.dat,county.late.dat$statecounty=="kansas,atchison")))

county.late.sum <- summary(late.county.lm)
```
Good.

```{r}
mid.counts <- tapply(county.mid.dat$Value,list(county.mid.dat$statecounty),length)
county.mid.dat$Count <- mid.counts[county.mid.dat$statecounty]
county.mid.dat <- subset(county.mid.dat,county.mid.dat$Count>9)
mid.lm <- lm(Value ~ 0 + statecounty + statecounty:Year,data=county.mid.dat)
#summary(mid.lm)


rpn.mid.estimates <- extract.county.estimates(mid.lm,term=1)
rpn.mid.year.estimates <- extract.county.estimates(mid.lm,term=2)
common.scale <- max(c(common.scale, max(abs(1.05*rpn.mid.year.estimates))))
```

```{r}
early.counts <- tapply(county.early.dat$Value,list(county.early.dat$statecounty),length)
county.early.dat$Count <- early.counts[county.early.dat$statecounty]
county.early.dat <- subset(county.early.dat,county.early.dat$Count>9)
early.lm <- lm(Value ~ 0 + statecounty + statecounty:Year,data=county.early.dat)
rpn.early.estimates <- extract.county.estimates(early.lm,term=1)
rpn.early.year.estimates <- extract.county.estimates(early.lm,term=2)
common.scale <- max(c(common.scale, max(abs(1.05*rpn.early.year.estimates))))
```


```{r}
map.values(rpn.late.year.estimates,names(rpn.late.year.estimates),1/common.scale)
map.values(rpn.mid.year.estimates,names(rpn.mid.year.estimates),1/common.scale)
map.values(rpn.early.year.estimates,names(rpn.early.year.estimates),1/common.scale)
```


### Weather 

http://wonder.cdc.gov/EnvironmentalData.html
List these options. 

Daily Air Temperatures and Heat Index (1979-2011) from North America Land Data Assimilation System (NLDAS) 
Data Request More information
Fine Particulate Matter (PM2.5) (µg/m³) (2003-2011) 
Data Request More information
Land Surface Temperature (LST) (2003-2008) from Moderate Resolution Imaging Spectroradiometer (MODIS) 
Data Request More information
Daily Sunlight (KJ/m²) (1979-2011) from North America Land Data Assimilation System (NLDAS) 
Data Request More information
Daily Precipitation (mm) (1979-2011) from North America Land Data Assimilation System (NLDAS) 
Data Request More information
Number of Heat Wave Days in May-September (1981-2010) 
Data Request More information


I've downloaded climate data from \verb|http://wonder.cdc.gov/EnvironmentalData.html|. We need to process the files.

```{r}
  if(!file.exists("min.lm.Rda")) {
  weather.dat <- read.csv("data/wonder/temp.csv", header = TRUE)
  weather.dat$Year <- as.numeric(weather.dat$Year)
  weather.dat$Year.Code <- as.numeric(weather.dat$Year.Code)
  weather.dat$County.Code <- as.numeric(weather.dat$County.Code)
  
  weather.dat <- subset(weather.dat,weather.dat$Year>1983)
  
  weather.dat$Avg.Daily.Max.Air.Temperature..C. <- as.numeric(weather.dat$Avg.Daily.Max.Air.Temperature..C.)
  weather.dat$Avg.Daily.Min.Air.Temperature..C. <- as.numeric(weather.dat$Avg.Daily.Min.Air.Temperature..C.)
  weather.dat$Avg.Daily.Max.Heat.Index..C. <- as.numeric(weather.dat$Avg.Daily.Max.Heat.Index..C.)
  weather.dat$County <- tolower(as.character(weather.dat$County))
  weather.dat$State <- tolower(as.character(weather.dat$State))
  weather.dat$statecounty <- paste(weather.dat$State,weather.dat$County,sep=",")

  weather.dat$statecounty <- as.factor(weather.dat$statecounty)

  min.lm <- lm(Avg.Daily.Max.Air.Temperature..C.~statecounty + statecounty:Year,data=weather.dat)
  max.lm <- lm(Avg.Daily.Min.Air.Temperature..C.~statecounty + statecounty:Year,data=weather.dat)
  heat.lm <- lm(Avg.Daily.Max.Heat.Index..C.~statecounty + statecounty:Year,data=weather.dat)
  
  precip.dat <- read.csv("data/wonder/precip.csv", header = TRUE)
  precip.dat$County <- tolower(as.character(precip.dat$County))
  precip.dat$State <- tolower(as.character(precip.dat$State))
  precip.dat$statecounty <- paste(precip.dat$State,precip.dat$County,sep=",")
  precip.lm <- lm(Avg.Daily.Precipitation..mm.~statecounty + statecounty:Year,data=precip.dat)

  sunlight.dat <- read.csv("data/wonder/sunlight.csv", header = TRUE)
  sunlight.dat$County <- tolower(as.character(sunlight.dat$County))
  sunlight.dat$State <- tolower(as.character(sunlight.dat$State))
  sunlight.dat$statecounty <- paste(sunlight.dat$State,sunlight.dat$County,sep=",")
  sun.lm <- lm(Avg.Daily.Sunlight..KJ.m..~statecounty + statecounty:Year,data=sunlight.dat)
  
  save(min.lm, file="min.lm.Rda")
  save(max.lm, file="max.lm.Rda")
  save(heat.lm, file="heat.lm.Rda")
  save(precip.lm, file="precip.lm.Rda")
  save(sun.lm, file="sun.lm.Rda")
   
  } else {
    load(file="min.lm.Rda")
    load(file="max.lm.Rda")
    load(file="heat.lm.Rda")
    load(file="precip.lm.Rda")
    load(file="sun.lm.Rda")
   }

```

The data are limited, so we subset data to match our recent yield data.

```{r}

```

Before we can use weather data, we need to process county names so we can copy this to our recent data set.

This part took to long, so I manually edited files

weather.dat$County <- as.character(weather.dat$County)
for(i in 1:length(weather.dat$County)) {
   current <- as.character(weather.dat$County[i])
   tmp <- strsplit(current," County")
   current <- tolower(tmp[[1]][1])
   weather.dat$County[i] <- current
}


```{r}
summary(aov(min.lm))
min.estimates <- extract.county.estimates(min.lm,term=2)
min.estimates[1:10]
```

map.values(min.estimates,names(min.estimates))

summary(aov(max.lm))
max.estimates <- extract.county.estimates(max.lm,term=2)
max.estimates[1:10]
map.values(max.estimates,names(max.estimates))

summary(aov(heat.lm))
heat.estimates <- extract.county.estimates(heat.lm,term=2)
heat.estimates[1:10]
map.values(heat.estimates,names(heat.estimates))

summary(aov(precip.lm))
precip.estimates <- extract.county.estimates(precip.lm,term=2)
precip.estimates[1:10]
map.values(precip.estimates,names(precip.estimates))


summary(aov(sun.lm))
sun.estimates <- extract.county.estimates(sun.lm,term=2)
sun.estimates[1:10]
map.values(sun.estimates,names(sun.estimates))


Don't forget to map "Month Code.


Fine particulate data and surface temperatures have different numbers of observations, we
need to process these separately.

```{r}
if(!file.exists("fine.lm.Rda")) {
fine.dat <- read.csv("data/wonder/fine.csv", header = TRUE)
surface.dat <- read.csv("data/wonder/surface.csv", header = TRUE)

fine.dat$County <- as.character(fine.dat$County)

fine.dat$State <- tolower(as.character(fine.dat$State))

surface.dat$County <- as.character(surface.dat$County)

surface.dat$State <- tolower(as.character(surface.dat$State))

fine.dat$statecounty <- paste(fine.dat$State,fine.dat$County,sep=",")
surface.dat$statecounty <- paste(surface.dat$State,surface.dat$County,sep=",")

fine.lm <- lm(Avg.Fine.Particulate.Matter~statecounty + statecounty:Year,data=fine.dat)
day.lm <- lm(Avg.Day.Land.Surface.Temperature~statecounty + statecounty:Year,data=surface.dat)
night.lm <- lm(Avg.Night.Land.Surface.Temperature~statecounty + statecounty:Year,data=surface.dat)

  save(fine.lm, file="fine.lm.Rda")
  save(day.lm, file="day.lm.Rda")
  save(night.lm, file="night.lm.Rda")   
  } else {
    load(file="fine.lm.Rda")
    load(file="day.lm.Rda")
    load(file="night.lm.Rda")
}
```

summary(aov(fine.lm))
fine.estimates <- extract.county.estimates(fine.lm,term=2)
fine.estimates[1:10]
map.values(fine.estimates,names(fine.estimates))

summary(aov(day.lm))
day.estimates <- extract.county.estimates(day.lm,term=2)
day.estimates[1:10]
map.values(day.estimates,names(day.estimates))

summary(aov(night.lm))
night.estimates <- extract.county.estimates(night.lm,term=2)
night.estimates[1:10]
map.values(night.estimates,names(night.estimates))



### Nutrients
http://nugis.ipni.net/Applications/


```{r}
ipni.dat <- read.csv("data/ipni/county_data_20120106_4_18.csv", header = TRUE)
ipni.dat$State <- tolower(as.character(ipni.dat$STATE_NAME))
```

We can use \verb|STATE_NAME|, \verb|GEO| to match to statecounty
```{r}
ipni.dat$County <- tolower(as.character(ipni.dat$GEO))
ipni.dat$statecounty <- paste(ipni.dat$State,ipni.dat$County,sep=",")
head(ipni.dat)
ipni.dat <- subset(ipni.dat,ipni.dat$statecounty %in% names(min.estimates))
```

```{r}
if(!file.exists("Farm_TonsN.lm.Rda")) {
  Farm_TonsN.lm <- lm(Farm_TonsN~statecounty + statecounty:Year,data=ipni.dat)
  Farm_TonsP.lm <- lm(Farm_TonsP ~ statecounty + statecounty:Year,data=ipni.dat)
  Farm_TonsK.lm <- lm(Farm_TonsK ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_N_Exc.lm <- lm(Tons_N_Exc ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_P2O5_Exc.lm <- lm(Tons_P2O5_Exc ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_K2O_Exc.lm <- lm(Tons_K2O_Exc ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_N_Recovered.lm <- lm(Tons_N_Recovered ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_P2O5_Recovered.lm <- lm(Tons_P2O5_Recovered ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_K2O_Recovered.lm <- lm(Tons_K2O_Recovered ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_N_Fixed_Legumes.lm <- lm(Tons_N_Fixed_Legumes ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_N_Rem.lm <- lm(Tons_N_Rem ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_P2O5_Rem.lm <- lm(Tons_P2O5_Rem ~ statecounty + statecounty:Year,data=ipni.dat)
  Tons_K2O_Rem.lm <- lm(Tons_K2O_Rem ~ statecounty + statecounty:Year,data=ipni.dat)
  BalanceN_Tons.lm <- lm(BalanceN_Tons ~ statecounty + statecounty:Year,data=ipni.dat)
  BalanceP2O5_Tons.lm <- lm(BalanceP2O5_Tons ~ statecounty + statecounty:Year,data=ipni.dat)
  BalanceK2O_Tons.lm <- lm(BalanceK2O_Tons ~ statecounty + statecounty:Year,data=ipni.dat)
  RatioN.lm <- lm(RatioN ~ statecounty + statecounty:Year,data=ipni.dat)
  RatioP2O5.lm <- lm(RatioP2O5 ~ statecounty + statecounty:Year,data=ipni.dat)
  RatioK2O.lm <- lm(RatioK2O ~ statecounty + statecounty:Year,data=ipni.dat)
  N_PPCA.lm <- lm(N_PPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  P2O5_PPCA.lm <- lm(P2O5_PPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  K2O_PPCA.lm <- lm(K2O_PPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  FarmNPPCA.lm <- lm(FarmNPPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  FarmPPPCA.lm <- lm(FarmPPPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  FarmKPPCA.lm <- lm(FarmKPPCA ~ statecounty + statecounty:Year,data=ipni.dat)
  X21Crop_TotalPlantedAc.lm <- lm(X21Crop_TotalPlantedAc ~ statecounty + statecounty:Year,data=ipni.dat)
  X21Crop_TotalHarvestAc.lm <- lm(X21Crop_TotalHarvestAc ~ statecounty + statecounty:Year,data=ipni.dat)
  Total_Harvested_Cropland_Acres.lm <- lm(Total_Harvested_Cropland_Acres ~ statecounty + statecounty:Year,data=ipni.dat)
  TotalCropland.lm <- lm(TotalCropland ~ statecounty + statecounty:Year,data=ipni.dat)
  
  save(Farm_TonsN.lm, file="Farm_TonsN.lm.Rda")
  save(Farm_TonsP.lm, file="Farm_TonsP.lm.Rda")
  save(Farm_TonsK.lm, file="Farm_TonsK.lm.Rda")
  save(Tons_N_Exc.lm, file="Tons_N_Exc.lm.Rda")
  save(Tons_P2O5_Exc.lm, file="Tons_P2O5_Exc.lm.Rda")
  save(Tons_K2O_Exc.lm, file="Tons_K2O_Exc.lm.Rda")
  save(Tons_N_Recovered.lm, file="Tons_N_Recovered.lm.Rda")
  save(Tons_P2O5_Recovered.lm, file="Tons_P2O5_Recovered.lm.Rda")
  save(Tons_K2O_Recovered.lm, file="Tons_K2O_Recovered.lm.Rda")
  save(Tons_N_Fixed_Legumes.lm, file="Tons_N_Fixed_Legumes.lm.Rda")
  save(Tons_N_Rem.lm, file="Tons_N_Rem.lm.Rda")
  save(Tons_P2O5_Rem.lm, file="Tons_P2O5_Rem.lm.Rda")
  save(Tons_K2O_Rem.lm, file="Tons_K2O_Rem.lm.Rda")
  save(BalanceN_Tons.lm, file="BalanceN_Tons.lm.Rda")
  save(BalanceP2O5_Tons.lm, file="BalanceP2O5_Tons.lm.Rda")
  save(BalanceK2O_Tons.lm, file="BalanceK2O_Tons.lm.Rda")
  save(RatioN.lm, file="RatioN.lm.Rda")
  save(RatioP2O5.lm, file="RatioP2O5.lm.Rda")
  save(RatioK2O.lm, file="RatioK2O.lm.Rda")
  save(N_PPCA.lm, file="N_PPCA.lm.Rda")
  save(P2O5_PPCA.lm, file="K2O_PPCA.lm.Rda")
  save(K2O_PPCA.lm, file="K2O_PPCA.lm.Rda")
  save(FarmNPPCA.lm, file="FarmNPPCA.lm.Rda")
  save(FarmPPPCA.lm, file="FarmPPPCA.lm.Rda")
  save(FarmKPPCA.lm, file="FarmKPPCA.lm.Rda")
  save(X21Crop_TotalPlantedAc.lm, file="X21Crop_TotalPlantedAc.lm.Rda")
  save(X21Crop_TotalHarvestAc.lm, file="X21Crop_TotalHarvestAc.lm.Rda")
  save(Total_Harvested_Cropland_Acres.lm, file="Total_Harvested_Cropland_Acres.lm.Rda")
  save(TotalCropland.lm, file="TotalCropland.lm.Rda")
} else {
    
  load(file="Farm_TonsN.lm.Rda")
    load(file="Farm_TonsP.lm.Rda")
    load(file="Farm_TonsK.lm.Rda")
    load(file="Tons_N_Exc.lm.Rda")
    load(file="Tons_P2O5_Exc.lm.Rda")
    load(file="Tons_K2O_Exc.lm.Rda")
    load(file="Tons_N_Recovered.lm.Rda")
    load(file="Tons_P2O5_Recovered.lm.Rda")
    load(file="Tons_K2O_Recovered.lm.Rda")
    load(file="Tons_N_Fixed_Legumes.lm.Rda")
    load(file="Tons_N_Rem.lm.Rda")
    load(file="Tons_P2O5_Rem.lm.Rda")
    load(file="Tons_K2O_Rem.lm.Rda")
    load(file="BalanceN_Tons.lm.Rda")
    load(file="BalanceP2O5_Tons.lm.Rda")
    load(file="BalanceK2O_Tons.lm.Rda")
    load(file="RatioN.lm.Rda")
    load(file="RatioP2O5.lm.Rda")
    load(file="RatioK2O.lm.Rda")
    load(file="N_PPCA.lm.Rda")
    load(file="P2O5_PPCA.lm.Rda")
    load(file="K2O_PPCA.lm.Rda")
    load(file="FarmNPPCA.lm.Rda")
    load(file="FarmPPPCA.lm.Rda")
    load(file="FarmKPPCA.lm.Rda")
    load(file="X21Crop_TotalPlantedAc.lm.Rda")
    load(file="X21Crop_TotalHarvestAc.lm.Rda")
    load(file="Total_Harvested_Cropland_Acres.lm.Rda")
    load(file="TotalCropland.lm.Rda")
    }
 summary(aov(Farm_TonsN.lm))
 summary(aov(Farm_TonsP.lm))
 summary(aov(Farm_TonsK.lm))
 summary(aov(Tons_N_Exc.lm))
 summary(aov(Tons_P2O5_Exc.lm))
 summary(aov(Tons_K2O_Exc.lm))
 summary(aov(Tons_N_Recovered.lm))
 summary(aov(Tons_P2O5_Recovered.lm))
 summary(aov(Tons_K2O_Recovered.lm))
 summary(aov(Tons_N_Fixed_Legumes.lm))
 summary(aov(Tons_N_Rem.lm))
 summary(aov(Tons_P2O5_Rem.lm))
summary(aov(Tons_K2O_Rem.lm))
summary(aov(BalanceN_Tons.lm))
summary(aov(BalanceP2O5_Tons.lm))
summary(aov(BalanceK2O_Tons.lm))
summary(aov(RatioN.lm))
summary(aov(RatioP2O5.lm))
  summary(aov(RatioK2O.lm))
 summary(aov(N_PPCA.lm))
 summary(aov(P2O5_PPCA.lm))
 summary(aov(K2O_PPCA.lm))
 summary(aov(FarmNPPCA.lm))
 summary(aov(FarmPPPCA.lm))
 summary(aov(FarmKPPCA.lm))
 summary(aov(X21Crop_TotalPlantedAc.lm))
 summary(aov(X21Crop_TotalHarvestAc.lm))
 summary(aov(Total_Harvested_Cropland_Acres.lm))
 summary(aov(TotalCropland.lm))
```






Climate Data Online
http://www.ncdc.noaa.gov/cdo-web/
Submitted query by searching for SD
1984-2014
Monthly summary
Summary is limited to 5000 location years, this is 27,712 Station Years, so must include multiple stations per county (66)





Plant Available Water from USDA NASS? See Clay's paper in Global Food Security

### Quickstats Lite
Gives different options, more columns at one time.

http://www.nass.usda.gov/Quick_Stats/Lite/









Aquifer Data
 USGS High Plains Water-Level Monitoring Study
http://ne.water.usgs.gov/ogw/hpwlms/data.html
County and state level data, downloaded as individual files

HWW RPN
http://www.ars.usda.gov/Main/docs.htm?docid=11932

References

ray.d-12-2012
- yield unchanging, stagnating, collapsing, increasing.
ray.d-2013
cites yield increases in ND, SD, based on crop census reports 1989-2008


clay.d-01-2014
Show yield gaps w.r.t. corn in SD

Wheat Yields
graybosch.r-2014

Wheat Yields in France
brisson.n-10-2010

Periods in yields
thompson.l-01-1988

Small yield gains in corn
farfan.i-2013

Europe
moore.f-03-2015

Open Data
carolan.l-2015

brklacich.m-1995
CERES-wheat model in Canada






