---
title: "Correlograms"
author: "Peter Claussen"
date: "9/5/2017"
output:
  html_document: default
  pdf_document: default
---

# Libraries

### nlme : Linear and Nonlinear Mixed Effects Models
```{r}
library(nlme)
```

# Data

```{r}
load(file="autocorrelation.Rda")
attach(autocorrelation.dat)

load(file="sample.dat.Rda")
sample.pass14.dat <- sample.dat[sample.dat$PassNum==14,]
sample.pass15.dat <- sample.dat[sample.dat$PassNum==15,]
```

Let's reconsider the sample lag-1 autocorrelation coefficient $r_1$. Suppose we generalize this to an arbitrary lag distance $k$, by

$$
r_k = \frac{\Sigma _{i=1} ^ {n-k} (y_{i}-\bar{y})(y_{i-k}-\bar{y})}
{\Sigma _{i=1} ^n (y_i - \bar{y})^2}
$$
and 
$$\bar{y} = (\Sigma y_i)/n $$
is the sample mean.


Note that for lag 0, we have

$$
r_0 = \frac{\Sigma _{i=1} ^ {n} (y_{i}-\bar{y})(y_{i}-\bar{y})}
{\Sigma _{i=1} ^n (y_i - \bar{y})^2} = 1
$$

We can modify our autocorrelation function to work with an arbitrary lag,

```{r}
auto.correlation <- function(univariate,k=1) {
  x.bar <- mean(univariate)
  ss <- sum((univariate-x.bar)^2)
  n <- length(univariate)
  lag.ss <- sum((univariate[(1+k):n]-x.bar)*(univariate[1:(n-k)]-x.bar))
  return(lag.ss/ss)
}
```

# Example (Simulated) Data

We'll keep using the same simulated data as before.

First, test this function with white noise

```{r}
auto.correlation(white.noise,k=1)
auto.correlation(white.noise,k=2)
auto.correlation(white.noise,k=3)
```

We expect small $r_k$ for all $k$, since white noise values should be independent.

```{r}
auto.correlation(autoregressive,k=1)
auto.correlation(autoregressive,k=2)
auto.correlation(autoregressive,k=3)
```
With simple autoregression, we see correlation coefficient approximating $\alpha$ at $k=1$
and decreasing as we increase the gap $k$ between values.


We might want to visualize how autocorrelation changes with lag; this will help us understand the process that creates a sequence of values. 

```{r,fig.width=8,fig.height=4}
autoregressive.r <- rep(0,20)
for(i in 1:20) {
  autoregressive.r[i] <- auto.correlation(autoregressive,k=i)
}
plot(1:20,autoregressive.r)
```

This is an example of an autocorrelation plot, sometimes called a correlogram.

We can also use the function `acf` from `nlme`
```{r,fig.width=6,fig.height=3}
autoregressive.acf = acf(autoregressive,lag.max=50)
plot(autoregressive.acf$lag,autoregressive.acf$acf)
```

```{r,fig.width=6,fig.height=3}
plot(autoregressive.acf)
```


```{r,fig.width=6,fig.height=3}
white.noise.acf = acf(white.noise,lag.max=50)
plot(white.noise.acf$lag,white.noise.acf$acf)
```

```{r,fig.width=6,fig.height=3}
random.walk.acf = acf(random.walk,lag.max=50)
plot(random.walk.acf$lag,random.walk.acf$acf)
```

```{r,fig.width=6,fig.height=3}
moving.average.acf = acf(moving.average,lag.max=50)
plot(moving.average.acf$lag,moving.average.acf$acf)
```

```{r,fig.width=6,fig.height=3}
trend.error.acf = acf(trend.error,lag.max=50)
plot(trend.error.acf$lag,trend.error.acf$acf)
```


# Autocorrelation plots from Yield Monitor Data

We'll consider autocorrelation by observation within a single pass.

```{r,fig.width=8,fig.height=4}
plot(sample.pass14.dat$Yield)
```

```{r,fig.width=8,fig.height=4}
trend.error.acf = acf(sample.pass14.dat$Yield,lag.max=50)
```

```{r,fig.width=8,fig.height=4}
plot(sample.pass15.dat$Yield)
```

```{r,fig.width=8,fig.height=4}
trend.error.acf = acf(sample.pass15.dat$Yield,lag.max=50)
```

```{r,fig.width=8,fig.height=4}
trend.error.acf = acf(sample.pass14.dat$Distance,lag.max=50)
```


```{r,fig.width=8,fig.height=4}
trend.error.acf = acf(sample.pass14.dat$Moisture,lag.max=50)
```


# Variogram

We've used a measure of correlation that depends on calculating a mean $\bar{y}$. Now suppose we wish to use a measure of difference between observations that is independent of a mean. We write

$$
\gamma _k = \frac{\Sigma _{i=1} ^ {n-k} (y_{i}-y_{i-k})^2}
{2(n-k)}
$$

and implement this as

```{r}
auto.correlation <- function(univariate,k=1) {
  n <- length(univariate)
  lag.ss <- sum((univariate[(1+k):n]-univariate[1:(n-k)])^2)
  return(lag.ss/(n-k))
}
```

```{r,fig.width=8,fig.height=4}
autoregressive.r <- rep(0,20)
for(i in 1:20) {
  autoregressive.r[i] <- auto.correlation(autoregressive,k=i)
}
plot(1:20,autoregressive.r)
```

This is an example of a variogram, which we'll consider in more detail when we move to two dimensional analysis.



