---
title: "Misc"
author: "Peter Claussen"
date: "9/5/2017"
output:
  html_document: default
---

Let's consider a full field,

```{r}
web_yield_r.dat <- read.csv("web_yield_r.csv",header=TRUE)
web_yield_v.dat <- read.csv("web_yield_v.csv",header=TRUE)
```

```{r}
summary(web_yield_r.dat)
summary(web_yield_v.dat)
```



Let's consider head up - head down.

```{r}
web_yield_v.dat$HeaderMovement  <- "Steady"
web_yield_v.dat$HeaderEventIndex <- -100
web_yield_v.dat$EventNumber <- 0
currentIdx <- 0
lastEvent <- 0
range = 20
state <- web_yield_v.dat$Header[20]
i <- range+1
rows <- dim(web_yield_v.dat)[1]
EventNumber <- 1

while(i<(rows-range)) {
  #what is the current event?
  current <- web_yield_v.dat$Header[i]
  if(current!=state) {
    #we have a change in header position, from i-1 to i. Index.
    #Keep i at 0
    web_yield_v.dat$HeaderEventIndex[(i+1):(i+range)] <- 1:range
    web_yield_v.dat$HeaderEventIndex[(i-range):(i-1)] <- -(range:1)
    web_yield_v.dat$HeaderEventIndex[i] <- 0
    state <- current
    if((i-lastEvent)>range) {
      if(current=="Up") {
        web_yield_v.dat$HeaderMovement[(i-range):(i+range)]  <- "MovingUp"
      } else {
        web_yield_v.dat$HeaderMovement[(i-range):(i+range)]  <- "MovingDown"
      } 
    } else {
      web_yield_v.dat$HeaderMovement[(i-range):(i+range)]  <- "Jumps"
    }
    #this is inefficient, but it makes sure that steady state, head down has an event number.
    #we can use this for pass number.
    web_yield_v.dat$EventNumber[(i-range):rows] <- EventNumber
    lastEvent <- i
    i = i+range
    EventNumber <- EventNumber+1
  } else {
    i=i+1
  }
}
```

```{r}
movement.dat <- subset(web_yield_v.dat,web_yield_v.dat$HeaderMovement != "Steady")
plot(GrainMassFlow ~HeaderEventIndex,data=movement.dat[movement.dat$HeaderMovement=="MovingUp",])
plot(GrainMassFlow ~HeaderEventIndex,data=movement.dat[movement.dat$HeaderMovement=="MovingDown",])
```

```{r}
plot(GrainMassFlow ~HeaderEventIndex,data=movement.dat[movement.dat$HeaderMovement=="Jumps",])
```

```{r}
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
ggplot(web_yield_v.dat, aes(Longitude, Latitude)) + 
geom_point(aes(colour = GrainMassFlow),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[5]) +
labs(colour = "Flow", x="Longitude (m)", y="Latitude (m)", title = "Sample Yield Monitor Data")
```

```{r}
ggplot(web_yield_v.dat, aes(Longitude, Latitude)) + 
geom_point(aes(colour = HeaderMovement),size=1) + 
labs(colour = "Header", x="Longitude (m)", y="Latitude (m)", title = "Sample Yield Monitor Data")
```

```{r}
ggplot(web_yield_v.dat, aes(Longitude, Latitude)) + 
geom_point(aes(colour = EventNumber),size=1) + 
labs(colour = "Header", x="Longitude (m)", y="Latitude (m)", title = "Sample Yield Monitor Data")
```





min.lat <- min(trimmed.dat$Latitude)
max.lat <- max(trimmed.dat$Latitude)
lat.rng <- max.lat-min.lat
mid.lat <- (max.lat+min.lat)/2
trimmed.dat$Sample <- trimmed.dat$Latitude<(mid.lat + (lat.rng/40)) & 
                      trimmed.dat$Latitude>(mid.lat - (lat.rng/40))
sample.dat <- subset(trimmed.dat,trimmed.dat$Sample)






sample.dat$LonM <- sample.dat$Longitude - min(sample.dat$Longitude)
sample.dat$LatM <- sample.dat$Latitude - min(sample.dat$Latitude)
latMid <- (min(sample.dat$Latitude) + max(sample.dat$Latitude))/2
m_per_deg_lat = 111132.954 - 559.822 * cos( 2.0 * latMid ) + 1.175 * cos( 4.0 * latMid)
m_per_deg_lon = (3.14159265359/180 ) * 6367449 * cos ( latMid )
sample.dat$LonM <- sample.dat$LonM*m_per_deg_lon
sample.dat$LatM <- sample.dat$LatM*m_per_deg_lat

sample.dat$PassNum <- as.factor(sample.dat$PassNum)
pass.data <- data.frame(
  PassNum = as.integer(levels(sample.dat$PassNum)),
  Longitude = tapply(sample.dat$Longitude,list(sample.dat$PassNum),mean),
  ID = tapply(sample.dat$ID,list(sample.dat$PassNum),mean),
  Elevation = tapply(sample.dat$Elevation,list(sample.dat$PassNum),mean),
  CropFlwV = tapply(sample.dat$CropFlwV,list(sample.dat$PassNum),mean),
  Distance = tapply(sample.dat$Distance,list(sample.dat$PassNum),mean),
  Moisture = tapply(sample.dat$Moisture,list(sample.dat$PassNum),mean),
  YldVolDry = tapply(sample.dat$YldVolDry,list(sample.dat$PassNum),mean)
)
