agridat
========================================================
```{r}
library(agridat)
```
Agridat is a pretty good R package with data sets from a variety of sources. There is signficant overlap with ARMR, so I'm making notes.

According to Wright, "Some of the examples use the asreml package since it is the only option for fitting mixed models with complex variance structures to large datasets, and also the only option (even for small datasets) for modelling AR1xAR1 structures. "


From the help page, organized by analysis type

Uniformity trials with a single genotype
----------------------------------------

### baker.barley.uniformity
```{r}
dat <- baker.barley.uniformity

desplot(yield~col*row|year, data=dat, main="Heatmaps by year")
dat2 <- aggregate(yield ~ row*col, data=dat, FUN=mean, na.rm=TRUE)
asp <- (161*3+30)/827 # True aspect ratio

desplot(yield~col*row, data=dat2, main="Avg yield over 10 years", aspect=asp)
# Note lower yield in upper right, slanting to left a bit due to sandy soil.

# Baker fig 2, stdev vs mean
dat3 <- aggregate(yield ~ row*col, data=dat, FUN=sd, na.rm=TRUE)

plot(dat2$yield, dat3$yield, xlab="Mean yield", ylab="Std Dev yield")

# Baker table 4, correlation of plots across years
require(reshape2)
mat <- acast(dat, row+col~year)
round(cor(mat, use='pair'),2)
```

### batchelor.apple.uniformity
```{r}
require(lattice)

# Apple
dat <- batchelor.apple.uniformity
desplot(yield~col*row, dat, aspect=30/16,
          main="Jonathon apple tree yields")
```
### batchelor.lemon.uniformity
```{r}
# Lemon
dat <- batchelor.lemon.uniformity
desplot(yield~col*row, dat, aspect=26/14,
          main="Eureka lemon tree yields")
```
### batchelor.navel1.uniformity
```{r}
# Navel1 (Arlington)
dat <- batchelor.navel1.uniformity
desplot(yield~col*row, dat, aspect=50/20,
          main="Navel orange tree yields (Arlington)")
```
### batchelor.navel2.uniformity
```{r}
# Navel2 (Antelope)
dat <- batchelor.navel2.uniformity
desplot(yield~col*row, dat, aspect=33/15,
          main="Navel orange tree yields (Antelope)")
```
### batchelor.valencia.uniformity
```{r}
# Valencia
dat <- batchelor.valencia.uniformity
desplot(yield~col*row, dat, aspect=20/12,
          main="Valencia orange tree yields")
```
### batchelor.walnut.uniformity
```{r}
# Walnut
dat <- batchelor.walnut.uniformity
desplot(yield~col*row, dat, aspect=32/10,
          main="Seedling walnut yields")
```

garber.multi.uniformity	 45 x 6	 xy, 2 years/crops	
gomez.rice.uniformity	 18 x 36	 xy	 aov
goulden.barley.uniformity	 20 x 20	 xy	
harris.multi.uniformity	 2 x 23	 xy, 23 crops	 corrgram
immer.sugarbeet.uniformity	 10 x 60	 xy, 3 traits	
kempton.barley.uniformity	 7 x 28	 xy	
li.millet.uniformity	 6 x 100	 xy	
lyon.potato.uniformity	 34 x 6	 xy	
mercer.wheat.uniformity	 25 x 20	 xy, 2 traits	 spplot
odland.soybean.uniformity	 25 x 42	 xy	
odland.soyhay.uniformity	 28 x 55	 xy	
smith.corn.uniformity	 6 x 20	 xy, 3 years	 rgl
stephens.sorghum.uniformity	 100 x 20	 xy	
wiebe.wheat.uniformity	 12 x 125	 xy	 medianpolish, loess
williams.barley.uniformity	 48 x 15	 xy	 loess
williams.cotton.uniformity	 24 x 12	 xy	 loess

Animals
-------
name	 gen	 loc	 years	 trt	 other	 model
diggle.cow				 4	 ts	
henderson.milkfat						 nls,lm,glm,gam
ilri.sheep	 4		 6		 diallel	 lmer, asreml
zuidhof.broiler					 ts	

Trees
-----

name	 gen	 loc	 reps	 years	 trt	 other	 model
archbold.apple	 2		 5		 24	 split-split	 lmer
box.cork						 repeated	 radial, asreml
harris.wateruse	 2				 2	 repeated	 asreml
lavoranti.eucalyptus	 70	 7					 svd
pearce.apple			 4		 6	 cov	 lm,lmer
williams.trees	 37	 62		

Field and horticulture crops
----------------------------


name	 gen	 loc	 reps	 years	 trt	 other	 model
adugna.sorghum	 28	 13		 5			
aastveit.barley	 15			 9		 Yr*Gen~Yr*Trait	 pls
allcroft.lodging	 32	 7				 percent	 tobit

### ars.earlywhitecorn96
```{r}
require(lattice)
dat <- ars.earlywhitecorn96
# These views emphasize differences between locations
dotplot(gen~yield, dat, group=loc, auto.key=list(columns=3),
        main="ars.earlywhitecorn96")
dotplot(gen~stalklodge, dat, group=loc, auto.key=list(columns=3),
        main="ars.earlywhitecorn96")
splom(~dat[,3:9], group=dat$loc, auto.key=list(columns=3))
```

### australia.soybean
```{r}
dat <- australia.soybean
dm <- melt(dat, id.var=c('env', 'year','loc','gen'))

# Joint plot of genotypes & traits. Similar to Figure 1 of Kroonenberg 1989
dmat <- acast(dm, gen~variable, fun=mean)
dmat <- scale(dmat)
biplot(princomp(dmat), main="australia.soybean trait x gen biplot", cex=.75)

# Figure 1 of Kozak 2010, lines 44-58
dmat2 <- dmat[44:58,]
require("lattice")
parallelplot(dmat2[,c(2:6,1)], horiz=FALSE)
```

### besag.bayesian
TODO asreml
```{r}
dat <- besag.bayesian

# Yield values were scaled to unit variance
var(dat$yield, na.rm=TRUE)

# Besag Fig 2. Reverse row numbers to match Besag, Davison
dat$rrow <- 76 - dat$row
library("lattice")
xyplot(yield ~ rrow|col, dat, layout=c(1,3), type='s')

## Not run: 
# Use asreml to fit a model with AR1 gradient in rows
#require(asreml)
#dat <- transform(dat, cf=factor(col), rf=factor(rrow))
#m1 <- asreml(yield ~ -1 + gen, data=dat, random=~ar1v(rf))

# Visualize trends, similar to Besag figure 2.
#dat$res <- resid(m1)
#dat$geneff <- coef(m1)$fixed[as.numeric(dat$gen)]
#dat <- transform(dat, fert=yield-geneff-res)
#xyplot(geneff ~ rrow|col, dat, layout=c(1,3), type='s',
#       main="Variety effects", ylim=c(5,15 ))
#xyplot(fert ~ rrow|col, dat, layout=c(1,3), type='s',
#       main="Fertility", ylim=c(-2,2))
#xyplot(res ~ rrow|col, dat, layout=c(1,3), type='s',
#       main="Residuals", ylim=c(-4,4))
```

besag.elbatan	 50		 3			 xy	 lm, gam
besag.met	 64	 6	 3			 xy, incblock	 asreml, lme
blackman.wheat	 12	 7			 2		 biplot
bond.diallel	 6*6				 9		 diallel
bridges.cucumber	 4	 2	 4			 xy, latin, hetero	 asreml
caribbean.maize		 17	 4		 3		
carmer.density	 8				 4		 nls
cochran.bib	 13	 13				 BIB	 aov, lme
cochran.crd					 7	 xy, crd	 aov
cochran.latin			 6		 6	 xy, latin	 aov
cochran.wireworms			 5		 5	 xy, latin	 glm
cochran.eelworms			 4		 5	 xy	 aov
corsten.interaction	 20	 7					
crossa.wheat	 18	 25					 AMMI
crowder.seeds	 2		 21		 2		 glm,jags
cox.stripsplit			 4		 3,4,2		 aov
darwin.maize			 12		 2		 t.test
denis.missing	 5	 26					 lme
denis.ryegrass	 21	 7					 aov
digby.jointregression	 10	 17			 4		 lm
durban.competition	 36		 3			 xy, competition	 lm
durban.rowcol	 272		 2			 xy	 lm, gam, asreml
durban.splitplot	 70		 4		 2	 xy	 lm, gam, asreml
eden.potato			 4	 3	 4-12	 xy, rcb, latin	 aov
engelstad.nitro		 2		 5	 6		 nls quadratic plateau
fan.stability	 13	 10		 2		 3-way	 stability
federer.diagcheck	 122					 xy	 lm, lmer, asreml
federer.tobacco			 8		 7	 xy	 lm
gathmann.bt	 2		 8				 TOST
gauch.soy	 7	 7	 4	 12			 AMMI
gilmour.serpentine	 108		 3			 xy, serpentine	 asreml
gilmour.slatehall	 25		 6			 xy	 asreml
gomez.fractionalfactorial			 2		 6	 xy	 lm
gomez.groupsplit	 45		 3		 2	 xy, 3 gen groups	 aov

### gomez.multilocsplitplot
```{r}
dat <- gomez.multilocsplitplot

# Gomez figure 8.3
xyplot(yield~nitro, dat, group=loc, type=c('p','smooth'), auto.key=TRUE)

# AOV
# Be careful to use the right stratum, 'nf' appears in both strata.
# Still not quite the same as Gomez table 8.21
dat$nf <- factor(dat$nitro)
t1 <- terms(yield ~ loc * nf * gen + Error(loc:rep:nf),
            "Error", keep.order=TRUE)
m1 <- aov(t1, data=dat)
summary(m1)

# F values are somewhat similar to Gomez Table 8.21
require(lme4)
m2 <- lmer(yield ~ loc*nf*gen + (1|loc/rep/nf), dat)
anova(m2)
```

### gomez.nitrogen
```{r}
dat <- gomez.nitrogen

# Note the depletion of nitrogren over time (stage)
library(HH)
interaction2wt(nitro ~ rep/trt + trt*stage, data=dat)
# Just the fertilizer profiles
with(dat, interaction.plot(stage, trt, nitro, col=1:4, lty=1:3))

# Gomez table 6.16
m1 <- aov(nitro ~ Error(rep/trt) + trt*stage, data=dat)
summary(m1)

# Gomez table 6.18
# Treatment                    1 2 3 4 5 6 7 8
cont <- cbind("T7 vs others" = c( 1, 1, 1, 1, 1, 1,-7, 1),
              "T8 vs others"  = c( 1, 1, 1, 1, 1, 1, 0,-6),
              "T2,T5 vs others"   = c(-1, 2,-1,-1, 2,-1, 0, 0),
              "T2 vs T5"       = c( 0, 1, 0, 0,-1, 0, 0, 0))
contrasts(dat$trt) <- cont
contrasts(dat$trt)

m2 <- aov(nitro ~ Error(rep/trt) + trt*stage, data=dat)
summary(m2, expand.split=FALSE,
        split=list(trt=list(
                     "T7 vs others"=1,
                     "T8 vs others"=2,
                     "T2,T5 vs others"=3,
                     "T2 vs T5"=4,
                     rest=c(5,6,7)),
          "trt:stage"=list(
            "(T7 vs others):P"=c(1,8),
            "(T8 vs others):P"=c(2,9),
            "(T2,T5 vs others):P"=c(3,10),
            "(T2 vs T5):P"=c(4,11),
            "rest:P"=c(5,6,7,12,13,14))
          ))

```

gomez.seedrate			 4		 6	 rate	 lm
gomez.splitsplit	 3		 3			 xy, nitro, mgmt	 aov, lmer
gomez.stripplot	 6		 3			 xy, nitro	 aov
gomez.stripsplitplot	 6		 3			 xy, nitro	 aov
gotway.hessianfly	 16		 4			 xy	 lmer
graybill.heteroskedastic	 4	 13				 hetero	
hanks.sprinkler	 3		 3			 xy	 asreml
hayman.tobacco	 8		 2				 diallel
hernandez.nitrogen		 5	 4				 lm, nls
hildebrand.systems		 14			 4		 asreml
holshouser.splitstrip	 4		 4		 2*4		 lmer
hughes.grapes			 3		 6	 binomial	 lmer, aod, glmm
ivins.herbs	 13		 6			 2 traits	 lm, friedman
jenkyn.mildew			 9		 4		 lm
john.alpha	 24		 3			 alpha	 lm, lmer
kempton.competition	 36		 3			 xy, competition	 lme AR1
kempton.rowcol	 35		 2			 xy, row-col	 lmer
kempton.slatehall	 25		 6			 xy	 asreml, lmer
lyons.wheat		 12		 4			
mcconway.turnip	 2		 4		 2,4	 hetero	 aov, lme
mead.cowpeamaize	 3,2		 3		 4	 intercrop	
mead.germination			 4		 4,4	 binomial	 glm
mead.strawberry	 8		 4				
minnesota.barley.weather		 6		 10			
minnesota.barley.yield	 22	 6		 10			 dotplot
ortiz.tomato	 15	 18			 16	 Env*Gen~Env*Cov	 pls
pacheco.soybean	 18	 11					 AMMI
rothamsted.brussels			 4		 6		
ryder.groundnut	 5		 4			 xy, rcb	 lm
senshu.rice		 40					 lm,Fieller
shafii.rapeseed	 6	 14	 3	 3			 biplot
snedecor.asparagus			 4	 4	 4		 split-plot, antedependence
steel.soybeanmet	 12	 3	 3				
streibig.competition	 2		 3				 glm
stroup.nin	 56		 4			 xy	 asreml
stroup.splitplot			 4				 asreml, MCMCglmm
student.barley	 2	 51		 6			 lmer
talbot.potato	 9	 12				 Gen*Env~Gen*Trait	 pls
theobald.covariate	 10	 7	 5			 cov	 jags
thompson.cornsoy		 5		 33		 repeated measures	 aov
vargas.wheat1	 7			 6		 G*Y~G*Trait, Y*G~Y*Cov	 pls
vargas.wheat2	 8	 7				 Env*Gen~Env*Cov	 pls
verbyla.lupin	 9	 8		 2		 xy, density	
vsn.lupin3	 336	 3				 xy	 asreml
wedderburn.barley	 10	 9				 percent	 glm
yan.winterwheat	 18	 9					 biplot
yates.missing			 10		 3^2	 factorial	 lm, pca
yates.oats	 3		 6			 xy, nitro	 lmer


Time series
-----------
name	 years	 trt	 other	 model
byers.apple				 lme
broadbalk.wheat	 74	 17		
hessling.argentina	 30		 temp,precip	
lambert.soiltemp	 1	 7		
nass.barley	 146			
nass.corn	 146			
nass.cotton	 146			
nass.hay	 104			
nass.sorghum	 93			
nass.wheat	 146			
nass.rice	 117			
nass.soybean	 88	


Other
-----
name	 model
beall.borers	 glm
cate.potassium	 cate-nelson
cleveland.soil	 loess 2D
johnson.blight	 logistic regression
nebraska.farmincome	 choropleth
pearl.kernels	 chisq
waynick.soil	


