Bayesian
========================================================

Use examples from che.x-2010 "Bayesian data analysis for agricultural experiments"
BUGS
JAGS
stan

Simplest problem, RCB with missing values.


```{r}
library(ARMR)
data(Geisbrecht)

Table5.7 <- subset(Table5.7,!is.na(Table5.7$obs))

lm1 <- lm(obs ~ rep + trt,data=Table5.7)

anova(lm1)
```

We want to compare Bayesian estimates of $\sigma$ and $\sigma_b$ to REML estimates, and to fixed effects estimates.

```{r}
library(nlme)
lme1 <- lme(obs ~ trt, random= ~ 1 | rep, data=Table5.7)
lme1
ranef(lme1)
```

Stan
-----



Need to create
~/.R/Makevars

CXX=g++ -arch x86_64 -ftemplate-depth-256 -stdlib=libstdc++

Test intallation
```{r}
# using library inline to compile a C++ code on the fly
library(inline) 
library(Rcpp)
src <- ' 
  std::vector<std::string> s; 
  s.push_back("hello");
  s.push_back("world");
  return Rcpp::wrap(s);
'
hellofun <- cxxfunction(body = src, includes = '', plugin = 'Rcpp', verbose = FALSE)
cat(hellofun(), '\n') 
```

Installation
```
options(repos = c(getOption("repos"), rstan = "http://wiki.rstan-repo.googlecode.com/git/"))
install.packages('rstan', type = 'source')
```

```{r}
library(rstan) 
set_cppo("fast")  # for best running speed
#set_cppo('debug') # make debug easier
```

Example
```{r}
schools_code <- '
  data {
    int<lower=0> J; // number of schools 
    real y[J]; // estimated treatment effects
    real<lower=0> sigma[J]; // s.e. of effect estimates 
  }
  parameters {
    real mu; 
    real<lower=0> tau;
    real eta[J];
  }
  transformed parameters {
    real theta[J];
    for (j in 1:J)
      theta[j] <- mu + tau * eta[j];
  }
  model {
    eta ~ normal(0, 1);
    y ~ normal(theta, sigma);
  }
'

schools_dat <- list(J = 8, 
                    y = c(28,  8, -3,  7, -1,  1, 18, 12),
                    sigma = c(15, 10, 16, 11,  9, 11, 10, 18))

fit <- stan(model_code = schools_code, data = schools_dat, 
            iter = 1000, chains = 4)
print(fit)
```


```
J <- 8
y <- c(28,  8, -3,  7, -1,  1, 18, 12)
sigma_y <- c(15, 10, 16, 11,  9, 11, 10, 18)

schools_dat <- read_rdump('8schools.rdump')

source('8schools.rdump') 
fit <- stan(file = '8schools.stan', data = c("J", "y", "sigma_y"), 
            iter = 1000, chains = 4) 
```


```
fit1 <- stan(file = '8schools.stan', data = schools_dat, iter = 1000, chains = 4)
fit2 <- stan(fit = fit1, data = schools_dat, iter = 10000, chains = 4)
```

```
print(fit2)
plot(fit2)

la <- extract(fit2, permuted = TRUE) # return a list of arrays 
mu <- la$mu 

## return an array of three dimensions: iterations, chains, parameters 
a <- extract(fit2, permuted = FALSE) 

## use S3 functions as.array (or as.matrix) on stanfit objects
a2 <- as.array(fit2)
m <- as.matrix(fit2)
```

    
Fixed effects model
------------------
```{r}
rcb_code <- '
  data {
    int<lower=0> N;
    int<lower=0> t;
    int<lower=0> r;
    vector[N] obs;
    vector[N] trt;
    vector[N] rep;
  }
  transformed data {
    vector[N] trt2; 
    vector[N] trt3; 
    vector[N] trt4; 
    vector[N] trt5;
    vector[N] trt6;
    vector[N] rep2;
    vector[N] rep3;
    vector[N] rep4;
    for (i in 1:N) {
      trt2[i] <- trt[i] == 2;
      trt3[i] <- trt[i] == 3;
      trt4[i] <- trt[i] == 4;
      trt5[i] <- trt[i] == 5;
      trt6[i] <- trt[i] == 6;
      rep2[i] <- rep[i] == 2;
      rep3[i] <- rep[i] == 3;
      rep4[i] <- rep[i] == 4;
    }
  }
  parameters {
    vector[9] beta;
    real<lower=0> sigma;
  }
  model {
    obs ~ normal(beta[1] + beta[2] * rep2 + beta[3] * rep3 + beta[4] * rep4 +
          beta[5] * trt2 + beta[6] * trt3 + beta[7] * trt4 + beta[8] * trt5 + beta[9] * trt6
         , sigma);
  }'

rcb_dat <- list(N=length(Table5.7$obs),
                t=length(levels(Table5.7$trt)),
                r=length(levels(Table5.7$rep)),
                obs=Table5.7$obs,
                trt=as.numeric(Table5.7$trt),
                rep=as.numeric(Table5.7$rep))
fit1 <- stan(model_code = rcb_code, data = rcb_dat, 
            iter = 1000, chains = 4)
print(fit1)
```

lm1
```

vector mult 
inter <- u .* x;

Random effects model (Model 1)
--------------------

```{r}
rcb_code <- '
  data {
    int<lower=0> N;
    int<lower=0> t;
    int<lower=0> r;
    vector[N] obs;
    vector[N] trt;
    int<lower=1,upper=4> rep[N];
  }
  transformed data {
    vector[N] trt2; 
    vector[N] trt3; 
    vector[N] trt4; 
    vector[N] trt5;
    vector[N] trt6;
    for (i in 1:N) {
      trt2[i] <- trt[i] == 2;
      trt3[i] <- trt[i] == 3;
      trt4[i] <- trt[i] == 4;
      trt5[i] <- trt[i] == 5;
      trt6[i] <- trt[i] == 6;
    }
  }
  parameters {
    vector[6] beta;
    vector[4] u;
    real mu_u;
    real<lower=0> sigma_u;
    real<lower=0> sigma;
  }
  transformed parameters {
    vector[N] y_hat;

    for (i in 1:N)
      y_hat[i] <- beta[1] + u[rep[i]] + beta[2] * trt2[i] + beta[3] * trt3[i] + beta[4] * trt4[i] + beta[5] * trt5[i] + beta[6] * trt6[i];
  }
  model {
    mu_u ~ normal(0, 1);
    u ~ normal(mu_u, sigma_u);

    obs ~ normal(y_hat, sigma);
  }'
fit2 <- stan(model_code = rcb_code, data = rcb_dat, 
            iter = 1000, chains = 4)
print(fit2)
```

```{r}
rcb_code <- '
  data {
    int<lower=0> N;
    int<lower=0> t;
    int<lower=0> r;
    vector[N] obs;
    vector[N] trt;
    vector[N] rep;
  }
  transformed data {
    vector[N] trt2; 
    vector[N] trt3; 
    vector[N] trt4; 
    vector[N] trt5;
    vector[N] trt6;
    vector[N] rep1;
    vector[N] rep2;
    vector[N] rep3;
    vector[N] rep4;
    
    for (i in 1:N) {
      trt2[i] <- trt[i] == 2;
      trt3[i] <- trt[i] == 3;
      trt4[i] <- trt[i] == 4;
      trt5[i] <- trt[i] == 5;
      trt6[i] <- trt[i] == 6;
      rep1[i] <- rep[i] == 1;
      rep2[i] <- rep[i] == 2;
      rep3[i] <- rep[i] == 3;
      rep4[i] <- rep[i] == 4;
    }
  }
  parameters {
    vector[6] beta;
    vector[4] u;
    real mu_u;
    real<lower=0> sigma_u;
    real<lower=0> sigma;
  }
  model {
    mu_u ~ normal(0, 1);
    u ~ normal(mu_u, sigma_u);
    obs ~ normal(beta[1] + u[1] * rep1 + u[2] * rep2 + u[3] * rep3 + u[4] * rep4 +
          beta[2] * trt2 + beta[3] * trt3 + beta[4] * trt4 + beta[5] * trt5 + beta[6] * trt6
         , sigma);
  }'
fit3 <- stan(model_code = rcb_code, data = rcb_dat, 
            iter = 1000, chains = 4)
print(fit3)
```

Compare with MCMCglmm

```{r}
library(MCMCglmm)

rcb.MCMCglmm <- MCMCglmm(fixed=obs ~ trt, random = ~ rep,data=Table5.7, verbose=FALSE)
summary(rcb.MCMCglmm)
```

### glmmBUGS
```{r}
library(glmmBUGS)
p399.grp$Trial <- as.factor(as.integer(p399.grp$Trial))
getDesignMatrix(Yield ~ Variety, data=p399.grp, effects="Trial")
p399.arr <- winBugsRaggedArray(p399.grp)
p399.pql <- glmmPQLstrings(effects="Trial", covariates=NULL, observations="Yield", data = p399.grp, family="gaussian")

writeBugsModel("model.bug", effects="Trial",  observations="Yield",
  covariates=list(observations="Variety"),
  family="normal", priors=c(intercept="dunif(-10,10)") ) 
getStartingValues(pql=p399.pql, ragged=p399.arr)

#hom1.glmmBUGS <- glmmBUGS(Yield ~ Variety, data=p399.grp, effects="Trial", family="gaussian")

data(Muscle)
muscleRagged = glmmBUGS(length~conc , data=Muscle, effects="Strip", family="gaussian")
startingValues = muscleRagged$startingValues
```
library(nlme)
data(Muscle)

## Not run:
# run with winbugs
source("getInits.R")
require(R2WinBUGS)
muscleResult = bugs(muscleRagged$ragged, getInits, parameters.to.save = names(getInits()),
model.file="model.bug", n.chain=3, n.iter=1000, n.burnin=100, n.thin=10,
program="winbugs", working.directory=getwd())
# a jags example
require(R2jags)
muscleResultJags = jags(
muscleRagged$ragged, getInits, parameters.to.save = names(getInits()),
model.file="model.bug", n.chain=3, n.iter=1000,
n.burnin=100, n.thin=10,
working.directory=getwd())
## End(Not run)
data(muscleResult)
muscleParams = restoreParams(muscleResult, muscleRagged$ragged)
summaryChain(muscleParams)
checkChain(muscleParams)
# a spatial example
## Not run:
glmmBUGS 13
library(diseasemapping)
data(popdata)
data(casedata)
model = getRates(casedata, popdata, ~age*sex)
ontario = getSMR(popdata, model, casedata)
ontario = ontario@data[,c("CSDUID","observed","logExpected")]
library(spdep)
popDataAdjMat = poly2nb(popdata,row.names=as.character(popdata[["CSDUID"]]))
## End(Not run)
data(popDataAdjMat)
data(ontario)
forBugs = glmmBUGS(formula=observed + logExpected ~ 1,
effects="CSDUID", family="poisson", spatial=popDataAdjMat,
spatialEffect="CSDUID",
data=ontario)
startingValues = forBugs$startingValues
source("getInits.R")
## Not run:
library(R2WinBUGS)
ontarioResult = bugs(forBugs$ragged, getInits,
parameters.to.save = names(getInits()),
model.file="model.bug", n.chain=3, n.iter=50, n.burnin=10, n.thin=2,
program="winbugs", debug=T,working.directory=getwd())
## End(Not run)
data(ontarioResult)
ontarioParams = restoreParams(ontarioResult, forBugs$ragged)
ontarioSummary = summaryChain(ontarioParams)
# posterior probability of having 10x excess risk
postProb = apply(ontarioParams$FittedRCSDUID, 3, function(x) mean(x>log(10)) )
hist(postProb)
## Not run:
ontario = mergeBugsData(popdata, ontarioSummary)
spplot(ontario, "FittedRateCSDUID.mean")
ontario = mergeBugsData(ontario, postProb, newcol="postProb", by.x="CSDUID")
14 glmmBUGS
spplot(ontario, "postProb")
## End(Not run)
# geostatistical example
## Not run:
library(geoRglm)
data(rongelap)
## End(Not run)
rongelap= read.table(url("http://www.leg.ufpr.br/lib/exe/fetch.php/pessoais:paulojus:mbgbook:datasets:rongelap.library(spdep)
coordinates(rongelap) = ~cX+cY
rongelap$logOffset = log(rongelap$time)
rongelap$site = seq(1, length(rongelap$time))
forBugs = glmmBUGS(
formula=counts + logOffset ~ 1, family="poisson",
data=rongelap@data, effects="site", spatial=rongelap,
priors=list(phisite="dgamma(100,1)"))
startingValues = forBugs$startingValues
startingValues$phi$site = 100
source("getInits.R")
## Not run:
rongelapResult = bugs(forBugs$ragged, getInits,
parameters.to.save = names(getInits()),
model.file="model.bug", n.chain=2, n.iter=20, n.burnin=4, n.thin=2,
program="winbugs", debug=TRUE,
working.directory=getwd())
## End(Not run)
data(rongelapResult)
rongelapParams = restoreParams(rongelapResult, forBugs$ragged)
checkChain(rongelapParams)
rongelapParams$siteGrid = CondSimuPosterior(rongelapParams, rongelap,gridSize=100)
glmmPQLstrings 15
rongelapSummary=summaryChain(rongelapParams)
# plot posterior probabilities of being above average
image(rongelapSummary$siteGrid$pgt0)

```{r}
#glmmBUGS(data, effects=c("Variety"), covariates = list(Trial="Trial", Block="Block"))
```

### ADMB
### stan
### JAGS


Small data
----------

four.trials.hom.var1 <- lmer(GY ~ entry + (1 | env) + (1 | entry:env) + (1|env:bloc), data=four.trials)
four.trials.hom.var1

cpt.pbal.hom.var1 <- lmer(GY ~ entry + (1 | env) + (1 | entry:env) + (1|env:bloc), data=cpt.pbal)
print(cpt.pbal.hom.var1,correlation=FALSE)

#heterogeneous GEI variances
het.var1 <- lmer(GY ~ entry + (1 | env) + (entry | env) + (1|env:bloc),data=four.trials)
print(het.var1,correlation=FALSE)
het.var1.0 <- lmer(GY ~ entry + (1 | env) + (0 + entry | env) + (1|env:bloc),data=four.trials)
print(het.var1.0,correlation=FALSE)

#heterogenous error
MCMCglmm(fixed=  GY ~ entry + env + entry:env, random = ~ env:bloc,data=four.trials,rcov=~idh(env):units, verbose=FALSE)




#heterogeneous GEI variances



### MCMCglmm

four.trials.hom.var1 <- lmer(GY ~ entry + (1 | env) + (1 | entry:env) + (1|env:bloc), data=four.trials)
four.trials.hom.var1

het.var1 <- lmer(GY ~ entry + (1 | env) + (entry | env) + (1|env:bloc),data=four.trials)
print(het.var1,correlation=FALSE)
het.var1.0 <- lmer(GY ~ entry + (1 | env) + (0 + entry | env) + (1|env:bloc),data=four.trials)
print(het.var1.0,correlation=FALSE)

hom.mcmc1 <- MCMCglmm(fixed=  GY ~ entry, random = ~ env + env:entry + env:bloc, data=four.trials, verbose=FALSE)
summary(hom.mcmc1)

het.mcmc1 <- MCMCglmm(fixed=  GY ~ entry, random = ~ env + idh(entry):env + env:bloc,data=four.trials, verbose=FALSE)
summary(het.mcmc1)


Large data
----------


cpt.pbal.hom.var1 <- lmer(GY ~ entry + (1 | env) + (1 | entry:env) + (1|env:bloc), data=cpt.pbal)
print(cpt.pbal.hom.var1,correlation=FALSE)

cpt.pbal.mcmc1 <- MCMCglmm(fixed=  GY ~ entry, random = ~ env + env:entry + env:bloc, data=cpt.pbal, verbose=FALSE)
summary(cpt.pbal.mcmc1)

het.mcmc2 <- MCMCglmm(fixed=  GY ~ entry + env + entry:env, random = ~ env:bloc,data=four.trials,rcov=~idh(env):units, verbose=FALSE)
summary(het.mcmc2)
print(lm(GY ~ entry + env + entry:env,data=four.trials))