Fundamentals of Experimental Design: Guidelines for Designing Successful Experiments
========================================================
Michael D. Casler 

Appendix 1
----------
> SAS code to compute Tukey’s test for nonadditivity in a randomized complete block design. The test is computed in two parts: (1) output the predicted values from the mixed models analysis,
then (2) square the predicted values and include this term as a single-degree-of-freedom regressor variable (covariate) as a test for multiplicative block and treatment effects (Sahai and Ageel, 2000).

data a; infile ‘tukey.dat’;
input rep block trt y;
proc mixed; class trt;
model pcb = trt / outpred=x;
random block;
data x; set x;
p2=pred*pred;
proc mixed; class trt;
model pcb = trt p2;
random block;

Casler cites Sahai, which provide the following code (p 264)

data tukey;
input a b y;
datalines;
...
proc glm;
class a b;
model y = a b;
output out = t t = pred;

data t;
set t;
p2 = pred * pred;
proc glm
class a b;
model y = a b p2;
run;

In R,
```{r}
tukey.dat <- data.frame(
  y=c(12,4,2,5,4,-2,-4,-5,4,-3,-7,-2),
  squares=c(14,2,1,2,2,0,2,2,2,1,5,0),
	a=as.factor(c(1,1,1,1,2,2,2,2,3,3,3,3)),
	b=as.factor(c(1,2,3,4,1,2,3,4,1,2,3,4)))
tuk.lm <- lm(y ~ a + b,data=tukey.dat)
p2 <- predict(tuk.lm)
tukey.dat$p2 <- p2*p2
tuk2.lm <- lm(y ~ a + b + p2,data=tukey.dat)
anova(tuk2.lm)
```

```{r}
nonadditivity <- function(data=tukey.dat) {
   require(lme4)
   model1 <- lmer(y ~ trt + (1 | block),data=tukey.dat)
   p2 <- fitted(model1)
   tukey.dat$p2 <- p2*p2
   model2 <- lmer(y ~ trt + p2 + (1 | block),data=tukey.dat)
   return(model2)
}
```

```{r}
library(ARMR)

tukey.dat$trt <- tukey.dat$a
tukey.dat$block <- tukey.dat$b
tuk.lmer <- nonadditivity(tukey.dat)
anova(tuk.lmer)

tdf <- tukey.1df.ARMST(data=tukey.dat,AName="a",BName="b",response="y")
anova(tdf$lm)
```

Appendix 2
---------
> This SAS code to estimate the power of a hypothesis test has the following parameters: treatment means = 95 and 100, variance components = 5 and 10 (experimental error and sampling
error, respectively), r = 4 replicates, s = 2 observational units per experimental unit, and the assumption of normally distributed errors (adapted from Gbur et al., 2012).

options nocenter mprint;
data a; input trt y;
do rep=1 to 4 by 1;
do samples=1 to 2 by 1;
output;
end;
end;
datalines;
1 95
2 100
run;
proc glimmix; class trt rep;
model y = trt;
random rep(trt);
parms (5)(10) / hold=1,2;
ods output tests3=power_terms;
data power;
set power_terms;
alpha=0.05;
ncparm=numdf*Fvalue;
F_critical=finv(1-alpha, numdf, dendf, 0);
power=1–probf(F_critical, numdf, dendf, ncparm);
proc print;
run;

```{r}
reps <- 1:4
samples <- 1:2
means <- c(95,100)
alpha = 0.05
numdf <- 2
dendf <- 5
ncparm <- numdf * Fvalue
F_critical=finv(1-alpha, numdf, dendf, 0);
power <- 1 - pf(F_critical, numdf, dendf, ncparm)
```

Appendix 3
----------
> The SAS code from Appendix 1 is embedded in a macro that allows power to be estimated for a range of experimental designs with four to eight experimental units per treatment (rep, repl, repmax) and two to four observational units per experimental unit (obs, obsv, obsmax).

options nocenter mprint;
%macro one(obsmax,repmax);
data a;
%do obsv=2 %to &obsmax;
group1=&obsv;
%do repl=2 %to &repmax;
group2=&repl;
do obs=2 to &obsv by 1;
do rep=4 to &repl by 1;
do trt=0 to 1 by 1;
output;
end;
end;
end;
%end;
%end;
%mend one;

%one(4,8); /* change values here */
run;
proc sort; by group1 group2;
data b; set a; by group1 group2;
if trt=0 then y=95;
if trt=1 then y=100;
run;
proc glimmix; class trt rep; by group1 group2;
model y = trt;
random rep(trt);
parms (5)(10) / hold=1,2;
ods output tests3=power_terms;
data power;
set power_terms;
alpha=0.05;
ncparm=numdf*Fvalue;
F_critical=finv(1–alpha, numdf, dendf, 0);
power=1–probf(F_critical, numdf, dendf, ncparm);
proc print;
run;

Appendix 4
----------
> This SAS code to estimate the power of a hypothesis test has the following parameters: treatment means = 9 and 10, variance components = 0.02 and 0.2 (treatment ´ location interaction and experimental error, respectively), r = 4 to 20 replicates, l = 2 to 6 locations, and the assumption of normally distributed errors (adapted from Gbur et al., 2012).

options nocenter mprint;
%macro two(locmax,repmax);
data a;
%do locn=2 %to &locmax;
group1=&locn;
%do repl=4 %to &repmax;
group2=&repl;
do loc=2 to &locn by 1;
do rep=4 to &repl by 1;
do trt=0 to 1 by 1;
output;
end;
end;
end;
%end;
%end;
%mend two;
%two(6,20); /* change here */
run;
proc sort; by group1 group2;
data b; set a; by group1 group2;
if trt=0 then y=9;
if trt=1 then y=10;
run;
proc glimmix; class location trt rep; by group1 group2;
model y = trt;
random trt*location;
parms (0.02)(0.2) / hold=1,2;
ods output tests3=power_terms;
data power;
set power_terms;
alpha=0.05;
ncparm=numdf*Fvalue;
F_critical=finv(1–alpha, numdf, dendf, 0);
power=1–probf(F_critical, numdf, dendf, ncparm);
proc print;
run;

