Comparing LMM packages
========================================================

```{r}
library(ggplot2)
library(ASA.CSSA.SSSA)
#data(cpt)

#remove fill
#cpt.dat <- subset(cpt.dat,!(cpt.dat$entry=="fill"))
#cpt.dat$entry <- as.factor(as.character(cpt.dat$entry))

#convert to Mg ha-1
#cpt.pbal$GY <- (cpt.pbal$TW * cpt.pbal$GY)*0.00112
#cpt.bal$GY <- (cpt.bal$TW * cpt.bal$GY)*0.00112

#remove missing yield
#cpt.dat <- subset(cpt.dat,!is.na(cpt.dat$GY))

#processed data
data(cpt_data)
cpt.pbal <- subset(cpt.pbal,!is.na(cpt.pbal$GY))

#sum(is.na(cpt.pbal$GY))
#cpt.pbal <- cpt.pbal[!is.na(cpt.pbal$GY),]
cpt.pbal$year <- as.factor(cpt.pbal$year)
#cpt.bal <- subset(cpt.bal,!is.na(cpt.bal$GY))
#cpt.bal$year <- as.factor(cpt.bal$year)

```

some are better encoded this way
from http://glmm.wikidot.com/faq

Whether you explicitly specify a random effect as nested or not depends (in part) on the way the levels of the random effects are coded. If the 'lower-level' random effect is coded with unique levels, then the two syntaxes (1|a/b) (or (1|a+a:b)) and (1|a)+(1|b) are equivalent. If the lower-level random effect has the same labels within each larger group (e.g. blocks 1, 2, 3, 4 within sites A, B, and C) then the explicit nesting (1|a/b) is required. It seems to be considered best practice to code the nested level uniquely (e.g. A1, A2, …, B1, B2, …) so that confusion between nested and crossed effects is less likely.

```{r}
cpt.pbal$blocInEnv <- cpt.pbal$env:cpt.pbal$bloc

#create small data set
three.entries <- subset(cpt.pbal, cpt.pbal$entry %in% c("sd97059-2","wesley","sd98102"))
four.trials <- subset(three.entries, three.entries$location == "Brookings")
four.trials$entry <- as.factor(as.character(four.trials$entry))
four.trials$env <- as.factor(as.character(four.trials$env))
four.trials$bloc <- as.factor(as.character(four.trials$bloc))
four.trials<-four.trials[order(four.trials$year),]
```

Range of estimates for RCB

```{r}
library(nlme)
library(MCMCglmm)
library(glmmADMB)
library(glmmLasso)
library(MASS)

envs <- levels(cpt.pbal$env)

if(!file.exists("table1.Rda")) {
table1.lm <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table1.lme <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table1.MCMCglmm <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table1.glmmadmb <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table1.glmmLasso <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table1.glmmPQL <- data.frame(trial=envs,rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
for(idx in 1:length(table1.lm$trial)) {
  env <- table1.lm$trial[idx]
  current.trial <- cpt.pbal[(cpt.pbal$env == env),]
  current.trial <- current.trial[!is.na(current.trial$GY),]
  if(length(current.trial$GY>2)) {
    current.lm <- lm(GY ~ entry + bloc,data=current.trial)
    #manually compute variance
    current.aov.tbl <- anova(current.lm)
    
    trts <- current.aov.tbl[1,1]+1
    errordf <- current.aov.tbl[3,1]
    #residual
    rms <- current.aov.tbl[3,3]
    table1.lm$err.var[idx] <- rms
    
    
    #res.lm <- current.lm$fitted - current.trial$GY
    #rms <- sum(res.lm^2)/errordf
    
    #rep in trial
    rep.var <- (current.aov.tbl[2,3]-current.aov.tbl[3,3])/trts
    table1.lm$rep.var[idx] <- rep.var
    
    #table1.lm <- rbind(table1.lm,res)
    #extract rcb
    current.lme <- lme(GY ~ entry,random = ~ 1 | bloc,data=current.trial)
    rep.var <- as.numeric(VarCorr(current.lme)[1,1])
    rms <- as.numeric(VarCorr(current.lme)[2,1])
    table1.lme$err.var[idx] <- rms
    table1.lme$rep.var[idx] <- rep.var
    
    #MCMC
    current.MCMCglmm <- MCMCglmm(fixed=GY ~ entry, random = ~ bloc,data=current.trial, verbose=FALSE)
    rms <- summary(current.MCMCglmm)$Rcovariances[1]
    
    rep.var <- summary(current.MCMCglmm)$Gcovariances[1,1]
    table1.MCMCglmm$err.var[idx] <- rms
    table1.MCMCglmm$rep.var[idx] <- rep.var
    
    current.glmmadmb <- glmmadmb(GY ~ entry, random = ~ 1 | bloc, family = "gaussian", data = current.trial)
    rep.var <- VarCorr(current.glmmadmb)[[1]]
    rms <- sum(current.glmmadmb$residuals^2)/errordf #var(current.glmmadmb$residuals)
    table1.glmmadmb$err.var[idx] <- rms
    table1.glmmadmb$rep.var[idx] <- rep.var
    
    current.glmmLasso <- glmmLasso(GY ~ entry, rnd = list(bloc=~1), lambda=1, data = current.trial)
    rep.var <- current.glmmLasso$StdDev*current.glmmLasso$StdDev
    res <- current.glmmLasso$fitted.values - current.trial$GY
    rms <- sum(res^2)/errordf
    rms <- var(res)
    table1.glmmLasso$err.var[idx] <- rms
    table1.glmmLasso$rep.var[idx] <- rep.var
    
    current.glmmPQL <- glmmPQL(GY ~ entry, random = ~ 1 | bloc,family=gaussian, data = current.trial)
    rep.var <- as.numeric(VarCorr(current.glmmPQL)[1,1])
    rms <- as.numeric(VarCorr(current.glmmPQL)[2,1])

    table1.glmmPQL$err.var[idx] <- rms
    table1.glmmPQL$rep.var[idx] <- rep.var
  }
}

table1.lme$method <- "lme"
table1.lm$method <- "lm"
table1.MCMCglmm$method <- "MCMCglmm"
table1.glmmadmb$method <- "glmmadmb"
table1.glmmLasso$method <- "glmmLasso"
table1.glmmPQL$method <- "glmmPQL"

table1 <- rbind(table1.lm,table1.lme,table1.MCMCglmm,table1.glmmadmb,table1.glmmLasso,table1.glmmPQL)
save(table1,file="table1.Rda")
} else {
  load(file="table1.Rda")
  table1.lm = subset(table1,table1$method=="lm")  
  table1.lme = subset(table1,table1$method=="lme")

  table1.MCMCglmm = subset(table1,table1$method=="MCMCglmm")
  table1.glmmadmb = subset(table1,table1$method=="glmmadmb")
  table1.glmmLasso = subset(table1,table1$method=="glmmLasso")
  table1.glmmPQL = subset(table1,table1$method=="glmmPQL")
  
}

table1 <- subset(table1,table1$rep.var < 2*max(table1.lm$rep.var))

```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
#ggplot(table1, aes(x=rep.var, fill = method)) + geom_bar(position="dodge",binwidth = .1)
ggplot(table1, aes(x=rep.var, fill = method)) + geom_bar(position="dodge",binwidth = 10)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
#ggplot(table1, aes(x=err.var, fill = method)) + geom_bar(position="dodge",binwidth = .05)
ggplot(table1, aes(x=err.var, fill = method)) + geom_bar(position="dodge",binwidth = 20)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
corr.tbl <- data.frame(Expected=rep(table1.lm$rep.var,6),
                       Predicted = c(table1.lm$rep.var,
                                     table1.lme$rep.var,
                                     table1.MCMCglmm$rep.var,
                                     table1.glmmadmb$rep.var,
                                     table1.glmmLasso$rep.var,
                                     table1.glmmPQL$rep.var),
                       Method =c(table1.lm$method,
                                 table1.lme$method,
                                     table1.MCMCglmm$method,
                                     table1.glmmadmb$method,
                                     table1.glmmLasso$method,
                                     table1.glmmPQL$method) )
corr.tbl <- subset(corr.tbl,corr.tbl$Predicted < 2*max(table1.lm$rep.var))
ggplot(corr.tbl, aes(x=Expected, y=Predicted,color = Method)) + geom_point(size=3,aes(color=Method)) + geom_smooth(aes(group=Method,linetype=Method,color=Method),size=1,method="lm",se = FALSE) +
  ggtitle("Replicate Variances")
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
err.tbl <- data.frame(Expected=rep(table1.lm$err.var,6),
                       Predicted = c(table1.lm$err.var,
                                     table1.lme$err.var,
                                     table1.MCMCglmm$err.var,
                                     table1.glmmadmb$err.var,
                                     table1.glmmLasso$err.var,
                                     table1.glmmPQL$err.var),
                       Method =c(table1.lm$method,
                                 table1.lme$method,
                                     table1.MCMCglmm$method,
                                     table1.glmmadmb$method,
                                     table1.glmmLasso$method,
                                     table1.glmmPQL$method) )
err.tbl <- subset(err.tbl,err.tbl$Predicted < 2*max(table1.lm$rep.var))
ggplot(err.tbl, aes(x=Expected, y=Predicted,color = Method)) + geom_point(size=3,aes(color=Method)) + geom_smooth(aes(group=Method,linetype=Method,color=Method),size=1,method="lm",se = FALSE) +
  ggtitle("Residual Variances")
```

Combined Trials
---------------
```{r}

### lm
combined.lm <- lm(GY ~ entry + env + env:bloc,data=cpt.pbal)
combined.aov.tbl <- anova(combined.lm)
trts <- combined.aov.tbl[1,1]+1
reps <- combined.aov.tbl[3,1]+1
errordf <- combined.aov.tbl[4,1]
#residual
lm.rms <- combined.aov.tbl[4,3]
lm.rep.var <- (combined.aov.tbl[3,3]-combined.aov.tbl[4,3])/trts
lm.env.var <- (combined.aov.tbl[2,3]-combined.aov.tbl[3,3])/(trts*reps)

### lme
combined.lme <- lme(GY ~ entry,random = ~ 1 | env/bloc,data=cpt.pbal)
lme.env.var <- as.numeric(VarCorr(combined.lme)[[2]])
lme.rep.var <- as.numeric(VarCorr(combined.lme)[[4]])
lme.rms <- as.numeric(VarCorr(combined.lme)[[5]])

#MCMC
combined.MCMCglmm <- MCMCglmm(fixed=GY ~ entry, random = ~ env + env:bloc ,data=cpt.pbal, verbose=FALSE)
mcmc.rms <- summary(combined.MCMCglmm)$Rcovariances[1]
mcmc.rep.var <- summary(combined.MCMCglmm)$Gcovariances[2,1]
mcmc.env.var <- summary(combined.MCMCglmm)$Gcovariances[1,1]

combined.glmmadmb <- glmmadmb(GY ~ entry, random = ~ 1 | env/bloc, family = "gaussian", data = cpt.pbal)
glmmadmb.env.var <- VarCorr(combined.glmmadmb)[[1]]
glmmadmb.rep.var <- VarCorr(combined.glmmadmb)[[2]]
glmmadmb.rms <- var(combined.glmmadmb$residuals)

 #combined.glmmLasso <- glmmLasso(GY ~ entry, rnd = list(blocInEnv=~1 + env), lambda=20, data = cpt.pbal)   
#combined.glmmLasso <- glmmLasso(GY ~ entry, rnd = list(bloc=~1 + env), lambda=1, data = cpt.pbal)
#glmmadmb.rep.var <- combined.glmmLasso$StdDev*combined.glmmLasso$StdDev
#glmmadmb.res <- combined.glmmLasso$fitted.values - cpt.pbal$GY
#glmmadmb.rms <- sum(res^2)/errordf
        
combined.glmmPQL <- glmmPQL(GY ~ entry, random = ~ 1 | env/bloc,family=gaussian, data = cpt.pbal)
glmmPQL.env.var <- as.numeric(VarCorr(combined.glmmPQL)[[2]])
glmmPQL.rep.var <- as.numeric(VarCorr(combined.glmmPQL)[[4]])
glmmPQL.rms <- as.numeric(VarCorr(combined.glmmPQL)[[5]])

```

```{r}
if(!file.exists("table2.Rda")) {
table2.lm <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table2.lme <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table2.MCMCglmm <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table2.glmmadmb <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table2.glmmLasso <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
table2.glmmPQL <- data.frame(trial=envs,env.var=rep(0,length(envs)),rep.var=rep(0,length(envs)),err.var=rep(0,length(envs)))
for(idx in 1:length(envs)) {
#for(idx in 1:2) {
  env <- table2.lm$trial[idx]
  current.trial <- cpt.pbal[(cpt.pbal$env != env),]
  current.trial <- current.trial[!is.na(current.trial$GY),]
  if(length(current.trial$GY>2)) {
    #lm
    current.lm <- lm(GY ~ entry + env + env:bloc,data=current.trial)
    current.aov.tbl <- anova(current.lm)
    trts <- current.aov.tbl[1,1]+1
    reps <- current.aov.tbl[3,1]+1
    errordf <- current.aov.tbl[4,1]
  
    lm.rms <- current.aov.tbl[4,3]
    lm.rep.var <- (current.aov.tbl[3,3]-current.aov.tbl[4,3])/trts
    lm.env.var <- (current.aov.tbl[2,3]-current.aov.tbl[3,3])/(trts*4)
    table2.lm$env.var[idx] <- lm.env.var
    table2.lm$err.var[idx] <- lm.rms
    table2.lm$rep.var[idx] <- lm.rep.var 

    #lme
    current.lme <- lme(GY ~ entry,random = ~ 1 | env/bloc,data=current.trial)
    lme.env.var <- as.numeric(VarCorr(current.lme)[[2]])
    lme.rep.var <- as.numeric(VarCorr(current.lme)[[4]])
    lme.rms <- as.numeric(VarCorr(current.lme)[[5]])
    table2.lme$env.var[idx] <- lme.env.var 
    table2.lme$rep.var[idx] <- lme.rep.var
    table2.lme$err.var[idx] <- lme.rms
    
    
    #MCMC
    current.MCMCglmm <- MCMCglmm(fixed=GY ~ entry, random = ~ env + env:bloc ,data=current.trial, verbose=FALSE)
    mcmc.rms <- summary(current.MCMCglmm)$Rcovariances[1]
    mcmc.rep.var <- summary(current.MCMCglmm)$Gcovariances[2,1]
    mcmc.env.var <- summary(current.MCMCglmm)$Gcovariances[1,1]
    
    table2.MCMCglmm$env.var[idx] <- mcmc.env.var
    table2.MCMCglmm$rep.var[idx] <- mcmc.rep.var
    table2.MCMCglmm$err.var[idx] <- mcmc.rms
    
    
    #glmmadmb
    current.glmmadmb <- glmmadmb(GY ~ entry, random = ~ 1 | env/bloc, family = "gaussian", data = current.trial)
    glmmadmb.env.var <- VarCorr(current.glmmadmb)[[1]]
    glmmadmb.rep.var <- VarCorr(current.glmmadmb)[[2]]
    glmmadmb.rms <- var(current.glmmadmb$residuals)
    table2.glmmadmb$env.var[idx] <- glmmadmb.env.var
    table2.glmmadmb$rep.var[idx] <- glmmadmb.rep.var
    table2.glmmadmb$err.var[idx] <- glmmadmb.rms
    
    
    #glmmLasso
    #this is what the help looks like, but does not work
    #current.glmmLasso <- glmmLasso(GY ~ entry, rnd = list(bloc=~1 + env), lambda=1, data = current.trial)
    #current.glmmLasso <- glmmLasso(GY ~ entry, rnd = list(blocInEnv=~1 + env), lambda=1, data = cpt.pbal)
    #rep.var <- current.glmmLasso$StdDev*current.glmmLasso$StdDev
    #res <- current.glmmLasso$fitted.values - current.trial$GY
    #rms <- sum(res^2)/errord 
    #table2.glmmLasso$err.var[idx] <- rms
    #table2.glmmLasso$rep.var[idx] <- rep.var
    
    #glmmPQL
    current.glmmPQL <- glmmPQL(GY ~ entry, random = ~ 1 | env/bloc,family=gaussian, data = current.trial)
    glmmPQL.env.var <- as.numeric(VarCorr(current.glmmPQL)[[2]])
    glmmPQL.rep.var <- as.numeric(VarCorr(current.glmmPQL)[[4]])
    glmmPQL.rms <- as.numeric(VarCorr(current.glmmPQL)[[5]])

    table2.glmmPQL$env.var[idx] <- glmmPQL.env.var
    table2.glmmPQL$rep.var[idx] <- glmmPQL.rep.var
    table2.glmmPQL$err.var[idx] <- glmmPQL.rms
    
  }
}

table2.lme$method <- "lme"
table2.lm$method <- "lm"
table2.MCMCglmm$method <- "MCMCglmm"
table2.glmmadmb$method <- "ADMB"
table2.glmmLasso$method <- "glmmLasso"
table2.glmmPQL$method <- "glmmPQL"

table2 <- rbind(table2.lm,
                table2.lme,
                table2.MCMCglmm,
                table2.glmmadmb,
                table2.glmmPQL)
                #table2.glmmLasso,
save(table2,file="table2.Rda")
} else {
   load(file="table2.Rda")
   table2.lme = subset(table2,table2$method=="lme")
  table2.lm = subset(table2,table2$method=="lm")
  table2.MCMCglmm = subset(table2,table2$method=="MCMCglmm")
  table2.glmmadmb = subset(table2,table2$method=="ADMB")
  #table2.glmmLasso = subset(table2,table2$method=="glmmLasso")
  table2.glmmPQL = subset(table2,table2$method=="glmmPQL")
}
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
ggplot(table2, aes(x=env.var, fill = method)) + geom_bar(position="dodge",binwidth = 10)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
ggplot(table2, aes(x=rep.var, fill = method)) + geom_bar(position="dodge",binwidth = 1)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
ggplot(table2, aes(x=err.var, fill = method)) + geom_bar(position="dodge",binwidth = 1)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
env.tbl.2 <- data.frame(Expected=rep(table2.lm$env.var,5),
                       Predicted = c(table2.lm$env.var,
                                     table2.lme$env.var,
                                     table2.MCMCglmm$env.var,
                                     table2.glmmadmb$env.var,
                                     #table2.glmmLasso$env.var,
                                     table2.glmmPQL$env.var),
                       Method =c(table2.lm$method,
                                 table2.lme$method,
                                     table2.MCMCglmm$method,
                                     table2.glmmadmb$method,
                                     #table2.glmmLasso$method,
                                     table2.glmmPQL$method) )
ggplot(env.tbl.2, aes(x=Expected, y=Predicted,color = Method)) + geom_point(size=3,aes(color=Method)) + geom_smooth(aes(group=Method,linetype=Method,color=Method),size=1,method="lm",se = FALSE)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
rep.tbl.2 <- data.frame(Expected=rep(table2.lm$rep.var,5),
                       Predicted = c(table2.lm$rep.var,
                                     table2.lme$rep.var,
                                     table2.MCMCglmm$rep.var,
                                     table2.glmmadmb$rep.var,
                                     #table2.glmmLasso$rep.var,
                                     table2.glmmPQL$rep.var),
                       Method =c(table2.lm$method,
                                 table2.lme$method,
                                     table2.MCMCglmm$method,
                                     table2.glmmadmb$method,
                                     #table2.glmmLasso$method,
                                     table2.glmmPQL$method) )
ggplot(rep.tbl.2, aes(x=Expected, y=Predicted,color = Method)) + geom_point(size=3,aes(color=Method)) + geom_smooth(aes(group=Method,linetype=Method,color=Method),size=1,method="lm",se = FALSE)
```

```{r fig=TRUE,echo=FALSE,width=9,height=5}
err.tbl.2 <- data.frame(Expected=rep(table2.lm$err.var,5),
                       Predicted = c(table2.lm$err.var,
                                     table2.lme$err.var,
                                     table2.MCMCglmm$err.var,
                                     table2.glmmadmb$err.var,
                                     #table2.glmmLasso$err.var,
                                     table2.glmmPQL$err.var),
                       Method =c(table2.lm$method,
                                 table2.lme$method,
                                     table2.MCMCglmm$method,
                                     table2.glmmadmb$method,
                                     #table2.glmmLasso$method,
                                     table2.glmmPQL$method) )
ggplot(err.tbl.2, aes(x=Expected, y=Predicted,color = Method)) + geom_point(size=3,aes(color=Method)) + geom_smooth(aes(group=Method,linetype=Method,color=Method),size=1,method="lm",se = FALSE)
```





(1|group)  random group intercept
(x|group) = (1+x|group)	random slope of x within group with correlated intercept
(0+x|group) = (-1+x|group)	random slope of x within group: no variation in intercept
(1|group) + (0+x|group)	uncorrelated random intercept and random slope within group
(1|site/block) = (1|site)+(1|site:block)	intercept varying among sites and among blocks within sites (nested random effects)
site+(1|site:block)	fixed effect of sites plus random variation in intercept among blocks within sites
(x|site/block) = (x|site)+(x|site:block) = (1 + x|site)+(1+x|site:block)	slope and intercept varying among sites and among blocks within sites
(x1|site)+(x2|block)	two different effects, varying at different levels
x*site+(x|site:block)	fixed effect variation of slope and intercept varying among sites and random variation of slope and intercept among blocks within sites
(1|group1)+(1|group2)	intercept varying among crossed random effects (e.g. site, year)


