GEI models using lme
========================================================

```{r}
library(ASA.CSSA.SSSA)
data(SteelTorrie)
```


```{r}
library(nlme)
p399$GEI <- p399$Variety:p399$Trial
p399$Block <- p399$Trial:p399$Rep

#group by trails and replicates
p399.grp <- groupedData(Yield ~ 1 |Trial/Rep, data=p399)

#p399.grp <- groupedData(Yield ~ 0 + 1 | GEI, data=p399)
plot(p399.grp)
#This produces an estimate for Trial variance.
#lme(Yield ~ Variety*Trial, random = ~ 1 | Trial/Rep, data = p399.grp)
lme(Yield ~ Variety*Trial, random = ~ 1 | Block, data = p399.grp)

hom.lme <- lme(Yield ~ Variety*Trial, random = ~ 1 | Block, data = p399)
hom.lme
```

Grouping data
```{r}
#p399.grp <- groupedData(Yield ~ Variety | Trial, data=p399)
#p399.grp2 <- groupedData(Yield ~ Variety | Trial/Rep, data=p399)
```

Based on Pinheiro and Bates
```{r}
lme(Yield ~ Variety*Trial, p399.grp, random=pdBlocked(list(pdIdent(~ 1),pdIdent(~ Trial - 1),pdIdent(~ Variety - 1))))
```

This requires grouped data, otherwise, 
```
Error in getGroups.data.frame(dataMix, groups) : 
  invalid formula for groups
```

```{r}
lme(Yield ~ Variety, random = ~ 1 | Trial/Rep, data = p399.grp)
lme(Yield ~ Variety, random = ~ 1 | GEI, data = p399.grp2)
#crashes
#lme(Yield ~ Variety, random = ~ GEI | Trial/Rep, data = p399.grp2)

hom.lme <- lme(Yield ~ Variety, random = ~ 1 | Trial/Rep, data = p399.grp)

lme(Yield ~ Variety, random=list(Trial=~1,Variety=~Trial), data = p399.grp)

#error
#lme(Yield ~ Variety, random=list(Block=~1,Variety=~Trial), data = p399.grp)
#hangs
#lme(Yield ~ Variety, random=list(Trial=~1,Rep=~Variety), data = p399.grp)

lme(Yield ~ Variety, random=list(~1|Trial,~1|Rep), data = p399.grp)


#not quite
#lme(Yield ~ Variety, random=list(~1|Trial,~1|Rep,~Trial|Variety), data = p399.grp)

#hangs
#lme(Yield ~ Variety, random=list(~Variety|Trial,~1|Rep), data = p399.grp)
#lme(Yield ~ Variety, random=list(~1|Trial,~Variety|Rep), data = p399.grp)

#Error in MEEM(object, conLin, control$niterEM) : 
#  NAs in foreign function call (arg 2)
#lme(Yield ~ Variety, random=list(~1|Trial/Rep,~1|GEI), data = p399.grp)

#close
lme(Yield ~ Variety, random=list(~1|GEI,~1|Block), data = p399.grp)
lme(Yield ~ Variety, random=list(~1|Block,~1|GEI), data = p399.grp)

# a trick from the web
one <- rep(1,length(p399.grp$Yield))
#a=~1,one=~b
lme(Yield ~ Variety, random=list(Block=~1,one=~GEI), data = p399.grp)
lme(Yield ~ Variety, random=list(one=pdSymm(~1|Block)), data = p399.grp)
```

Random block structure
Note we need to remove intercept from the names
```{r}
blocks <- pdSymm(~ 0 + Block,data=p399.grp)
gei <- pdSymm(~ 0 + GEI,data=p399.grp)

blocks <- pdSymm(~ 0 + Block,data=p399)
gei <- pdSymm(~ 0 + GEI,data=p399)
blocks <- pdSymm(value=~ 0 + Block,data=p399)
gei <- pdSymm(value=~ 0 + GEI,data=p399)

blocks <- pdSymm(value=~ 0 + Block,data=p399.grp)
gei <- pdSymm(value=~ 0 + GEI,data=p399.grp)

pdConstruct(gei,data=p399)

blocks <- pdSymm(~ 0 + 1 | Trial/Rep,data=p399)
gei <- pdSymm(value=~0 + GEI,form=~ 0 + GEI,data=p399)

gbnames <- c(attr(blocks, "Dimnames"),attr(gei, "Dimnames"))

geiblocks <- pdBlocked(list(blocks,gei),data=p399.grp)
geiblocks <- pdBlocked(list(blocks,gei))

pdConstruct(geiblocks,data=p399)
lme(Yield ~ Variety, random=geiblocks, data = p399.grp)



pd1 <- pdBlocked(list(blocks,gei),nam=list(attr(blocks, "Dimnames")[[1]],attr(gei, "Dimnames")[[1]]),data=p399.grp)

pd1 <- pdBlocked(list(blocks,gei),data=p399.grp)

lme(Yield ~ Variety, random=pd1, data = p399.grp)

#this fails to converge
#lme.2 <- lme(Yield ~ Variety, random=pdBlocked(list(pdSymm(~ 0 + Block),pdSymm(~ 0 + GEI))), data = p399.grp)

lme.2 <- lme(Yield ~ Variety, random=pdBlocked(list(pdSymm(~ 0 + Block),pdSymm(~ 0 + GEI))), data = p399)

lme(Yield ~ Variety, random=list(one=pdBlocked(list(Blocks=pdSymm(~ 0 + 1|Trial/Rep), 
            GEI=pdSymm(~0 + 1|GEI)))), data = p399.grp)
            
hom.lme

het1.lme <- lme(Yield ~ Variety, random = ~ 1 | Trial/Rep, data = p399)
#heterogenous variances does not converge for this data.
#het2.lme <- lme(Yield ~ Variety, random = ~ Variety | Trial/Rep, data = p399)
het3.lme <- lme(Yield ~ Variety, random = ~ 1 | Trial/Rep, weights=varIdent(form=~1|Trial), data = p399)
het3.lme
```

```{r}


#pdSymm(~Variety,data=p399.grp)

#hom2.lme <- lme(Yield ~ Variety, random = pdBlocked(list(pdSymm(~Variety), pdSymm(~Trial))), data = p399)
#hom2.lme

#het1.lme <- lme(Yield ~ Variety, random = ~ Variety | Trial/Rep, weights=varIdent(form=~1|Trial), data = p399)
#het1.lme 

#het1.lme <- lme(Yield ~ Variety, random = ~ Variety | Trial/Rep, data = p399)
#het1.lme 

#list(~ Variety | Trial, ~ 1 | Trial/Rep)
hom.lme <- lme(Yield ~ Variety, random = list(~ 1 | GEI,~ 1 | Trial,~ 1 | Block), data = p399)
hom.lme

#het2.lme <- lme(Yield ~ Variety, random = ~ 1 | Trial/Rep, weights=varIdent(form=~1|Trial), data = p399)
#het2.lme

```

```{r fig.width=7, fig.height=6}
plot(cars)
```


Multilocation example
```{r}
library(SASmixed)
data(Multilocation)

options( contrasts = c(factor = "contr.SAS", ordered = "contr.poly") )
formula( Multilocation )
names( Multilocation )
### Create a Block %in% Location factor
Multilocation$Grp <-
  getGroups( Multilocation, form = ~ Location/Block, level = 2 )
fm1Mult <- lme( Adj ~ Location * Trt, data = Multilocation, ~ 1 | Grp,
               method = "ML")
summary( fm1Mult )
fm2Mult <- update( fm1Mult, Adj ~ Location + Trt )
fm3Mult <- update( fm1Mult, Adj ~ Location )
fm4Mult <- update( fm1Mult, Adj ~ Trt )
fm5Mult <- update( fm1Mult, Adj ~ 1 )
anova( fm1Mult, fm2Mult, fm3Mult, fm5Mult )
anova( fm1Mult, fm2Mult, fm4Mult, fm5Mult )
### AIC, BIC, and likelihood ratio tests all prefer model fm2Mult
summary( fm2Mult )
fm2RMult <- update( fm2Mult, method = "REML" ) # get REML estimates
summary( fm2RMult )
### Treating the location as a random effect
fm1MultR <- lme( Adj ~ Trt, data = Multilocation, method = "ML",
  random = list( Location = pdCompSymm( ~ Trt - 1 ), Block = ~ 1 ) )
summary( fm1MultR )
fm2MultR <- update( fm1MultR, random = list( Location = ~ Trt-1, Block = ~ 1 ))
anova( fm1MultR, fm2MultR )
## No indication that a general variance-covariance is preferred to
## a compound symmetry structure.
fm1RMultR <- update( fm1MultR, method = "REML" )
summary( fm1RMultR )
c( 0.34116, 0.07497, 0.18596)^2  # compare with estimates, p. 84
```


update( fm1MultR, random = list( Trt = ~ Location-1, Block = ~ 1 ))

 getGroups( Multilocation, form = ~ Location:Trt)
Multilocation$GEI <-Multilocation$Location:Multilocation$Trt
Multilocation$Grp <-Multilocation$Location:Multilocation$Block
  getGroups( Multilocation, form = ~ Location:Trt)

lme(Adj ~ Trt, random=pdBlocked(list(pdSymm(~ 0 + Grp),pdSymm(~ 0 + GEI))), data = Multilocation)

