Comparison of open source mixed model packages for GEI
======================================================

http://glmm.wikidot.com/pkg-comparison

Single RCB
```{r}

# example gls(..., corSpher ...)
# Pinheiro and Bates, pp. 261, 263
fm1Wheat2 <- gls(yield ~ variety - 1, Wheat2)
# p. 262 
fm2Wheat2 <- update(fm1Wheat2, corr =
   corSpher(c(28, 0.2),
     form = ~ latitude + longitude, nugget = TRUE))


library(nlme)
data(Wheat2)
nin.aov <- aov(yield ~ variety + Block,data=Wheat2)
nin.aov.tbl <- anova(nin.aov)
nin.aov.tbl

trts <- length(levels(Wheat2$variety))

#residual
sqrt(nin.aov.tbl[3,3])

#rep in trial
sqrt((nin.aov.tbl[2,3]-nin.aov.tbl[3,3])/trts)
```

### lme
```{r}
nin.1.lme <- lme(yield ~ variety,random = ~ 1 | Block,data=Wheat2)
print(nin.1.lme,correlation=FALSE,digits=10)
```

```{r}
library(ASA.CSSA.SSSA)
data(cpt)
library(SASmixed)
data(Multilocation)

#remove fill
cpt.dat <- subset(cpt.dat,!(cpt.dat$entry=="fill"))
cpt.dat$entry <- as.factor(as.character(cpt.dat$entry))
#remove missing yield
cpt.dat <- subset(cpt.dat,!is.na(cpt.dat$GY))

#processed data
data(cpt_data)
cpt.pbal <- subset(cpt.pbal,!is.na(cpt.pbal$GY))
cpt.pbal$year <- as.factor(cpt.pbal$year)
cpt.bal <- subset(cpt.bal,!is.na(cpt.bal$GY))
cpt.bal$year <- as.factor(cpt.bal$year)
#convert to Mg ha-1
cpt.pbal$GY <- (cpt.pbal$TW * cpt.pbal$GY)*0.00112
cpt.bal$GY <- (cpt.bal$TW * cpt.bal$GY)*0.00112

#create small data set
three.entries <- subset(cpt.pbal, cpt.pbal$entry %in% c("sd97059-2","wesley","sd98102"))
four.trials <- subset(three.entries, three.entries$location == "Brookings")
four.trials$entry <- as.factor(as.character(four.trials$entry))
four.trials$env <- as.factor(as.character(four.trials$env))
four.trials$bloc <- as.factor(as.character(four.trials$bloc))
four.trials<-four.trials[order(four.trials$year),]
```


Motivation
----------
R is most commonly used open source statistical package. Two mixed model packages commonly used. These packages do not allow for certain types of variance/covariance specifications.


Models
Standard
Heterogeneous Interaction
Heterogeneous Error

### Cotes model


Advantages over LM/AOV
----------------------

Parameters to estimate
----------------------
$$
\mathbf{\theta}= \left(\begin{array}{c}
        \mathbf{\beta}\\
        \mathbf{u}_1\\
        .\\
        .\\
        .\\
        \mathbf{u}_{3 ( g)}
      \end{array}\right), \mathbf{\theta}_0 \left(\begin{array}{c}
        \mathbf{\beta}_0\\
        \mathbf{0}\\
        .\\
        .\\
        .\\
        \mathbf{0}
      \end{array}\right), \mathbf{D}= \left(\begin{array}{cccccc}
        \mathbf{I}\mathbf{\sigma}_0^2 &  &  &  &  & \\
        & \mathbf{I}\mathbf{\sigma}_{u_1}^2 &  &  &  & \\
        &  & . &  &  & \\
        &  &  & . &  & \\
        &  &  &  & . & \\
        &  &  &  &  & \mathbf{I}\mathbf{\sigma}_{u_{3 ( g)}}^2
      \end{array}\right)
$$


Packages considered, illustrated with Steel Torrie and SAS multilocation
-------------------
```{r}
data(SteelTorrie)
data(Multilocation)
```

Expected MS for GEI data, assuming all effects random
Source                   |     Mean square    |   EMS
-------------------------|--------------------|-------------------
Environment (E)          |           $MS_{E}$ | $\sigma ^2 _e + r \sigma ^2 _{GE} + g \sigma^2 _{R} + rg \sigma ^2 _{E}$
Replicate in Environment |           $MS_{R}$ | $\sigma ^2 _e + g \sigma^2 _{R}$
Genotype (G)             |           $MS_{G}$ | $\sigma ^2 _e + r \sigma ^2 _{GE} + rg \sigma ^2 _{G}$
G x E                    |          $MS_{GE}$ | $\sigma ^2 _e + r \sigma ^2 _{GE}$
Error                    |           $MS_{e}$ | $\sigma ^2 _e$

http://www.knowledgebank.irri.org/ricebreedingcourse/Lesson_6__Multi-environment_trials___design_and_analysis_.htm (see also for table providing necessary replicates and predicted LSD)

Thus, $\sigma ^2 _{GE} = (MS_{GE} - MS_{e})/r$ and $\sigma ^2 _{E} = (MS_{G} - MS_{GE})/rg$

```{r}
st.aov <- aov(Yield ~ Variety + Trial + Variety:Trial + Trial:Rep,data=p399)
st.aov.tbl <- anova(st.aov)
st.aov.tbl

trts <- length(levels(p399$Variety))
trials <- length(levels(p399$Variety))
blocks <- length(levels(p399$Rep))

#residual
rms <- st.aov.tbl[5,3]

#rep in trial
msr <- st.aov.tbl[4,3]
(msr-rms)/trts
sr <- sqrt((msr-rms)/trts)
#trt by trial
msge <- st.aov.tbl[3,3]
(msge-rms)/blocks
sge <- sqrt((msge-rms)/blocks)

#trials
mse <- st.aov.tbl[2,3]
(mse- msr - msge + rms)/(trts*blocks)
se <- sqrt((mse- msr - msge + rms)/(trts*blocks))

sqrt(rms)
se 
sr
sge


trts <- length(levels(Multilocation$Trt))
trials <- length(levels(Multilocation$Location))
blocks <- length(levels(p399$Rep))
sas.aov <- aov(Adj ~ Trt + Location + Location:Trt + Location:Block,data=Multilocation)
sas.aov.tbl <- anova(sas.aov)
sas.aov.tbl

#residual
rms <- sas.aov.tbl[5,3]

#rep in trial
msr <- sas.aov.tbl[4,3]
sr <- sqrt((msr-rms)/trts)
#trt by trial
msge <- sas.aov.tbl[3,3]
sge <- sqrt((msge-rms)/blocks)

#trials
mse <- sas.aov.tbl[2,3]
se <- sqrt((mse- msr - msge + rms)/(trts*blocks))

sqrt(rms)
se 
sr
sge


```

Fixed Effect model
------------------
Variety * Trial + 1 | Trial:Rep




#### Homogenous
```{r}
hom.fix <- as.formula(Yield ~ Variety)
hom.ran <- as.formula(~ Trial/Rep + Variety:Trial)
hom.form <- as.formula(Yield ~ Variety + (1 | Trial/Rep) + (1 | Variety:Trial))
```
#### Heterogeneous model 1
```{r}
het1.fix <- as.formula(Yield ~ Variety)
het1.ran <- as.formula(~ Trial/Rep + idh(Variety):Trial)
het1.form <- as.formula(Yield ~ Variety + (1 | Trial/Rep) + (Variety | Trial))
```
#### Heterogeneous model 2
```{r}
het2.rcov <- as.formula(~idh(Trial):units)
```

#### Heterogeneous model 3

### lme

```{r}
library(nlme)
p399$Block <- p399$Trial:p399$Rep
p399$GEI <- p399$Trial:p399$Variety
p399.grp <- groupedData(Yield ~ 1 |Trial/Rep, data=p399)

st.1.lme <- lme(Yield ~ Variety*Trial,random = ~ 1 | Block,data=p399.grp)
print(st.1.lme,correlation=FALSE,digits=10)
st.2.lme <- lme(Yield ~ Variety + Variety:Trial, random = ~ 1 | Trial/Rep, data = p399.grp)
print(st.2.lme,correlation=FALSE,digits=10)

st.3.lme <- lme(Yield ~ Variety, p399.grp, random=pdBlocked(list(pdIdent(~ Trial - 1),pdIdent(~ Variety - 1))))
print(st.3.lme,correlation=FALSE,digits=10)

Multilocation.grp <- groupedData(Adj ~ 1 |Location/Block, data=Multilocation)
Multilocation.blocks <- groupedData(Adj ~ 1 |Block, data=Multilocation)
sas.1.lme <- lme(Adj ~ Trt*Location,random = ~ 1 | Grp,data=Multilocation.grp)
print(sas.1.lme,correlation=FALSE,digits=10)
sas.2.lme <- lme(Adj ~ Trt + Trt:Location, random = ~ 1 | Location/Block, data = Multilocation.grp)
print(sas.2.lme,correlation=FALSE,digits=10)

#note - we need -1 so that we don't have duplicated column names
sas.3.lme <- lme(Adj ~ Trt, Multilocation.grp, random=pdBlocked(list(pdIdent(~ Location-1),pdIdent(~ Trt-1))))
print(sas.3.lme,correlation=FALSE,digits=10)
lme(Adj ~ Trt, Multilocation.blocks, random=pdBlocked(list(pdIdent(~ Trt-1),pdIdent(~ Location-1))))
lme(Adj ~ Trt, Multilocation.grp, random=pdIdent(~ Trt-1))
#not quite
#lme(Adj ~ Trt, Multilocation.grp, random=pdBlocked(list(pdIdent(~ 1),pdIdent(~ Location-1),pdIdent(~ Trt-1))))
```

lme allows specification of different correlation structures, corAR1, corCAR1, corCompSymm 

### lmer
```{r}
library(lme4)
```

Homgenous random effects
```{r}
st.1.lmer <- lmer(Yield ~ Variety*Trial + (1 | Trial:Rep),data=p399)
print(st.1.lmer,correlation=FALSE,digits=10)
st.2.lmer <- lmer(Yield ~ Variety + Variety:Trial + (1 | Trial/Rep),data=p399)
print(st.2.lmer,correlation=FALSE,digits=10)
st.3.lmer <- lmer(Yield ~ Variety + (1 | Trial/Rep) + (1 | Trial:Variety),data=p399)
print(st.3.lmer,correlation=FALSE,digits=10)
st.4.lmer <- lmer(Yield ~ (1 | Variety) + (1 | Trial/Rep) + (1 | Trial:Variety),data=p399)
print(st.3.lmer,correlation=FALSE,digits=10)
```

```{r}
sas.1.lmer <- lmer(Adj ~ Trt*Location + (1 | Location:Block),data=Multilocation)
print(sas.1.lmer,correlation=FALSE,digits=10)
sas.2.lmer <- lmer(Adj ~ Trt + Trt:Location + (1 | Location/Block),data=Multilocation)
print(sas.2.lmer,correlation=FALSE,digits=10)
sas.3.lmer <- lmer(Adj ~ Trt + (1 | Location/Block) + (1 | Location:Trt),data=Multilocation)
print(sas.3.lmer,correlation=FALSE,digits=10)
```

### MCMCglmm
```{r}
library(MCMCglmm)
```

```{n}
nin.1.MCMCglmm <- MCMCglmm(fixed=yield ~ variety, random = ~ Block,data=Wheat2, verbose=FALSE)
summary(nin.1.MCMCglmm)
```

```{r}
st.1.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety*Trial, random = ~ Trial:Rep,data=p399, verbose=FALSE)
summary(st.1.MCMCglmm)
#Trial/Rep syntax does not work
st.2.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety + Variety:Trial, random = ~ Trial + Trial:Rep,data=p399, verbose=FALSE)
summary(st.2.MCMCglmm)
st.3.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety, random = ~ Trial + Trial:Rep + Variety:Trial,data=p399, verbose=FALSE)
summary(st.3.MCMCglmm)
```

### glmmADMB
mcmc=FALSE -  default, true is to run MCMC after fitting.

```{r}
library(glmmADMB)

nin.1.admb <- glmmadmb(yield ~ variety, random = ~ 1 | Block, family = "gaussian", data = Wheat2)
summary(nin.1.admb)

st.1.admb <-  glmmadmb(Yield ~ Variety*Trial, random = ~ 1 | Block, family = "gaussian", data = p399)
summary(st.1.admb)
st.2.admb <-  glmmadmb(Yield ~ Variety + Variety:Trial, random = ~ 1 | Trial/Rep, family = "gaussian", data = p399)
summary(st.2.admb)

sas.1.admb <-  glmmadmb(Adj ~ Trt*Location, random = ~ 1 | Grp, family = "gaussian", data = Multilocation)
summary(sas.1.admb)
sas.2.admb <-  glmmadmb(Adj ~ Trt + Trt:Location, random = ~ 1 | Location/Block, family = "gaussian", data = Multilocation)
summary(sas.2.admb)
```
                            
### glmmAK


### glmmGS
glmmGS only supports poisson and binomial families
```{r}
#library(glmmGS)
#glmmGS(Yield ~ Variety + (1 | Trial/Rep), family = "gaussian",data = p399)
```

### glmmLasso
```{r}
library(glmmLasso)

nin.1.glmmLasso <- glmmLasso(yield ~ variety, rnd = list(Block=~1), lambda=200, data = Wheat2)
summary(nin.1.glmmLasso)

lm1 <- glmmLasso(Yield ~ Variety, rnd = list(Rep=~1), lambda=200, data = p399)
lm1
#fails
#glmmLasso(Yield ~ Variety, rnd = list(Trial=~1,GEI=~1), lambda=20, data = p399)
```


### glmmPQL
glmmPQL works by repeated calls to lme

```{r}
library(MASS)

nin.glmmPQL <- glmmPQL(yield ~ variety, random = ~ 1 | Block,family=gaussian, data = Wheat2)
summary(nin.glmmPQL)

hom.glmmPQL <- glmmPQL(Yield ~ Variety, random = ~ 1 | Trial/Rep,family=gaussian, data = p399)
#het.glmmPQL <- glmmPQL(Yield ~ Variety, random = ~ 1 | Variety:Trial,family=gaussian, data = p399)
hom.glmmPQL
```


### glmmML

### fastrml


```{r}
#hom.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety, random = ~ Trial + Trial:Rep + Variety:Trial,data=p399, verbose=FALSE)
#summary(hom.MCMCglmm)
#het1.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety, random = ~ Trial + Trial:Rep + idh(Variety):Trial,data=p399, verbose=FALSE)
#summary(het1.MCMCglmm)
#het2.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety, random = ~ Trial + Trial:Rep + Variety:Trial,data=p399,rcov=as.formula(~idh(Trial):units), verbose=FALSE)
#summary(het2.MCMCglmm)
#het3.MCMCglmm <- MCMCglmm(fixed=Yield ~ Variety, random = ~ Trial + Trial:Rep + idh(Variety):Trial,data=p399,rcov=as.formula(~idh(Trial):units), verbose=FALSE)
#summary(het3.MCMCglmm)
```

### regress
regress: Gaussian linear models with linear covariance structure

### pedigreemm

Repeat Zhang
------------
http://www.admb-project.org/examples/r-stuff/lmer-comparison

A note on terms. 
---------------
Mixed models are frequently described in the context of heirarchical models. Heirarchical models can be represented as nested linear (regression) models - each level of the heirarchy as a unique regression.  Within each level there are two options for regression
### Varying-intercept
### Varying-intercept, varying slope

For most R packages, the first (for effect B nested in A) is denoted (1 | A/B), the second as (A | B)
??? Is this accurate??


### Matrix forms
from nlme

1. pdSymm
   * general positive-definite matrix, with no additional structure
2. pdLogChol
   * general positive-definite matrix, with no additional structure, using a log-Cholesky parameterization
3. pdDiag
   * diagonal
4. pdIdent
   * multiple of an identity
5. pdCompSymm
   * compound symmetry structure (constant diagonal and constant off-diagonal elements)
6. pdBlocked
   * block-diagonal matrix, with diagonal blocks of any "atomic" pdMat class
7. pdNatural
   * general positive-definite matrix in natural parametrization (i.e. parametrized in terms of standard deviations and correlations). The underlying coefficients are not unrestricted, so this class should NOT be used for optimization.


### Correlation Structures

1. corAR1  
   * autoregressive process of order 1.
2. corARMA  
   * autoregressive moving average process, with arbitrary orders for the autoregressive and moving average components.
3. corCAR1	
   * continuous autoregressive process (AR(1) process for a continuous time covariate).
4. corCompSymm	
   * compound symmetry structure corresponding to a constant correlation.
5. corExp	
   * exponential spatial correlation.
6. corGaus	
   * Gaussian spatial correlation.
7. corLin	
   * linear spatial correlation.
8. corRatio	
   * Rational quadratics spatial correlation.
9. corSpher	
   * spherical spatial correlation.
10. corSymm	
   * general correlation matrix, with no additional structure.

\section{Interblock analysis}
The interblock analysis provides least squares means using a mixed model estimate.

interblock <- lm(Yield ~ Trt + Rep + BlockInRep:Rep + ColInRep:Rep,data=SlateHall)
intrablock <- lmer(Yield ~ Trt + (1 | Rep) +  (1 | BlockInRep:Rep) +  (1 | ColInRep:Rep),data=SlateHall)
intrablock.means <- lsmeans(intrablock, ~ Trt)


We want to duplicate models of the form (from http://stats.stackexchange.com/questions/18709/lme4-or-other-open-source-r-package-code-equivalent-to-asreml-r)


data(nin89)

# Model 1: RCB analysis with G and R structure
rcb.asr <- asreml(yield ~ Variety, random = ~ idv(Replicate), rcov = ~ idv(units), data = nin89)

# Model 2: two-dimensional spatial model with correlation in one direction
sp.asr <- asreml(yield ~ Variety, rcov = ~ Column:ar1(Row), data = nin89)

# model 3: two-dimensional spatial model, error structure in both direction
sp.asr <- asreml(yield ~ Variety, rcov = ~ ar1(Column):ar1(Row),  data = nin89)
sp.asr <- asreml(yield ~ Variety, random = ~ units, rcov = ~ ar1(Column):ar1(Row), data = nin89)



glmmADMB
install.packages("glmmADMB", repos="http://r-forge.r-project.org",
                      type="source")
install.packages("glmmADMB",repos=c("http://glmmadmb.r-forge.r-project.org/repos", getOption("repos")),type="source")
                                                       
### glmmAK

### glmmBUGS

### glmmGS
This project implements a block-wise Gauss-Seidel (GS) algorithm to fit Generalized Linear Mixed Models (GLMMs). The GS algorithm allows for a significant performance increase and memory saving.

### glmmLasso
An Algorithm for High-Dimensional Generalized Linear Mixed Models Using L1-Penalization

### glmmPQL
Schall, R. (1991) Estimation in generalized linear models with random effects. Biometrika 78, 719--727.
Breslow, N. E. and Clayton, D. G. (1993) Approximate inference in generalized linear mixed models. Journal of the American Statistical Association 88, 9--25.
Wolfinger, R. and O'Connell, M. (1993) Generalized linear mixed models: a pseudo-likelihood approach. Journal of Statistical Computation and Simulation 48, 233--243.
Venables, W. N. and Ripley, B. D. (2002) Modern Applied Statistics with S. Fourth edition. Springer.

summary(glmmPQL(y ~ trt + I(week > 2), random = ~ 1 | ID, family = binomial, data = bacteria))



### glmmML
Brostrm, G. and Holmberg, H. (2011). Generalized linear models with clustered data: Fixed and random effects models. Computational Statistics and Data Analysis 55:3123-3134.


### minque

```{r}
library(minque)
st.1.minque <- lmm(Yield ~ Variety*Trial | Trial:Rep,data=p399)
print(st.1.minque,correlation=FALSE,digits=10)
st.1.minque[[1]]$Var
st.1.minque[[1]]$FixedEffect
st.2.minque <- lmm(Yield ~ Variety + Variety:Trial | Trial/Rep,data=p399)
print(st.2.minque,correlation=FALSE,digits=10)
st.2.minque[[1]]$Var
st.2.minque[[1]]$FixedEffect
st.3.minque <- lmm(Yield ~ Variety| Trial/Rep + Trial:Variety,data=p399)
st.3.minque[[1]]$Var
st.3.minque[[1]]$FixedEffect
st.4.minque <- lmm(Yield ~ 1 | Trial*Variety + Trial/Rep,data=p399)
st.4.minque[[1]]$Var
st.4.minque[[1]]$FixedEffect
```

```{r}
data(ncii)
ncii.lmer <- lmer(Yld ~ (1|Female) + (1|Male) + (1|Female:Male)+(1 | Rep),data=ncii)
VarCorr(ncii.lmer)
res=lmm(Yld~1|Female*Male+Rep,data=ncii,method=c("reml","minque"))
res[[1]]$Var
res[[1]]$FixedEffect
res[[1]]$RandomEffect


data(brate)
brate$Geno=factor(brate$Geno)
brate$Pos=factor(brate$Pos)
brate$Rep=factor(brate$Rep)

brate.lmer <- lmer(Brate ~ (1|Geno) + (1|Pos) + (1|Geno:Pos)+(1 | Rep),data=brate)
VarCorr(brate.lmer)
res=lmm(Brate~1|Geno*Pos+Rep,data=brate)

res[[1]]$Var
res[[1]]$FixedEffect
#res[[1]]$RandomEffect
res=lmm.jack(Brate~1|Geno*Pos+Rep,data=brate,JacNum=10,JacRep=1,ALPHA=0.05)
res[[1]]$Var
res[[1]]$PVar
res[[1]]$FixedEffect
#res[[1]]$RandomEffect


data(cot)

cot$Geno=factor(cot$Geno)
cot$Loc=factor(cot$LOC)
cot$Rep=factor(cot$REP)
cot.lmer <- lmer(LY ~ (1|Geno) + (1|Loc) + (1|Geno:Loc)+(1 | Loc:Rep),data=cot)
VarCorr(cot.lmer)
res=lmm(LY~1|Geno*Loc+Loc:Rep,data=cot)
res[[1]]$Var
sqrt(res[[1]]$Var[[1]][,1])
res[[1]]$FixedEffect
#res[[1]]$RandomEffect
res=lmm.jack(LY~1|Geno*Loc+Loc:Rep,data=cot,JacNum=10,JacRep=1,ALPHA=0.05)
res[[1]]$Var
res[[1]]$PVar
res[[1]]$FixedEffect
#res[[1]]$RandomEffect
sqrt(res[[1]]$Var[[1]][,1])
```

Jackknife and Bootstrap methods
Permutation
