Spatial Analysis
========================================================

Tests for spatial heterogeneity
-------------------------------
From http://www.unc.edu/courses/2007spring/enst/562/001/docs/lectures/lecture42.htm
### Mantel test

```{r}
library(nlme)
data(Wheat2)

dist1<-dist(cbind(Wheat2$latitude, Wheat2$longitude))
dist2<-dist(Wheat2$yield)

library(vegan)
mantel(dist1,dist2)
```

The Mantel test indicates spatial variance, but how is it to be modelled?

From the web site above, we can fit the residual semivariogram. 
```{r}
library(geoR)

gmodel2<-gls(yield~variety+Block, data=Wheat2, method='ML')
newdat<-data.frame(Wheat2$latitude, Wheat2$longitude, residuals(gmodel2, type='n'))
geodat<-as.geodata(newdat)
geodat.v1 <- variog(geodat, uvec=1:50, max.dist=30, option='bin')
plot(geodat.v1)
```
I'm not sure I like including Block, since it's not uniform.
```{r}
gmodel3<-gls(yield~variety, data=Wheat2, method='ML')
newdat2<-data.frame(Wheat2$latitude, Wheat2$longitude, residuals(gmodel3, type='n'))
geodat<-as.geodata(newdat2)
geodat.v2 <- variog(geodat, uvec=1:50, max.dist=30, option='bin')
plot(geodat.v2)
```

```{r}
plot(geodat.v2)
ols2<-variofit(geodat.v2, ini=c(.8,30), nugget=.4, cov.model='exponential')
lines(ols2,col=2)
ols3<-variofit(geodat.v2, ini=c(.8,30), nugget=.4, cov.model='gaussian')
lines(ols3,col=4)
ols4<-variofit(geodat.v2, ini=c(.8,30), nugget=.4, cov.model='spherical')
lines(ols4,col=3)
ols5<-variofit(geodat.v2, ini=c(.8,30), nugget=.4, cov.model='linear')
lines(ols5,col='gray70')
legend(18,.5, c('exponential', 'Gaussian', 'spherical', 'linear'), col=c(2:4, 'gray70'), lty=rep(1,4), cex=.8, bty='n')
```

```{r}
library(agridat)
data(stroup.nin) #same as nin89 from ASReml-R

library(nlme)
data(Wheat2) #same as above, with some minor differences


stroup.nin <- subset(stroup.nin,!is.na(stroup.nin$yield))
length(stroup.nin$yield)
length(Wheat2$yield)

plot.matrix <- function(x,colors=NULL, title="Matrix") {
  if(is.null(colors)) {
		col_fun<-colorRampPalette(colors=c('white','black'))
		colors<-col_fun(256)
	}
	x.r <- nrow(x)
	x.c <- ncol(x)
	z <- array(x,dim=c(x.r,x.c))
	image(1:x.r,1:x.c,z, main=title,col=colors,xlab="",ylab="")
}
```

Note that lat and longitude are spaced differently.
max long = 26.4, max lat = 47.3

```{r fig.width=5.4, fig.height=9.6}
plot(latitude~longitude, col=as.numeric(Block), data=Wheat2)
```

Note that Block is effectively usesless. We can create a couple dummy variables
```{r}
Wheat2$Row <- as.factor(Wheat2$latitude/4.3)
Wheat2$Col <- as.factor(Wheat2$longitude/1.2)
```


```{r}
lme(yield ~ variety, random = ~ 1 | Row, data = Wheat2)
Wheat.ar1 <- lme(yield ~ variety, random = ~ 1 | latitude, data = Wheat2,corr = corAR1(form = ~ 1 | latitude))
anova(Wheat.ar1)
ranef(Wheat.ar1)
```

```{r fig.width=7, fig.height=6}
ACF(Wheat.ar1)
```

```{r}
Wheat.ar1.2 <- lme(yield ~ variety, random = ~ 1 | latitude, data = Wheat2,corr = corCAR1(form = ~ 1 | latitude))
anova(Wheat.ar1.2)
Wheat.ar1.2
```

```{r fig.width=7, fig.height=6}
plot(ACF(Wheat.ar1.2))
```

Two-dimensional auto regressive.

According to Pinheiro, p 233, we should be able to define a corStruct matrix of the form
```
form = ~ x + y
```
were x and y define a two-dimensional position vector.


This form gives us a singular convergence.
```
Wheat.ar1.3 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corCAR1(form = ~ latitude + longitude))
```

But not with
```{r}
Wheat.ar1.3a <- lme(yield ~ variety, random = ~ 1 | Row, data = Wheat2, corr = corCAR1(form = ~ latitude + longitude))
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.3a,form = ~ latitude + longitude | Block))
```

Similarly, AR1 works ok.
```{r}
#Wheat.ar1.3 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corAR1(form = ~ latitude))
#Wheat.ar1.3 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corAR1(form = ~ latitude + longitude))
```
```{r fig.width=7, fig.height=6}
#plot(Variogram(Wheat.ar1.3,form = ~ latitude + longitude))
```

```{r}
#Wheat.ar1.3
```

However, we really want a distance between x,y pairs. corExp uses euclidean distance.

```{r}
wht.cor <- corAR1(form = ~ latitude + longitude)
wht.cor <- Initialize(wht.cor,Wheat2)
```
```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor))
```
```{r}
wht.cor <- corCAR1(form = ~ latitude + longitude)
wht.cor <- Initialize(wht.cor,Wheat2)
```
```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor))

```
```{r}
wht.cor <- corExp(1,form = ~ latitude + longitude)
wht.cor <- Initialize(wht.cor,Wheat2)
dim(corMatrix(wht.cor))
```
```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor))
```
```{r}
wht.cor.2 <- corExp(1,form = ~ Row + Col)
wht.cor.2 <- Initialize(wht.cor.2,Wheat2)
#head(corMatrix(wht.cor.2))
```
```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor.2))
```
```{r}
wht.cor.2 <- corGaus(1,form = ~ Row + Col)
wht.cor.2 <- Initialize(wht.cor.2,Wheat2)
```

```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor.2))
```
```{r}
wht.cor.2 <- corSpher(1,form = ~ Row + Col)
wht.cor.2 <- Initialize(wht.cor.2,Wheat2)
```
```{r fig.width=7, fig.height=6}
plot.matrix(corMatrix(wht.cor.2))
```

```{r}
Wheat.ar1.4 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corExp(form = ~ latitude + longitude))
Wheat.ar1.4
```

```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.4,form = ~ latitude + longitude | Block))
```

We can also define other spatial correlation structures. Littell cites a spherical covariance model.
```{r}
Wheat.ar1.5 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corSpher(form = ~ longitude+ latitude))
Wheat.ar1.5
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.5))
```

Littell report a range of 18.1 and a sill of 61.6. The data in the appendix use lat and lon
```{r}
stroup.ar1.5 <- lme(yield ~ gen, random = ~ 1 | rep, data = stroup.nin, corr = corSpher(form = ~ x + y))
stroup.ar1.5
```
```{r fig.width=7, fig.height=6}
plot(Variogram(stroup.ar1.5))
```
     
```{r}
Wheat.ar1.6 <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corGaus(form = ~ latitude + longitude,nugget=TRUE))

Wheat.ar1.6
Variogram(Wheat.ar1.6)
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.6))
```
```{r fig.width=7, fig.height=6}
plot(Wheat.ar1.6)
```
```{r}
ranef(Wheat.ar1.6)
```

```{r}
Wheat.ar1.7.a <- lme(yield ~ variety, random = ~ 1 | Block, data = Wheat2, corr = corRatio(form = ~ latitude + longitude))
Wheat.ar1.7.b <- lme(yield ~ variety, random = ~ 1 | Row, data = Wheat2, corr = corRatio(form = ~ latitude + longitude))
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.7.a))
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.7.b))
```

We should not that corLin does not work if we use Block as random effect
```{r}
Wheat.ar1.8 <- lme(yield ~ variety, random = ~ 1 | Row, data = Wheat2, corr = corLin(form = ~ latitude + longitude))
Wheat.ar1.8
```
```{r fig.width=7, fig.height=6}
plot(Variogram(Wheat.ar1.8))
```


