---
title: "Case Study 1, Part 3"
author: "Peter Claussen"
date: "10/3/2017"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(gstat)
library(ape)
library(ggplot2)

library(rsm)
library(ncf)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```

Now we consider trend analysis. First, using the pooled data, what is an appropriate polynomial?

# Load Data
```{r, LoadData}
load(file="Pooled.Rda")
```

```{r}
Pooled.dat <- rbind(Corn2013.dat,Corn2015.dat,Soybean2014.dat,Soybean2016.dat)
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Quantile),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Quantile", x="Longitude (m)", y="Latitude (m)", title = "Pooled Quantile Maps")
```

# Fit polynomial models

```{r}
Quantile5.lm <- lm(Quantile ~ poly(Easting, Northing, degree=5), data=Pooled.dat)
Quantile6.lm <- lm(Quantile ~ poly(Easting, Northing, degree=6), data=Pooled.dat)
Quantile7.lm <- lm(Quantile ~ poly(Easting, Northing, degree=7), data=Pooled.dat)
Quantile8.lm <- lm(Quantile ~ poly(Easting, Northing, degree=8), data=Pooled.dat)
Quantile9.lm <- lm(Quantile ~ poly(Easting, Northing, degree=9), data=Pooled.dat)
```

Here we see one limitation of trend analysis - it doesn't work well if we don't have a rectangular shape. The missing corner in our field tends to induce a bias in the models.

```{r,fig.width=7,fig.height=8}
par(mfrow=c(3,1))
contour(Quantile5.lm, Northing ~ Easting, image = TRUE)
contour(Quantile7.lm, Northing ~ Easting, image = TRUE)
contour(Quantile9.lm, Northing ~ Easting, image = TRUE)
par(mfrow=c(1,1))
```

```{r,fig.width=7,fig.height=8}
par(mfrow=c(3,1))
contour(Quantile6.lm, Northing ~ Easting, image = TRUE)
contour(Quantile7.lm, Northing ~ Easting, image = TRUE)
contour(Quantile8.lm, Northing ~ Easting, image = TRUE)
par(mfrow=c(1,1))
```

# Extract residuals

```{r,ExtractResiduals}
Pooled.dat$Quantile5.resid <- Quantile5.lm$residuals
Pooled.dat$Quantile6.resid <- Quantile6.lm$residuals
Pooled.dat$Quantile7.resid <- Quantile7.lm$residuals
Pooled.dat$Quantile8.resid <- Quantile8.lm$residuals
Pooled.dat$Quantile9.resid <- Quantile9.lm$residuals
```

# Check for white noise

The paired distance matrix is very large (1Gb) so we should save between analyses.
```{r,ComputeI}
if(!file.exists("Distance.Rda")) {
  Distance.mat <- as.matrix(dist(cbind(Pooled.dat$Easting, Pooled.dat$Northing)))
  Distance.mat <- 1/Distance.mat
  diag(Distance.mat) <- 0
  save(Distance.mat,file="Distance.Rda")
} else {
  load(file="Distance.Rda")
}

```

```{r}
if(!file.exists("TrendI.Rda")) {
  Moran5 <- Moran.I(Pooled.dat$Quantile5.resid, Distance.mat)
  Moran6 <- Moran.I(Pooled.dat$Quantile6.resid, Distance.mat)
  Moran7 <-Moran.I(Pooled.dat$Quantile7.resid, Distance.mat)
  Moran8 <-Moran.I(Pooled.dat$Quantile8.resid, Distance.mat)
  Moran9 <-Moran.I(Pooled.dat$Quantile9.resid, Distance.mat)
  save(Moran5, Moran6, Moran7, Moran8, Moran9, file="TrendI.Rda")
} else {
  load(file="TrendI.Rda")
}
print(Moran5)
print(Moran6)
print(Moran7)
print(Moran8)
print(Moran9)
```

# Plot $I$

```{r}
fit.dat <- data.frame(
  Polynomial =  seq(5,9),
  I = c(Moran5$observed,
       Moran6$observed,
       Moran7$observed,
       Moran8$observed,
       Moran9$observed
)
   )
plot(I ~ Polynomial, data=fit.dat)
lines(I ~ Polynomial, data=fit.dat)

```

We can also reasonably use nested AOV to compare. 

```{r, ANOVA}
anova(Quantile5.lm, Quantile6.lm,Quantile7.lm,Quantile8.lm, Quantile9.lm)
```

ANOVA suggests 8, since there is relatively little improvement at between 8 and 9 ($\Delta SS \sim 10$).

We've fit a mean trend for four maps, but we also want to capture some of the year to year variability. To do this, we can extend our trend to include an interaction term:
```{r}
Pooled.dat$Crop <- "Corn"
Pooled.dat$Crop[Pooled.dat$Year==2014] <- "Soybean"
Pooled.dat$Crop[Pooled.dat$Year==2016] <- "Soybean"
Pooled.dat$Crop <- as.factor(Pooled.dat$Crop)
Pooled.dat$Year <- as.factor(Pooled.dat$Year)
```

```{r}
Quantile7Interaction.lm <- lm(Quantile ~ poly(Easting, Northing, degree=7) + Crop:poly(Easting, Northing, degree=7)+ Crop:Year:poly(Easting, Northing, degree=7), data=Pooled.dat)
summary(aov(Quantile7Interaction.lm))
```

Does this improve the residuals?
```{r}
Pooled.dat$Quantile7Interaction.resid <- Quantile7Interaction.lm$residuals
if(!file.exists("Moran7InteractionI.dat")) {
  Moran7InteractionI <-Moran.I(Pooled.dat$Quantile7Interaction.resid, Distance.mat)
  save(Moran7InteractionI, file="Moran7InteractionI.dat")
} else {
  load(file="Moran7InteractionI.dat")
}
print(Moran7InteractionI)
```

```{r}
#reclaim some memory
Distance.mat <- NULL
```


### Surface Plots

```{r,fig.width=7,fig.height=8}
par(mfrow=c(3,1))
image(Quantile7.lm, Northing ~ Easting)
contour(Quantile7.lm, Northing ~ Easting, image = TRUE)
persp(Quantile7.lm, Northing ~ Easting, zlab = "Quantile, Poly 7")
```

```{r,fig.width=7,fig.height=8}
par(mfrow=c(3,1))
image(Quantile7Interaction.lm, Northing ~ Easting)
contour(Quantile7Interaction.lm, Northing ~ Easting, image = TRUE)
persp(Quantile7Interaction.lm, Northing ~ Easting, zlab = "Quantile, Poly 7 Interaction")
```



### Residual Plots

```{r}
if(!file.exists("TrendsLISA.Rda")) {
  Quantile7.resid.lisa <- lisa(Pooled.dat$Easting, Pooled.dat$Northing, Pooled.dat$Quantile7.resid, 
                         neigh=30, resamp=10, quiet=TRUE)
  Quantile7Interaction.resid.lisa <- lisa(Pooled.dat$Easting, Pooled.dat$Northing, Pooled.dat$Quantile7Interaction.resid, 
                         neigh=30, resamp=10, quiet=TRUE)
  save(fit.dat, Quantile7.resid.lisa, Quantile7Interaction.resid.lisa, file="TrendsLISA.Rda")
} else {
  load(file="TrendsLISA.Rda")
}
```

```{r,Quantile7,fig.width=8,fig.height=4}
plot.lisa(Quantile7.resid.lisa, negh.mean=FALSE)
```

```{r,Quantile7Interaction,fig.width=8,fig.height=4}
plot.lisa(Quantile7Interaction.resid.lisa, negh.mean=FALSE)
```

