---
title: "Case Study 1"
author: "Peter Claussen"
date: "10/3/2017"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(gstat)
library(MASS)
library(ape)
library(ncf)
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```

```{r}
load(file="Pooled.Rda")
```

```{r}
Pooled.dat <- rbind(Corn2013.dat,Corn2015.dat,Soybean2014.dat,Soybean2016.dat)
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Quantile),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Quantile", x="Longitude (m)", y="Latitude (m)", title = "Pooled Yield Maps")
```

# Grid Cells

Using the same grid cells as before, divide the pooled data into a network. We'll proceed on the assumption that the four years data is uniform enough to be pooled.

```{r}
Pooled.dat$Row <- ceiling((Pooled.dat$Northing+0.1)/20)
Pooled.dat$Column <- ceiling((Pooled.dat$Easting+0.1)/20)
Pooled.dat$Cell <- as.factor(Pooled.dat$Row):as.factor(Pooled.dat$Column)
```

### Cell Borders

```{r}
rowPoints <- c(0,20*(1:ceiling(max(Pooled.dat$Northing+0.1)/20)))
               
colPoints <- c(0,20*(1:ceiling(max(Pooled.dat$Easting+0.1)/20)))
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
  geom_point(aes(colour = Quantile),size=1) + 
  scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Cell Grid over Data")
```


## Sample Grid

We will need a set of fixed points for interpolation. Since we have a 20x20m grid, we place points at 10m intervals, and offset by 5ms from the origin.
```{r}
columns <- ceiling(max(Pooled.dat$Easting)/10)
rows <- ceiling(max(Pooled.dat$Northing)/10)
Sample10.grd <- expand.grid(Northing=((1:rows)*10)-5,
                          Easting=((1:columns)*10)-5)
Sample10.grd$Row <- ceiling((Sample10.grd$Northing-5+0.1)/20)
Sample10.grd$Column <- ceiling((Sample10.grd$Easting-5+0.1)/20)
Sample10.grd$Cell <- as.factor(Sample10.grd$Row):as.factor(Sample10.grd$Column)
head(Sample10.grd)
```


```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
  geom_point(aes(colour = Quantile),size=1) + 
  scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_point(aes(Easting, Northing),data=Sample10.grd, size=1) + 
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Uniform Grid, 10x10")
```


```{r}
Grid.dat <- data.frame(
   Cell = levels(Sample10.grd$Cell),
   Easting = as.vector(tapply(Sample10.grd$Easting,list(Sample10.grd$Cell),mean,na.rm=TRUE)),
   Northing = as.vector(tapply(Sample10.grd$Northing,list(Sample10.grd$Cell),mean,na.rm=TRUE))
)

CellMeans = tapply(Pooled.dat$Quantile,list(Pooled.dat$Cell),mean,na.rm=TRUE)
Grid.dat$CellMeans <- as.vector(CellMeans[as.character(Grid.dat$Cell)])
CellCounts = tapply(Pooled.dat$Quantile,list(Pooled.dat$Cell),length)
Grid.dat$CellCounts <- as.vector(CellCounts[as.character(Grid.dat$Cell)])

truehist(Grid.dat$CellCounts)
```

We'll keep any grid cell that has at least 20 observations.

```{r}
Grid.dat <- subset(Grid.dat,Grid.dat$CellCounts>19)
# this is cheap way to remove extra cells
Grid.dat$Cell <- as.factor(as.character(Grid.dat$Cell))
Sample10.grd <- subset(Sample10.grd, Sample10.grd$Cell %in% levels(Grid.dat$Cell))
Sample10.grd$CellMeans <- as.vector(CellMeans[as.character(Sample10.grd$Cell)])
head(Sample10.grd)
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
  geom_point(aes(colour = Quantile),size=1) + 
  scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_point(aes(Easting, Northing),data=Sample10.grd, size=1) + 
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Uniform Grid, 10x10")
```

```{r,fig.width=8,fig.height=4}
ggplot(Sample10.grd, aes(Easting, Northing)) + 
  geom_point(aes(colour = CellMeans),size=3) + 
  scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Cell Means and Grid Cells")
```

# Trend Estimates

```{r}
load(file="Trends.Rda")
Sample10.grd$Quantile.trend <- predict(Quantile7.lm,Sample10.grd)
```

```{r,fig.width=8,fig.height=4}
ggplot(Sample10.grd, aes(Easting, Northing)) + 
  geom_point(aes(colour = Quantile.trend),size=3) + 
  scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Trend Yield and Grid Cells")
```

```{r}
TrendMeans = tapply(Sample10.grd$Quantile.trend,list(Sample10.grd$Cell),mean,na.rm=TRUE)
Grid.dat$TrendMeans <- as.vector(TrendMeans[as.character(Grid.dat$Cell)])
```

# Kriging

Load our variograms
```{r}
load(file="Variograms.Rda")
```

On my machine, kriging this data set takes about 2 hours. We'll save the fitted values

```{r,Kriging}
if(!file.exists("GridKrig.Rda")) {
  Quantile.krig <- krige(id="Quantile", 
                     formula=Quantile~1, 
                     data = Pooled.dat, 
                     newdata = Sample10.grd, 
                     model = Pooled.vgm,
                     maxdist = 100,
  locations=~Northing + Easting)
  save(Quantile.krig,file="GridKrig.Rda")
} else {
  load(file="GridKrig.Rda")
}
Sample10.grd$Quantile.krig <- Quantile.krig$Quantile.pred
KrigMeans = tapply(Sample10.grd$Quantile.krig,list(Sample10.grd$Cell),mean,na.rm=TRUE)
Grid.dat$KrigMeans <- as.vector(KrigMeans[as.character(Grid.dat$Cell)])
```

### Plot the kriged estimates

```{r,fig.width=8,fig.height=4}
ggplot(Sample10.grd, aes(Easting, Northing)) + 
geom_point(aes(colour = Quantile.krig),size=3) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
  labs(colour = "Yield (quantile)", x="Longitude (m)", y="Latitude (m)", title = "Kriged Yield and Grid Cells")
```

```{r}
plot(Quantile.krig ~ Quantile.trend,data=Sample10.grd)
```

```{r}
plot(KrigMeans~CellMeans,data=Grid.dat,col="blue")
points(TrendMeans~CellMeans,data=Grid.dat,col="red")
```

# Model Comparions

## Global spatial correlation.

We consider global spatial metrics of the three grids using Moran's $I$.

```{r}
grid.dists <- as.matrix(dist(cbind(Grid.dat$Easting, Grid.dat$Northing)))
grid.dists <- 1/grid.dists
diag(grid.dists) <- 0

Moran.I(Grid.dat$CellMeans, grid.dists)
Moran.I(Grid.dat$KrigMeans, grid.dists)
Moran.I(Grid.dat$TrendMeans, grid.dists)
```

## Local spatial correlation.

We also compute local spatial measures. We use a neighborhood of 30 - this gives us 1 grid widths.

```{r}
CellMeans.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$CellMeans, 
                         neigh=61, resamp=1000, quiet=TRUE)
TrendMeans.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$TrendMeans, 
                         neigh=61, resamp=1000, quiet=TRUE)
KrigMeans.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$KrigMeans, 
                         neigh=61, resamp=1000, quiet=TRUE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(CellMeans.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(TrendMeans.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(KrigMeans.lisa, negh.mean=FALSE)
```

# Residuals

## Global spatial correlation.

```{r}
Pooled.dat$KrigVar <- as.vector(Pooled.dat$Quantile - KrigMeans[as.character(Pooled.dat$Cell)])^2
Pooled.dat$TrendVar <- as.vector(Pooled.dat$Quantile - TrendMeans[as.character(Pooled.dat$Cell)])^2
Pooled.dat$CellVar <- as.vector(Pooled.dat$Quantile - CellMeans[as.character(Pooled.dat$Cell)])^2
```

```{r}
Grid.dat$CellVar <- as.vector(tapply(Pooled.dat$CellVar,list(Pooled.dat$Cell),mean,na.rm=TRUE)[as.character(Grid.dat$Cell)])
Grid.dat$TrendVar <- as.vector(tapply(Pooled.dat$TrendVar,list(Pooled.dat$Cell),mean,na.rm=TRUE)[as.character(Grid.dat$Cell)])
Grid.dat$KrigVar <- as.vector(tapply(Pooled.dat$KrigVar,list(Pooled.dat$Cell),mean,na.rm=TRUE)[as.character(Grid.dat$Cell)])
```

```{r}
Moran.I(Grid.dat$CellVar, grid.dists)
Moran.I(Grid.dat$TrendVar, grid.dists)
Moran.I(Grid.dat$KrigVar, grid.dists)
```

## Local spatial correlation.

```{r}
library(ncf)
CellVar.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$CellVar, 
                         neigh=60, resamp=500, quiet=TRUE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(CellVar.lisa, negh.mean=FALSE)
```

```{r}
TrendVar.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$TrendVar, 
                         neigh=60, resamp=500, quiet=TRUE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(TrendVar.lisa, negh.mean=FALSE)
```

```{r}
KrigVar.lisa <- lisa(Grid.dat$Easting, Grid.dat$Northing, Grid.dat$KrigVar, 
                         neigh=60, resamp=500, quiet=TRUE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(KrigVar.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
geom_point(aes(colour = CellVar),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
labs(colour = "Yield (bu/acre)", x="Longitude (m)", y="Latitude (m)", title = "Cell Mean Variance")
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
geom_point(aes(colour = TrendVar),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
labs(colour = "Yield (bu/acre)", x="Longitude (m)", y="Latitude (m)", title = "Trend Cell Variance")
```

```{r,fig.width=8,fig.height=4}
ggplot(Pooled.dat, aes(Easting, Northing)) + 
geom_point(aes(colour = KrigVar),size=1) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
  geom_vline(xintercept = colPoints,color = cbPalette[8]) +
  geom_hline(yintercept = rowPoints,color = cbPalette[6]) +
labs(colour = "Yield (bu/acre)", x="Longitude (m)", y="Latitude (m)", title = "Krig Cell Variance")
```

```{r,MoranIVar}
sample.dists <- as.matrix(dist(cbind(Pooled.dat$Easting, Pooled.dat$Northing)))
sample.dists <- 1/sample.dists
diag(sample.dists) <- 0
if(!file.exists("KrigVarI.Rda")) {
  CellVarI <- Moran.I(Pooled.dat$CellVar, sample.dists,na.rm=TRUE)
  TrendVarI <- Moran.I(Pooled.dat$TrendVar, sample.dists,na.rm=TRUE)
  KrigVarI <- Moran.I(Pooled.dat$KrigVar, sample.dists,na.rm=TRUE)
  save(CellVarI, TrendVarI, KrigVarI, file="KrigVarI.Rda")
} else {
  load(file="KrigVarI.Rda")
}
print(CellVarI)
print(TrendVarI)
print(KrigVarI)
```

```{r,LisaVar}
if(!file.exists("ellVarPooled.Rda")) {
  CellVarPooled.lisa <- lisa(Pooled.dat$Easting, Pooled.dat$Northing, Pooled.dat$CellVar, 
                         neigh=50, resamp=10, quiet=TRUE)
  TrendVarPooled.lisa <- lisa(Pooled.dat$Easting, Pooled.dat$Northing, Pooled.dat$TrendVar, 
                         neigh=50, resamp=10, quiet=TRUE)
  KrigVarPooled.lisa <- lisa(Pooled.dat$Easting, Pooled.dat$Northing, Pooled.dat$KrigVar, 
                         neigh=50, resamp=10, quiet=TRUE)
  save(CellVarPooled.lisa, TrendVarPooled.lisa, KrigVarPooled.lisa, file="KrigVarLISA.Rda")
} else {
  load(file="KrigVarLISA.Rda")
}
```


```{r,fig.width=8,fig.height=4}
plot.lisa(CellVarPooled.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(TrendVarPooled.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=4}
plot.lisa(KrigVarPooled.lisa, negh.mean=FALSE)
```


# Raster Plots

```{r,fig.width=8,fig.height=3}
ggplot(Grid.dat, aes(Easting, Northing)) +
  geom_raster(aes(fill = CellMeans)) +
  scale_fill_gradientn(colours = terrain.colors(12))
```

```{r,fig.width=8,fig.height=3}
ggplot(Grid.dat, aes(Easting, Northing)) +
  geom_raster(aes(fill = TrendMeans)) +
  scale_fill_gradientn(colours = terrain.colors(12))
```


```{r,fig.width=8,fig.height=3}
ggplot(Grid.dat, aes(Easting, Northing)) +
  geom_raster(aes(fill = KrigMeans)) +
  scale_fill_gradientn(colours = terrain.colors(12))
```



