---
title: "Case Study 2, Part 1"
author: "Peter Claussen"
date: "10/3/2017"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(MASS)
library(ggplot2)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```

We have two examples of corn fields planted with multiple varieties. Can we detect differences among varieties?

# Processing

The first step is to load each file and process

```{r}
EastQuarter.dat <- read.csv("East Quarter.csv",header=TRUE,comment.char = "#")
head(EastQuarter.dat)
North80.dat <- read.csv("North 80.csv",header=TRUE,comment.char = "#")
head(North80.dat)
```

We write a function to standardize each file.

```{r}
metric_from_gps <- function(longitude, latitude, origin=c(0,0)) {
  if(origin[1]==0) {
    origin <- c(min(longitude),min(latitude))
  }
  mid_latitude <- (origin[2] + max(latitude))/2
  
  easting <- longitude - origin[1]
  northing <- latitude - origin[2]
  
  m_per_deg_lat = 111132.954 - 559.822 * cos(2.0 * mid_latitude) + 1.175 * cos(4.0 * mid_latitude)
  m_per_deg_lon = (3.14159265359/180 ) * 6367449 * cos(mid_latitude)
  easting <- easting*m_per_deg_lon
  northing <- northing*m_per_deg_lat
  
  return(list(northing=northing,
              easting=easting,
              origin=origin,
              m_per_deg_lon=m_per_deg_lon,
              m_per_deg_lat=m_per_deg_lat))
}


standardize.field <- function(field.dat,origin=c(0,0)) {
  
  #we will aggregate those values which can be averaged.
  col.names = names(field.dat)
  drop.columns = c(
    which(col.names=="Field"),
    which(col.names=="Dataset"),
    which(col.names=="Product"),
    which(col.names=="Desc")
  )
  #convert date-time to seconds
  field.dat$DateTime <- as.POSIXct(as.character(field.dat[,1]), 
                                       format = "%m/%d/%Y %I:%M:%S %p",tz = "")
  field.dat$Seconds <- field.dat$DateTime - field.dat$DateTime[1]
  aggregate.dat <- field.dat[,-1]
  
  #remove trivial values
  field.dat <- subset(field.dat,field.dat$Yield!=0)
  
  meters <- metric_from_gps(field.dat$Longitude,
                            field.dat$Latitude,
                            origin)
  #convert longitude and latitude to meters
  field.dat$Easting <- meters$easting
  field.dat$Northing <- meters$northing
  
  #compute a quantile
  field.dat$Rank <- rank(field.dat$Yield)
  field.dat$Quantile <- field.dat$Rank/length(field.dat$Rank)
  field.dat$Percent <- 100*field.dat$Yield/median(field.dat$Yield)
  return(field.dat)
}
```

# East Quarter

I've already inspected the data to determine which part of the field has strips. We'll truncate to something reasonably square and balanced with regard to variety placement.

```{r, ProcessEastQuarter}
EastQuarter.dat$Yield <- EastQuarter.dat$YldVolDry
EastQuarter.dat <- standardize.field(EastQuarter.dat)
EastQuarter.dat$Product <- as.factor(EastQuarter.dat$Product)
```

```{r, SubsetEastQuarter}
EastQuarter.dat <- subset(EastQuarter.dat,EastQuarter.dat$Easting>=180)
EastQuarter.dat$Easting <- EastQuarter.dat$Easting - min(EastQuarter.dat$Easting)
EastQuarter.dat <- subset(EastQuarter.dat,EastQuarter.dat$Easting<=400)

EastQuarter.dat <- subset(EastQuarter.dat,EastQuarter.dat$Northing>=435)
EastQuarter.dat$Northing <- EastQuarter.dat$Northing - min(EastQuarter.dat$Northing)
EastQuarter.dat <- subset(EastQuarter.dat,EastQuarter.dat$Northing<=145)

EastQuarter.dat$Product <- as.factor(as.character(EastQuarter.dat$Product))
```

```{r,fig.width=8,fig.height=4, EastQuarterProduct}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,EastQuarterHistogram}
truehist(EastQuarter.dat$Yield)
```

```{r,fig.width=8,fig.height=4, EastQuarterYield}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Yield),size=2) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Yield", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

```{r,fig.width=8,fig.height=4, EastQuarterQuantile}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Quantile),size=2) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Quantile", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

# North

```{r,ProcessNorthQuarter}
North80.dat$Yield <- North80.dat$YldVolDry
North80.dat <- standardize.field(North80.dat)

North80.dat <- subset(North80.dat,North80.dat$Northing>=25)
North80.dat$Northing <- North80.dat$Northing - min(North80.dat$Northing)
North80.dat <- subset(North80.dat,North80.dat$Northing<=300)

North80.dat <- subset(North80.dat,North80.dat$Easting>=740)
North80.dat <- subset(North80.dat,North80.dat$Easting<=920)

North80.dat$Easting <- North80.dat$Easting - min(North80.dat$Easting)

North80.dat$Product <- as.factor(as.character(North80.dat$Product))
```

```{r,fig.width=6,fig.height=8}
ggplot(North80.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "North 80")
```

```{r,fig.width=6,fig.height=8}
ggplot(North80.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Yield),size=2) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Yield", x="Longitude (m)", y="Latitude (m)", title = "North 80")
```


```{r}
truehist(North80.dat$Yield)
```

```{r,fig.width=6,fig.height=8}
ggplot(North80.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Quantile),size=2) + 
scale_colour_gradient(low=cbPalette[7], high=cbPalette[4]) +
labs(colour = "Quantile", x="Longitude (m)", y="Latitude (m)", title = "North 80")
```


```{r}
summary(aov(lm(Yield ~ Product,data=EastQuarter.dat)))
summary(aov(lm(Quantile ~ Product,data=EastQuarter.dat)))
tapply(EastQuarter.dat$Yield,list(EastQuarter.dat$Product),mean)
tapply(EastQuarter.dat$Quantile,list(EastQuarter.dat$Product),mean)
```

```{r}
summary(aov(lm(Yield ~ Product,data=North80.dat)))
summary(aov(lm(Quantile ~ Product,data=North80.dat)))
tapply(North80.dat$Yield,list(North80.dat$Product),mean)
tapply(North80.dat$Quantile,list(North80.dat$Product),mean)
```

```{r}
save(EastQuarter.dat,North80.dat,file="Strips.Rda")
```