---
title: "Case Study 2, Part 2"
author: "Peter Claussen"
date: "10/3/2017"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(ggplot2)
library(rsm)
library(ncf)
library(ape)
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#F0E442","#CC79A7","#000000","#734f80", "#2b5a74", "#004f39", "#787221", "#003959", "#6aaf00", "#663cd3")
```



# East Quarter

```{r}
load(file="Strips.Rda")
```


```{r,fig.width=8,fig.height=4, EastQuarterProduct}
ggplot(EastQuarter.dat, aes(Easting,Northing)) + 
geom_point(aes(colour = Product),size=2) + 
scale_colour_manual(values=cbPalette) +
labs(colour = "Variety", x="Longitude (m)", y="Latitude (m)", title = "East Quarter")
```

We'll want to look at measures of spatial correlation, but first let's try to determine a trend model for each. We aren't too interested in kriging, since we won't be trying to map yields to a uniform set of points.

## Trend Surface

```{r}
Yield5.lm <- lm(Yield ~ poly(Easting, Northing, degree=5), data=EastQuarter.dat)
Yield7.lm <- lm(Yield ~ poly(Easting, Northing, degree=7), data=EastQuarter.dat)
Yield9.lm <- lm(Yield ~ poly(Easting, Northing, degree=9), data=EastQuarter.dat)
Yield11.lm <- lm(Yield ~ poly(Easting, Northing, degree=11), data=EastQuarter.dat)
```


```{r,fig.width=8,fig.height=12}
par(mfrow=c(4,1))
contour(Yield5.lm, Northing ~ Easting, image = TRUE,main="Poly 5")
contour(Yield7.lm, Northing ~ Easting, image = TRUE,main="Poly 7")
contour(Yield9.lm, Northing ~ Easting, image = TRUE,main="Poly 9")
contour(Yield11.lm, Northing ~ Easting, image = TRUE,main="Poly 11")
par(mfrow=c(1,1))
```

I'm concerned that Poly 11 might be overfitting in the lower left corner, so we'll choose Poly 9 (note - we could continue with diagnostics of Local I to check that assertion).

```{r,ExtractResiduals}
EastQuarter.dat$Yield9.resid <- Yield9.lm$residuals
```

# Check for white noise

```{r,ComputeDistance}
Distance.mat <- as.matrix(dist(cbind(EastQuarter.dat$Easting, EastQuarter.dat$Northing)))
Distance.mat <- 1/Distance.mat
diag(Distance.mat) <- 0
```

```{r,ComputeI}
print(Moran9Yield <-Moran.I(EastQuarter.dat$Yield, Distance.mat))
print(Moran9Resid <-Moran.I(EastQuarter.dat$Yield9.resid, Distance.mat))
```



# Local Correlation 

Resampling can take a very long time, so I'll use a flag to control whether we resample or simply plot local measures. Resampling is needed for p-values; I'm not concerned about p-values for the points in the correlogram.

```{r}
resample = 100
```

## Correlation in Yield
```{r,Yield9Correlog}
Yield.clg <- correlog(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Yield, 
                          increment=5, resamp=0, quiet=TRUE)
plot(Yield.clg)
```

```{r,Yield9LISA, fig.width=8,fig.height=5}
Yield9.lisa <- lisa(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Yield, 
                         neigh=10, resamp=resample, quiet=TRUE)
plot.lisa(Yield9.lisa, negh.mean=FALSE)
```

## Correlation in Yield Residuals

```{r,Yield9ResidualsCorrelog}
Yield9.resid.clg <- correlog(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Yield9.resid, 
                          increment=5, resamp=0, quiet=TRUE)
plot(Yield9.resid.clg)
```

```{r,Yield9ResidualsLISA, fig.width=8,fig.height=5}
Yield9.resid.lisa <- lisa(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Yield9.resid, 
                         neigh=10, resamp=resample, quiet=TRUE)
plot.lisa(Yield9.resid.lisa, negh.mean=FALSE)
```

```{r,fig.width=8,fig.height=5}
contour(Yield9.lm, Northing ~ Easting, image = TRUE,main="Poly 9")
```

## Correlation in Quantiles

```{r}
Quantile9.lm <- lm(Quantile ~ poly(Easting, Northing, degree=9), data=EastQuarter.dat)
EastQuarter.dat$Quantile9.resid <- Quantile9.lm$residuals
```

```{r,QuantilesCorrelog}
Quantile.clg <- correlog(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Quantile, 
                          increment=5, resamp=0, quiet=TRUE)
plot(Quantile.clg)
```

```{r,QuantilesResidualsCorrelog}
Quantile.resid.clg <- correlog(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Quantile9.resid, 
                          increment=5, resamp=0, quiet=TRUE)
plot(Quantile.resid.clg)
```

```{r,QuantileLISA, fig.width=8,fig.height=5}
Quantile.lisa <- lisa(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Quantile9, 
                         neigh=10, resamp=resample, quiet=TRUE)
plot.lisa(Quantile.lisa, negh.mean=FALSE)
```

```{r,QuantileResidualsLISA, fig.width=8,fig.height=5}
Quantile.resid.lisa <- lisa(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$Quantile9.resid, 
                         neigh=10, resamp=resample, quiet=TRUE)
plot.lisa(Quantile.resid.lisa, negh.mean=FALSE)
```

# Trend + Variety AOV

Does including variety (`Product`) in the model improve spatial correlation?

```{r}
YieldVariety5.lm <- lm(Yield ~ poly(Easting, Northing, degree=5) + Product, data=EastQuarter.dat)
summary(aov(YieldVariety5.lm))
YieldVariety9.lm <- lm(Yield ~ poly(Easting, Northing, degree=9) + Product, data=EastQuarter.dat)
summary(aov(YieldVariety9.lm))
YieldVariety11.lm <- lm(Yield ~ poly(Easting, Northing, degree=11) + Product, data=EastQuarter.dat)
summary(aov(YieldVariety11.lm))
```

```{r,fig.width=8,fig.height=8}
par(mfrow=c(2,1))
contour(Yield9.lm, Northing ~ Easting, image = TRUE,main="Poly 9")
contour(YieldVariety9.lm, Northing ~ Easting, image = TRUE,main="Poly 9 + Product")
par(mfrow=c(1,1))
```

```{r}
EastQuarter.dat$YieldVariety9.resid <- YieldVariety9.lm$residuals
print(Moran9Variety <-Moran.I(EastQuarter.dat$YieldVariety9.resid, Distance.mat))
```

```{r,YieldVariety9ResidualsCorrelog}
YieldVariety9.resid.clg <- correlog(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$YieldVariety9.resid, 
                          increment=5, resamp=0, quiet=TRUE)
plot(YieldVariety9.resid.clg)
```

```{r,YieldVariety9ResidualsLISA, fig.width=8,fig.height=5}
YieldVariety9.resid.lisa <- lisa(EastQuarter.dat$Easting, EastQuarter.dat$Northing, EastQuarter.dat$YieldVariety9.resid, 
                         neigh=10, resamp=resample, quiet=TRUE)
plot.lisa(YieldVariety9.resid.lisa, negh.mean=FALSE)
```

```{r}
library(lsmeans)
Yield.lm <- lm(Yield ~ Product, data=EastQuarter.dat)
lsmeans(Yield.lm, cld ~ Product)
lsmeans(YieldVariety5.lm, cld ~ Product)
lsmeans(YieldVariety9.lm, cld ~ Product)
lsmeans(YieldVariety11.lm, cld ~ Product)
```




